\section{Background}
\subsection{The qualitative interpretation}
The cumulant has the ability to enhance spectral features with respect to $GW$. The prototypical example that is given to motivate its utility is the analysis of the self-consistent $GW$ spectral function by von Barth and Holm for the uniform electron gas. There they show that scGW predicts an unphysical peak, known as the plasmaron, which is off from the expected plasmon frequency, as the only feature in the satellite spectrum. Cumulant plus $GW$, on the other hand, gives a more accurate answer. 
The way I think about this is as follows. $GW$ (with or without self-consistency) yields similar quasiparticle energies, while self-consistency mostly affects spectral weight distribution. However, $GW$ often produces an artificial plasmaron satellite. The cumulant expansion not only redistributes weight but also corrects the satellite structure, eliminating the spurious plasmaron and aligning the features with the physical plasmon frequency.\\\\
As we know, the ansatz for the cumulant $C(t)$ is
\begin{equation}
    G(t) = G_0(t) e^{C(t)}
\end{equation}
where we have the non-interacting and fully interacting Green's functions $G_0$ and $G$, respectively. After some derivation, we arrive at the Landau form for the cumulant
\begin{equation}
    C(t)=\int d \omega \frac{\beta(\omega)}{\omega^2}\left[e^{-i \omega t}+i \omega t-1\right]
\end{equation}
where the cumulant kernel is defined as
\begin{equation}
    \beta(\omega)=-\frac{1}{\pi} \operatorname{Im} \Sigma^{\mathrm{c}}(\omega)
\end{equation}
This form is amenable to physical interpretation if we partition into
\begin{equation}
    C(t)=-a+i \Delta t+\tilde{C}(t)
\end{equation}
where $a=\int d \omega \beta(\omega) / \omega^2$ is the net satellite strength, $\Delta=\int d \omega \beta(\omega) / \omega$ is the quasiparticle shift, or core-level "relaxation energy", and $\tilde{C}(t)$ is the remainder of the cumulant, which contains the information about the satellites.

\subsection{Alternate derivation starting from Dyson equation}
We can start from where Schwinger's fictitious potential $u$ has already been introduced:
\begin{align}
G_{u}\left(1,1^{\prime}\right)= & G^{0}\left(1,1^{\prime}\right)+G^{0}(1, \overline{2}) \left\{\left[u(\overline{2})+v_{H u}(\overline{2})\right] G_{u}\left(\overline{2}, 1^{\prime}\right)+i v_{c}(\overline{2}, \overline{3}) \frac{\delta G_{u}\left(\overline{2}, 1^{\prime}\right)}{\delta u\left(\overline{3}^{+}\right)}\right\} 
\end{align}
where $G^{0}$ is the non-interacting Green's function and $v_{c}$ is the bare Coulomb interaction. $v_{H u}$ is the Hartree potential built with the density $n_{u}(\mathbf{x})=-i G_{u}\left(\mathbf{x}, \mathbf{x}, t, t^{+}\right)$. One of the complications of the equations is the fact that the density $n_{u}$ in the Hartree potential introduces a term that is quadratic in $G_{u}$ for the first term in the above equation. To overcome this problem, we introduce the total classical potential
\begin{equation}
u_{\mathrm{cl}}(1)=u(1)+v_{H u}(1)
\end{equation}
which allows us to rewrite the equation for $G_{u}\equiv G_u^{\mathrm{cl}}$ as
\begin{align}
G_{u}\left(1,1^{\prime}\right)= & G^{0}\left(1,1^{\prime}\right)+G^{0}(1, \overline{2}) u_{\mathrm{cl}}(\overline{2}) G_{u}\left(\overline{2}, 1^{\prime}\right) +i G^{0}(1, \overline{2}) v_{c}(\overline{2}, \overline{3}) \frac{\delta G_{u}\left(\overline{2}, 1^{\prime}\right)}{\delta u\left(\overline{3}^{+}\right)} \\
= & G^{0}\left(1,1^{\prime}\right)+G^{0}(1, \overline{2}) u_{\mathrm{cl}}(\overline{2}) G_{u}\left(\overline{2}, 1^{\prime}\right) +i G^{0}(1, \overline{2}) W_{u}(\overline{2}, \overline{3}) \frac{\delta G_{u}\left(\overline{2}, 1^{\prime}\right)}{\delta u_{\mathrm{cl}}\left(\overline{3}^{+}\right)}
\end{align}
where we have defined the screened Coulomb interaction $W_{u} =\epsilon_{u}^{-1} v_{c}$ with the time-ordered inverse dielectric function $\epsilon_{u}^{-1} =\delta u_{\mathrm{cl}} / \delta u$. Note that $\epsilon_{u}^{-1}$ is not the usual linear response dielectric function, since it depends on the perturbing potential. However, since we are interested in the solution for vanishing $u$, a reasonable approximation is to evaluate the equation using $\epsilon_{u}^{-1} \approx \epsilon^{-1}$ at $u=0$. \emph{This corresponds to a linear-response approximation.} Written in a basis, the resulting equation reads
\begin{align}
G_{i j}^{u_{cl}}\left(t_{12}\right)= & G_{i j}^{0}\left(t_{12}\right)+G_{i m}^{0}\left(t_{13}\right) u_{\mathrm{cl}, m k}\left(t_{3}\right) G_{k j}^{u_{cl}}\left(t_{32}\right) +i G_{i k}^{0}\left(t_{13}\right) W_{k l m n}\left(t_{34}\right) \frac{\partial G_{n j}^{u_{cl}}\left(t_{32}\right)}{\partial u_{\mathrm{cl}, l m}\left(t_{4}\right)}
\label{eq:gw_start}
\end{align}
where $t_{12} \equiv\left(t_{1}, t_{2}\right)$ or $\left(t_{1}-t_{2}\right)$ in equilibrium, $W_{k l m n}$ is a matrix element of the screened Coulomb interaction $W$, and we have replaced functional derivatives by partial derivatives, supposing the basis to be discrete, which corresponds to calculations in practice. Repeated indices are summed over.
\subsubsection{GW approximation}
 The $GW$ approximation sets
\begin{equation}
\frac{\partial G_{n j}^{u}\left(t_{32}\right)}{\partial u_{\mathrm{cl}, l m}\left(t_{4}\right)} \approx G_{n l}\left(t_{34}\right) G_{m j}\left(t_{42}\right)
\end{equation}
At $u=0$, this yields the Dyson equation $G =G^{0}+G^{0} \Sigma^{G W} G$ with the $GW$ approximation for the self-energy,
\begin{equation}
\Sigma_{i m}^{G W}\left(t_{34}\right)=v_{H, i m}+i G_{n l}\left(t_{34}\right) W_{i l m n}\left(t_{34}\right) .
\end{equation}
But we will take a different route here, in order to obtain the cumulant expression for the Green's function.
\subsubsection{Cumulant expansion}
The basic idea is to introduce a quasi-particle Green's function $G^{Q P, u}$, defined as
\begin{align}
\left[G^{Q P, u}\right]_{i j}^{-1}&=\left[G_{0}^{-1}\right]_{i j}-\left[u_{\mathrm{cl}}\right]_{i j}-\Sigma_{i j}^{G W}\left(\frac{\varepsilon_{i}+\varepsilon_{j}}{2}\right)\\
 \implies \left[G_0\right]_{ij} &= G^{Q P, u}_{i j} - G^{Q P, u}_{i m} \left( u_{\mathrm{cl}, m k} + \Sigma_{m k}^{G W}\left(\frac{\varepsilon_{m}+\varepsilon_{k}}{2}\right) \right) \left[ G_0\right]_{kj}
\end{align}
Plugging this into \ref{eq:gw_start} (suppressing the time and orbital indices for ease of notation) gives
\begin{align}
G^{u}&= G^{Q P, u} - G^{Q P, u} \left( u_{\mathrm{cl}} +  \Sigma  \right) G_0 \notag \\
& + \left(G^{Q P, u} - G^{Q P, u} \left( u_{\mathrm{cl}} +  \Sigma \right) G_0\right) u_{\mathrm{cl}} G^{u} \notag \\
& + i \left(G^{Q P, u} - G^{Q P, u} \left( u_{\mathrm{cl}} +  \Sigma \right) G_0\right) W \frac{\partial G^{u}}{\partial u_{\mathrm{cl}}} \\
&= G^{Q P, u} + G^{Q P, u} u_{\mathrm{cl}} G^{u} + i G^{Q P, u} W \frac{\partial G^{u}}{\partial u_{\mathrm{cl}}} \notag \\
& - G^{Q P, u} \left( u_{\mathrm{cl}} +  \Sigma \right) \left[ \underbrace{G_0 + G_0 u_{\mathrm{cl}} G^{u} + i G_0 W \frac{\partial G^{u}}{\partial u_{\mathrm{cl}}}}_{G^{u}} \right] \notag \\
&= G^{Q P, u} + i G^{Q P, u} W \frac{\partial G^{u}}{\partial u_{\mathrm{cl}}} - G^{Q P, u}  \Sigma  G^{u} \\
\implies G^{u}_{ij}(t_{12}) &= G^{Q P, u}_{ij}(t_{12}) + i G^{Q P, u}_{ik}(t_{13}) W_{klmn}(t_{34}) \frac{\partial G^{u}_{mj}(t_{32})}{\partial u_{\mathrm{cl}, lm}(t_4)} - G^{Q P, u}_{ik}(t_{13}) \Sigma^{GW}_{kl}\left(\frac{\varepsilon_k + \varepsilon_l}{2}\right) G^{u}_{lj}(t_{32})
\end{align}
\textcolor{orange}{%
We have made use of the $GW$ self-energy. It is known that in the $GW$ approximation, because of a fortuitous cancellation of errors, it is most wise to use the RPA approximation for the dielectric function that goes into the screened Coloumb interaction. I wonder if this is also the smartest decision for the cumulant expansion; we could try using a more accurate approximation to the dielectric function and see what the effect is.} Now one decouples the equations by supposing that $G^{u}$ and $G^{Q P, u}$ are diagonal in the same $u$-independent basis. So we take the diagonal components of all operators in the above equation, so $G^{u}_{ij} \rightarrow G^{u}_{ii}\equiv \mathcal{G}^{u}$, $G^{Q P, u}_{ij} \rightarrow G^{Q P, u}_{ii} \equiv \mathcal{G}^{Q P, u}$, $\Sigma^{GW}_{ij}\left(\frac{\varepsilon_{i}+\varepsilon_{j}}{2}\right) \rightarrow \Sigma^{GW}_{ii}\left(\varepsilon_i\right) \equiv \tilde{\Sigma}^{GW}$, $W_{ijkl} \rightarrow W_{iiii} \equiv \mathcal{W}$, and $u_{\mathrm{cl}, ij} \rightarrow u_{\mathrm{cl}, ii} \equiv u$. This is a strong assumption, but nevertheless, it allows us to get to the conventional form for the cumulant expansion. The resulting equation is
\begin{equation}
\mathcal{G}^{u}(t_{12}) = \mathcal{G}^{Q P, u}(t_{12}) + i \mathcal{G}^{Q P, u}(t_{13}) \mathcal{W}(t_{34}) \frac{\partial \mathcal{G}^{u}(t_{32})}{\partial {u}(t_4)} - \mathcal{G}^{Q P, u}(t_{13}) \tilde{\Sigma}^{GW} \mathcal{G}^{u}(t_{32})
\end{equation}
In the paper they claim that the solution for $u \rightarrow 0$ is
\begin{align}
\mathcal{G}\left(t_{12}\right)= & \mathcal{G}_{Q P}^{0}\left(t_{12}\right) e^{i\left(t_{1}-t_{2}\right) \Sigma_{i i}^{G W}\left(\varepsilon_{i}\right)} \exp \left[-i \int_{t_{1}}^{t_{2}} d t^{\prime} \int_{t^{\prime}}^{t_{2}} d t^{\prime \prime} \mathcal{W}\left(t^{\prime}-t^{\prime \prime}\right)\right].
\end{align}
 I have not been able to derive, but my attempts are below, and we will just continue for now. The double integral can be evaluated as
\begin{align}
-i \int_{t_{1}}^{t_{2}} d t^{\prime} \int_{t^{\prime}}^{t_{2}} d t^{\prime \prime} \mathcal{W}\left(t^{\prime}-t^{\prime \prime}\right) 
\label{a}
& =-\frac{i}{2\pi} \int d\omega\, \mathcal W(\omega)
\int_{t_1}^{t_2} dt' \int_{t'}^{t_2} dt''\, e^{-i\omega (t' - t'')}\\
&= -\frac{1}{2\pi} \int d\omega\, \frac{\mathcal W(\omega)}{\omega}
\int_{t_1}^{t_2} dt' \Big( e^{i\omega (t_2-t')} - 1 \Big) 
\label{b}
\\
&= -\frac{1}{2\pi} \int d\omega\, \frac{\mathcal W(\omega)}{\omega}
\left[ \frac{e^{i\omega (t_2-t_1)} - 1}{i\omega} - (t_2-t_1) \right] 
\label{c}
\\
&=-\left(t_{1}-t_{2}\right) \frac{1}{2 \pi} \int d \omega \frac{\mathcal{W}(\omega)}{\omega} +\frac{i}{2 \pi} \int d \omega \frac{\mathcal{W}(\omega)}{\omega^{2}}\left(e^{-i \omega\left(t_{1}-t_{2}\right)}-1\right)
\label{d}
\end{align}
where in going from Eq.~(\ref{a}) to Eq.~(\ref{b}) we have used $\int_{t'}^{t_2} dt'' \, e^{-i\omega(t'-t'')}  = \frac{e^{i\omega (t_2-t')} - 1}{i\omega}$, and in going from Eq.~(\ref{b}) to Eq.~(\ref{c}) we have used $\int_{t_1}^{t_2} dt' \big(e^{i\omega(t_2-t')} - 1\big)
= \frac{e^{i\omega \Delta}-1}{i\omega} - \Delta$ with $\Delta = t_2-t_1$.
Let us first examine the term proportional to $\left(t_{1}-t_{2}\right)$ in Eq.~(\ref{d}), by comparing it to a GW quasi-particle shift. In the decoupling approximation, $\Sigma_{k k}^{G W} \approx i G_{k k} W_{k k k k}$. Evaluated at the quasi-particle energy, this yields exactly the term we are interested in. This means that $e^{-\left(t_{1}-t_{2}\right) \frac{1}{2 \pi} \int d \omega \frac{\mathcal{W}(\omega)}{\omega}}$ approximately cancels with the GW shift in $e^{i\left(t_{1}-t_{2}\right) \Sigma_{i i}^{G W}\left(\varepsilon_{i}\right)}$, and we are left with
\begin{equation*}
\mathcal{G}\left(t_{12}\right)=\mathcal{G}_{Q P}^{0}\left(t_{12}\right) \exp \left[\frac{i}{2 \pi} \int d \omega \frac{\mathcal{W}(\omega)}{\omega^{2}}\left(e^{i \omega\left(t_{1}-t_{2}\right)}-1\right)\right] \tag{17}
\end{equation*}


\begin{tcolorbox}
Using the functional derivative identity $\frac{\partial \mathcal{G}^{u}(t_{32})}{\partial u(t_4)}|_{u=0} = \mathcal{G}(t_{34}) \mathcal{G}(t_{42})$ and correspondingly setting $\mathcal{G}^{u}\rightarrow \mathcal{G}$, $\mathcal{G}^{Q P, u}\rightarrow \mathcal{G}^{Q P}$ gives
\begin{equation}
\mathcal{G}(t_{12}) = \mathcal{G}^{Q P}(t_{12}) + i \mathcal{G}^{Q P}(t_{13}) \mathcal{W}(t_{34}) \mathcal{G}(t_{34}) \mathcal{G}(t_{42}) - \mathcal{G}^{Q P}(t_{13}) \tilde{\Sigma}^{GW} \mathcal{G}(t_{32})
\end{equation}
Now define $\tilde{\mathcal{G}}(t_{12}) = e^{i (t_1 - t_2) \tilde{\Sigma}^{GW}} \mathcal{G}(t_{12}) \implies \mathcal{G}(t_{12}) = e^{-i (t_1 - t_2) \tilde{\Sigma}^{GW}} \tilde{\mathcal{G}}(t_{12})$. Plugging this in gives
\begin{align}
\tilde{\mathcal{G}}(t_{12}) &= e^{i (t_1 - t_2) \tilde{\Sigma}^{GW}} \mathcal{G}^{Q P}(t_{12}) + i e^{i (t_1 - t_2) \tilde{\Sigma}^{GW}} \mathcal{G}^{Q P}(t_{13}) \mathcal{W}(t_{34}) e^{-i (t_3 - t_4) \tilde{\Sigma}^{GW}} \tilde{\mathcal{G}}(t_{34}) e^{-i (t_4 - t_2) \tilde{\Sigma}^{GW}} \tilde{\mathcal{G}}(t_{42}) \notag \\
& - e^{i (t_1 - t_2) \tilde{\Sigma}^{GW}} \mathcal{G}^{Q P}(t_{13}) \tilde{\Sigma}^{GW} e^{-i (t_3 - t_2) \tilde{\Sigma}^{GW}} \tilde{\mathcal{G}}(t_{32}) \notag \\
\end{align}
\subsubsection{Inegration factor method}
Define $A(u)=-\mathcal{G}^{Q P, u}\left(t_{13}\right) \tilde{\Sigma}^{G W}, \quad B(u)=\mathcal{G}^{Q P, u}\left(t_{12}\right), \quad C(u)=i \mathcal{G}^{Q P, u}\left(t_{13}\right) \mathcal{W}\left(t_{34}\right) .$ Then the equation can be written as
\begin{equation}
C(u) \frac{\partial \mathcal{G}^u}{\partial u}+A(u) \mathcal{G}^u=B(u) .
\end{equation}
Divide through by $C(u)$, we get
\begin{equation}
\frac{\partial \mathcal{G}^u}{\partial u}+\frac{A(u)}{C(u)} \mathcal{G}^u=\frac{B(u)}{C(u)} .
\end{equation}
So our integrating factor is
\begin{equation}
\mu(u)=\exp \left(\int^u \frac{A(s)}{C(s)} d s\right) = \exp \left(+i \int^u d s \frac{\tilde{\Sigma}^{G W}}{\mathcal{W}}\right)
\end{equation}
and the solution is
\begin{align}
\mathcal{G}^u&=\frac{1}{\mu(u)}\left[C_0+\int^u \mu(s) \frac{B(s)}{C(s)} d s\right]\\
& = \exp \left(-i \int^u d s \frac{\tilde{\Sigma}^{G W}}{\mathcal{W}}\right)\left[C_0+\int^u d s \exp \left(+i \int^s d s' \frac{\tilde{\Sigma}^{G W}}{\mathcal{W}}\right) \frac{\mathcal{G}^{Q P, s}}{i \mathcal{G}^{Q P, s} \mathcal{W}}\right] \\
& = \exp \left(-i \int^u d s \frac{\tilde{\Sigma}^{G W}}{\mathcal{W}}\right)\left[C_0+\int^u d s \exp \left(+i\int^s d s' \frac{\tilde{\Sigma}^{G W}}{\mathcal{W}}\right) \frac{-i}{ \mathcal{W}}\right] \\
\end{align}    
\end{tcolorbox}


% Introduce shorthand:
% $$
% A(u)=-\mathcal{G}^{Q P, u}\left(t_{13}\right) \tilde{\Sigma}^{G W}, \quad B(u)=\mathcal{G}^{Q P, u}\left(t_{12}\right), \quad C(u)=i \mathcal{G}^{Q P, u}\left(t_{13}\right) \mathcal{W}\left(t_{34}\right) .
% $$

% Equation (1) is equivalent to
% $$
% C(u) \frac{\partial \mathcal{G}^u}{\partial u}+A(u) \mathcal{G}^u=B(u) .
% $$

% Divide through by $C(u)$ :
% $$
% \frac{\partial \mathcal{G}^u}{\partial u}+\frac{A(u)}{C(u)} \mathcal{G}^u=\frac{B(u)}{C(u)} .
% $$

% Now this is in the standard form $\frac{d Y}{d u}+\alpha(u) Y=\beta(u)$.
% 5. Integrating factor

% Define
% $$
% \mu(u)=\exp \left(\int^u \frac{A(s)}{C(s)} d s\right)
% $$

% Then the solution is
% $$
% g^u=\frac{1}{\mu(u)}\left[C_0+\int^u \mu(s) \frac{B(s)}{C(s)} d s\right]
% $$
% with constant $C_0$ fixed by the boundary condition.
% 6. Boundary condition and physical solution

% The physical requirement is:
% - As the Coulomb interaction $v_c \rightarrow 0$, or equivalently $W \rightarrow 0$, the solution must reduce to the non-interacting Green's function.
% - This selects the correct $C_0$.

% So you discard spurious solutions (phase transitions) and keep the branch that connects continuously to the free Green's function.
% 7. Set $u \rightarrow 0$

% Finally, evaluate (5) at $u=0$. Since $\mathcal{G}^{Q P, u}$ is linear in $u$, the coefficients $A(u), B(u), C(u)$ reduce to constants when $u=0$. The integral in the exponent then gives you exactly the exponentials in the cumulant solution:
% $$
% \mathcal{G}\left(t_{12}\right)=\mathcal{G}_{Q P}^0\left(t_{12}\right) \exp \left[i\left(t_1-t_2\right) \Sigma_{i i}^{G W}\left(\varepsilon_i\right)\right] \exp \left(-i \int_{t_1}^{t_2} d t^{\prime} \int_{t^{\prime}}^{t_2} d t^{\prime \prime} W\left(t^{\prime}-t^{\prime \prime}\right)\right)
% $$




\section{Cumulant expansion for electronic structure}

\subsection{Annotation of Loos paper}
The definition of the cumulant ansatz for the retarded Green's function is given by:
\begin{equation}
    \bm{G}(t) = \bm{G}^0(t)e^{\bm{C}(t)}
\end{equation}
where $\bm{C}(t)$ is the retarded cumulant and $\bm{G}^0(t)$ is the retarded HF Green's function. By relating the Dyson equation to the Taylor series expansion of the exponential (both to first order), we can write:
\begin{equation}
    \bm{G}^0(t) \bm{C}(t) = \iint \dd t_1 \dd t_2 \bm{G}^0(t-t_1) \bm{\Sigma}^c(t_1 - t_2) \bm{G}^0(t_2)
\end{equation}
\textbf{This first order expansion is exact up to the first order in the screened Coulomb interaction $W$. If we choose instead to use a second order self-energy, now the cumulant will be exact to second order in the bare Coulomb interaction $v$.}
Projecting to the spin-orbital basis and inserting the resolution of the identity, we get:
\begin{align}
    \sum_{r}\bra{p}\bm{G}^0(t) \ket{r}\bra{r}\bm{C}(t)\ket{q} &= \sum_{rs}\iint \dd t_1 \dd t_2 \bra{p}\bm{G}^0(t-t_1)\ket{r} \bra{r}\bm{\Sigma}^c(t_1 - t_2)\ket{s} \bra{s}\bm{G}^0(t_2)\ket{q} \\
    \sum_{r}\bm{G}_{pr}^0(t) \bm{C}_{rq}(t) &= \sum_{rs}\iint \dd t_1 \dd t_2 \bm{G}_{ps}^0(t-t_1) \bm{\Sigma}_{sr}^c(t_1 - t_2) \bm{G}_{rq}^0(t_2)\\
    \bm{G}_{pp}^{0}(t) \bm{C}_{pq}(t) &= \underbrace{\iint \dd t_1 \dd t_2 \bm{G}_{pp}^{0}(t-t_1) \bm{\Sigma}_{pq}^c(t_1 - t_2) \bm{G}_{qq}^{0}(t_2)}_{*}
    \label{eqn:cumulant_connection}
\end{align}
where $\bm{G}^0(t)$ is the retarded HF Green's function, which is diagonal in the spin-orbital basis, specifically $\bm{G}_{pp}^{0}(t) = -i\Theta(t)e^{-i\epsilon_p t}$, where $\epsilon_p$ is the HF energy of the $p$-th spin-orbital.
The formula for the inverse Fourier transform is given by:
\begin{equation}
    f(t) = \int \frac{\dd \omega}{2\pi} e^{-i\omega t} f(\omega)
\end{equation}
which implies that
\begin{align}
    \bm{G}_{pp}^{0}(t-t_1) = \int \frac{\dd \omega}{2\pi} e^{-i\omega (t-t_1)} \bm{G}_{pp}^{0}(\omega)\\
    \bm{\Sigma}_{pq}^c(t_1 - t_2) = \int \frac{\dd \omega'}{2\pi} e^{-i\omega' (t_1 - t_2)} \bm{\Sigma}_{pq}^c(\omega')\\
    \bm{G}_{qq}^{0}(t_2) = \int \frac{\dd \omega''}{2\pi} e^{-i\omega'' t_2} \bm{G}_{qq}^{0}(\omega'')
\end{align}
and plugging into the double time integral *, we get:
\begin{align}
    * &= \iint \dd t_1 \dd t_2 \left[\int \frac{\dd \omega}{2\pi} e^{-i\omega (t-t_1)} \bm{G}_{pp}^{0}(\omega)\right] \left[\int \frac{\dd \omega'}{2\pi} e^{-i\omega' (t_1 - t_2)} \bm{\Sigma}_{pq}^c(\omega')\right] \left[\int \frac{\dd \omega''}{2\pi} e^{-i\omega'' t_2} \bm{G}_{qq}^{0}(\omega'')\right]\\
    &= \underbrace{\int \dd t_1 e^{-i \left(\omega' -\omega\right)t_1} \int \dd t_2 e^{-i \left(\omega'' -\omega'\right)t_2}}_{4\pi^2 \delta(\omega' -\omega)\delta(\omega'' -\omega')} \iiint \dd \omega \dd \omega' \dd \omega'' \frac{e^{-i\omega t}}{8\pi^3} \bm{G}_{pp}^{0}(\omega)\bm{\Sigma}_{pq}^c(\omega')\bm{G}_{qq}^{0}(\omega'')\\
    &= \int \frac{\dd \omega}{2\pi} e^{-i\omega t} \bm{G}_{pp}^{0}(\omega)\bm{\Sigma}_{pq}^c(\omega)\bm{G}_{qq}^{0}(\omega)
\end{align}
Multiplying both sides of eqn.~\ref{eqn:cumulant_connection} by $ie^{\epsilon_p t} $ and recalling that we are dealing with retarded quantities that vanish for negative times, we get:
\emph{We are also interested in what happens if we use an exact self-energy in \ref{eq:Cpp_0} instead of the $GW$ one. Also can we get away with not using the diagonal approximation?} 
\subsection{Standard route: diagonal cumulant with GW self-energy}
\begin{align}
	 C_{pp}(t) &= i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}^c\left(\omega+\epsilon_p^{HF}\right)}{(\omega + i \eta)^2} e^{-i \omega t}
\label{eq:Cpp_0} \\
&= i \int \frac{d\omega}{2\pi} \frac{1}{(\omega + i \eta)^2} e^{-i \omega t} \left[ \sum_{i\nu} \frac{M_{pi\nu}^2}{\omega + \underbrace{\epsilon_p^{HF} - \epsilon_i + \Omega_\nu + i \eta}_{-\Delta_{pi\nu}}} + \sum_{a\nu} \frac{M_{pa\nu}^2}{\omega + \underbrace{\epsilon_p^{HF} - \epsilon_a - \Omega_\nu + i \eta}_{-\Delta_{pa\nu}}} \right] \\
& =\mathrm{i} \sum_{i v} M_{p i v}^2 \int \frac{\mathrm{~d} \omega}{2 \pi} e^{-\mathrm{i} \omega t} \frac{1}{[\omega+\mathrm{i} \eta]^2} \frac{1}{\omega-\Delta_{p i v}} +\mathrm{i} \sum_{a v} M_{p a v}^2 \int \frac{\mathrm{~d} \omega}{2 \pi} e^{-\mathrm{i} \omega t} \frac{1}{[\omega+\mathrm{i} \eta]^2} \frac{1}{\omega-\Delta_{p a v}}
\label{eq:Cpp_1}
\\
&= \sum_{i\nu} \zeta_{pi\nu} \left[ e^{-i\Delta_{pi\nu} t} - 1 + i\Delta_{pi\nu} t \right] + \sum_{a\nu} \zeta_{pa\nu} \left[ e^{-i\Delta_{pa\nu} t} - 1 + i\Delta_{pa\nu} t \right]
\label{eq:Cpp_2}
\end{align}
where in going from eqn.~\ref{eq:Cpp_m1} to eqn.~\ref{eq:Cpp_0}, where we made a diagonal approximation for the self-energy and introduced the frequency shift $\omega \to \omega + \epsilon_p^{HF}$, and then from eqn.~\ref{eq:Cpp_1} to eqn.~\ref{eq:Cpp_2}, we have evaluated a contour integral. For the final expression, we have defined $\zeta_{pi\nu} = \left(\frac{M_{pi\nu}}{\Delta_{pi\nu}}\right)^2$ and $\zeta_{pa\nu} = \left(\frac{M_{pa\nu}}{\Delta_{pa\nu}}\right)^2$. This allows us to arrive at the something similar to the Landau form of the cumulant.
\begin{tcolorbox}
A few notes on how to evaluate this integral: there is a double pole at $\omega_1 = -i\eta$ and a simple pole at $\omega_2 = -\Delta - i\eta$. Closing the contour in the lower half-plane because $\operatorname{Im}\left(\omega_1\right), \operatorname{Im}\left(\omega_2\right)<0$, and applying Cauchy's residue theorem, leads to
\begin{align}
    \int \frac{\mathrm{d} \omega}{2 \pi} e^{-\mathrm{i} \omega t} \frac{1}{\left(\omega-\omega_1\right)^2} \frac{1}{\omega-\omega_2} & =(-\mathrm{i})\left\{\left[\partial_\omega\left(\frac{e^{-\mathrm{i} \omega t}}{\omega-\omega_2}\right)\right]_{\omega=\omega_1}+\left[\frac{e^{-\mathrm{i} \omega t}}{\left(\omega-\omega_1\right)^2}\right]_{\omega=\omega_2}\right\} \\
    & =\frac{(-\mathrm{i})}{\left(\omega_1-\omega_2\right)^2}\left\{\left[(-\mathrm{i} t)\left(\omega_1-\omega_2\right)-1\right] e^{-\mathrm{i} \omega_1 t}+e^{-\mathrm{i} \omega_2 t}\right\}\\
\implies \int \frac{\mathrm{d} \omega}{2 \pi} e^{-i \omega t} \frac{1}{[\omega-(0-\mathrm{i} \eta)]^2} \frac{1}{\omega-\Delta}&=\frac{-\mathrm{i}}{\Delta^2}\left(e^{-\mathrm{i} \Delta t}+\mathrm{i} \Delta t-1\right)
\end{align}
\end{tcolorbox}
Now we plug in our derived expression for $C_{pp}(t)$ into the cumulant ansatz for the retarded Green's function:
\begin{align}
G_{pp}(t) & = G_{pp}^{HF}(t) e^{C_{pp}(t)} \\
& = -i \Theta(t) e^{-i \epsilon_p^{HF} t + C_{pp}(t)} \\
& = -i \Theta(t) e^{-i \epsilon_p^{HF} t + \sum_{i\nu} \zeta_{pi\nu}\left(e^{-i\Delta_{pi\nu} t} + i\Delta_{pi\nu} t - 1\right) + \sum_{a\nu} \zeta_{pa\nu} \left(e^{-i\Delta_{pa\nu} t} + i\Delta_{pa\nu} t - 1\right)}\\
& = -i \Theta(t) \underbrace{e^{-\sum_{i\nu} \zeta_{pi\nu} - \sum_{a\nu} \zeta_{pa\nu}}}_{Z_p^{QP}} e^{-i\overbrace{\left(\epsilon_p^{HF} - \sum_{i\nu} \zeta_{pi\nu}\Delta_{pi\nu} - \sum_{a\nu} \zeta_{pa\nu}\Delta_{pa\nu}\right)}^{\epsilon_p^{QP}} t} e^{\sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t}} \\ 
& = -i \Theta(t) Z_p^{QP} e^{-i \epsilon_p^{QP} t} e^{\sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t}} \\
\end{align}
where we have the weight of the quasiparticle peak $Z_p^{QP} = \exp\left(-\sum_{i\nu} \zeta_{pi\nu} - \sum_{a\nu} \zeta_{pa\nu}\right)$ and the quasiparticle energy $\epsilon_p^{QP} = \epsilon_p^{HF} - \left(\sum_{i\nu} \zeta_{pi\nu} \Delta_{pi\nu} + \sum_{a\nu} \zeta_{pa\nu} \Delta_{pa\nu}\right)$. 
\begin{tcolorbox}
We pause to make some important connections. Notice
\begin{align}
\epsilon_p^{QP} & = \epsilon_p^{HF} - \left(\sum_{i\nu} \zeta_{pi\nu} \Delta_{pi\nu} + \sum_{a\nu} \zeta_{pa\nu} \Delta_{pa\nu}\right) \\
& = \epsilon_p^{HF} - \left(\sum_{i\nu} \frac{M_{pi\nu}^2}{\Delta_{pi\nu}} + \sum_{a\nu} \frac{M_{pa\nu}^2}{\Delta_{pa\nu}}\right) \\
& = \epsilon_p^{HF} + \Sigma_{pp}^c\left(\epsilon_p^{HF}\right)
\end{align}
and
\begin{align}
Z_p^{QP} & = \exp\left(-\sum_{i\nu} \zeta_{pi\nu} - \sum_{a\nu} \zeta_{pa\nu}\right) \\
& = \exp\left(-\sum_{i\nu} \left(\frac{M_{pi\nu}}{\Delta_{pi\nu}}\right)^2 - \sum_{a\nu} \left(\frac{M_{pa\nu}}{\Delta_{pa\nu}}\right)^2\right) \\
& = \exp\left(\left[\frac{\partial \Sigma_{pp}^c(\omega)}{\partial \omega}\right]_{\omega = \epsilon_p^{HF}}\right) \\
\end{align}
where we have used the fact that $\Sigma_{pp}^c(\omega) = \sum_{i\nu} \frac{M_{pi\nu}^2}{\omega - \epsilon_i + \Omega_\nu} + \sum_{a\nu} \frac{M_{pa\nu}^2}{\omega - \epsilon_a - \Omega_\nu} \implies \left[\frac{\partial \Sigma_{pp}^c(\omega)}{\partial \omega}\right]_{\omega = \epsilon_p^{HF}} = -\sum_{i\nu} \left(\frac{M_{pi\nu}}{\Delta_{pi\nu}}\right)^2 - \sum_{a\nu} \left(\frac{M_{pa\nu}}{\Delta_{pa\nu}}\right)^2$.
\end{tcolorbox}
Next, we want to perform a Fourier transform.
\begin{align}
G_{pp}(\omega) & = \int_{-\infty}^{\infty} dt e^{i \omega t} G_{pp}(t)
\label{Gpp1}
\\
& = -i Z_p^{QP} \int_0^{\infty} dt e^{i(\omega - \epsilon_p^{QP}) t} e^{\sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t}} 
\label{Gpp2}
\\
& = -i Z_p^{QP} \int_0^{\infty} dt\, e^{i(\omega - \epsilon_p^{QP}) t} \left(1 + \sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t}4 \right) \\
&= -i Z_p^{QP} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP}) t]}\label{Gpp3} \\
&\quad - i Z_p^{QP} \sum_{i\nu} \zeta_{pi\nu} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP} - \Delta_{pi\nu}) t]} \\
&\quad - i Z_p^{QP} \sum_{a\nu} \zeta_{pa\nu} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP} - \Delta_{pa\nu}) t]} + \ldots \\
&= \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i\nu} \frac{Z_p^{QP} \zeta_{pi\nu}}{\omega - \epsilon_p^{QP} - \Delta_{pi\nu} + i\eta} + \sum_{a\nu} \frac{Z_p^{QP} \zeta_{pa\nu}}{\omega - \epsilon_p^{QP} - \Delta_{pa\nu} + i\eta} + \ldots\\
% & =-i Z_p^{Q P} \int_0^{+\infty} d r e^{\left[-\eta+i\left(\omega-\varepsilon_p^{Q P}\right)\right]} \\
% & -\mathrm{i} Z_p^{\mathrm{OP}} \sum_{i v} \zeta_{p i v} \int_0^{+\infty} \mathrm{d} r e^{\left\{-\eta+i\left[\omega-\left(\epsilon_p^{\mathrm{OP}}+\Delta_{p i v}\right)\right]\right\}^{\prime}}-\mathrm{i} Z_p^{\mathrm{OP}} \sum_{a v} \zeta_{p a v} \int_0^{+\infty} \mathrm{d} r e^{\left(-\eta+i\left[\omega-\left(\epsilon_p^{\mathrm{OP}}+\Delta_{p \omega v}\right)\right]\right\}^{\prime}} \\
& = \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i\nu} \frac{Z_{pi\nu}^{sat}}{\omega - \epsilon_{pi\nu}^{sat} + i\eta} + \sum_{a\nu} \frac{Z_{pa\nu}^{sat}}{\omega - \epsilon_{pa\nu}^{sat} + i\eta} + \ldots
\end{align}
In going from eqn.~\ref{Gpp1} to eqn.~\ref{Gpp2}, we used the step function to restrict the lower bound of the integral to $0$ and then we end by defining the satellite energies $\epsilon_{pi\nu}^{sat} = \epsilon_p^{QP} + \Delta_{pi\nu}$ and $\epsilon_{pa\nu}^{sat} = \epsilon_p^{QP} + \Delta_{pa\nu}$, as well as the satellite weights $Z_{pi\nu}^{sat} = Z_p^{QP} \zeta_{pi\nu}$ and $Z_{pa\nu}^{sat} = Z_p^{QP} \zeta_{pa\nu}$. \emph{What happens when we treat the exponential more than just up to the first order? Is this useful?}
\subsubsection{Spectral function}
The diagonal elements of the spectral function are obtained as (the virtual satellites spectral function, whose derivation will mirror that of the occupied satellites, are omitted for the sake of brevity)
\begin{align}
A_{pp}^{GW+C}(\omega) & = -\frac{1}{\pi} \operatorname{Im} G_{pp}(\omega) \\
& = -\frac{1}{\pi} \operatorname{Im}\left[\frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i\nu} \frac{Z_{pi\nu}^{sat}}{\omega - \epsilon_{pi\nu}^{sat} + i\eta} + \sum_{a\nu} \frac{Z_{pa\nu}^{sat}}{\omega - \epsilon_{pa\nu}^{sat} + i\eta}\right] \\
& = -\frac{1}{\pi} \operatorname{Im}\left[\frac{\operatorname{Re} Z_p^{QP} + i \operatorname{Im} Z_p^{QP}}{\omega - \operatorname{Re} \epsilon_p^{QP} + i\left(\eta - \operatorname{Im} \epsilon_p^{QP}\right)} + \sum_{i\nu} \frac{\operatorname{Re} Z_{pi\nu}^{sat} + i \operatorname{Im} Z_{pi\nu}^{sat}}{\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat} + i\left(\eta - \operatorname{Im} \epsilon_{pi\nu}^{sat}\right)} + \ldots \right] \\
& = -\frac{1}{\pi} \operatorname{Im}\left[\frac{\left(\operatorname{Re} Z_p^{QP} + i \operatorname{Im} Z_p^{QP}\right)\left(\omega - \operatorname{Re} \epsilon_p^{QP} - i\left(\eta - \operatorname{Im} \epsilon_p^{QP}\right)\right)}{\left(\omega - \operatorname{Re} \epsilon_p^{QP}\right)^2 + \left(\operatorname{Im} \epsilon_p^{QP}\right)^2}\right.\\
& \left. + \sum_{i\nu} \frac{\left(\operatorname{Re} Z_{pi\nu}^{sat} + i \operatorname{Im} Z_{pi\nu}^{sat}\right)\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat} - i\left(\eta - \operatorname{Im} \epsilon_{pi\nu}^{sat}\right)\right)}{\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat}\right)^2 + \left(\operatorname{Im} \epsilon_{pi\nu}^{sat}\right)^2} + \ldots \right] \\
& = -\frac{1}{\pi}\left[\frac{\left(\operatorname{Re} Z_p^{QP}\right)\left(\operatorname{Im} \epsilon_p^{QP}\right) + \left(\operatorname{Im} Z_p^{QP}\right)\left(\omega - \operatorname{Re} \epsilon_p^{QP}\right)}{\left(\omega - \operatorname{Re} \epsilon_p^{QP}\right)^2 + \left(\operatorname{Im} \epsilon_p^{QP}\right)^2}\right.\\
& \left. + \sum_{i\nu} \frac{\left(\operatorname{Re} Z_{pi\nu}^{sat}\right)\left(\operatorname{Im} \epsilon_{pi\nu}^{sat}\right) + \left(\operatorname{Im} Z_{pi\nu}^{sat}\right)\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat}\right)}{\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat}\right)^2 + \left(\operatorname{Im} \epsilon_{pi\nu}^{sat}\right)^2} + \ldots \right]
\end{align}
\subsection{Annotation of CC Cumulant Green's function paper}
\subsubsection{Cumulant from second order self-energy}
The second order self-energy, which uses a HF reference, can be written as
\begin{align}
\Sigma_{pq}^{(2)}(\omega) =& \frac{1}{2} \sum_{iab} \frac{\langle pi || ab \rangle \langle ab || qi \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \frac{1}{2} \sum_{ija} \frac{\langle pa || ij \rangle \langle ij || qa \rangle}{\omega + \epsilon_a - \epsilon_i - \epsilon_j} \\
\implies \Sigma_{pp}^{(2)}(\omega+\epsilon_p) =&
\frac{1}{2} \sum_{iab}
\frac{\left< pi \left| \right| ab \right>^2}
{\omega-\epsilon_{pi}^{ab}} + \frac{1}{2} \sum_{ija}
\frac{\left< pa \left| \right| ij \right>^2}
{\omega-\epsilon_{pa}^{ij}}
\end{align}
where
$\epsilon_{pi}^{ab} = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i}$
and
$\epsilon_{pa}^{ij} = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}$. So we can write the diagonal cumulant\footnote{ 
Note that in order to get from eqn.~\ref{eq:cumulant_2nd_1} to eqn.~\ref{eq:cumulant_2nd} we have used the identity $\int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon\right)} = \frac{1}{\epsilon^2} \left(e^{-i \epsilon t} +i \epsilon t -1 \right) \mathrm{sgn}(t)$, and since we are dealing with retarded quantities, we only care about $t>0$ so $\mathrm{sgn}(t) = 1$.} as
\begin{align}
C_{pp}(t) &\equiv i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}^c\left(\omega+\epsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t} \\
\implies C_{pp}^{(2)}(t) &= \frac{1}{2} \sum_{iab} \left< pi \left| \right| ab \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pi}^{ab}\right)} + \frac{1}{2} \sum_{ija} \left< pa \left| \right| ij \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pa}^{ij}\right)} 
\label{eq:cumulant_2nd_1}
\\
&= \frac{1}{2}\sum_{iab} \frac{\left< pi \left| \right| ab \right>^2}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
+\frac{1}{2}\sum_{ija} \frac{\left< pa \left| \right| ij \right>^2}{\left(\epsilon_{pa}^{ij}\right)^2}
\left(e^{-i \epsilon_{pa}^{ij} t} +i \epsilon_{pa}^{ij} t -1 \right) 
\label{eq:cumulant_2nd}
\\
&= \frac{1}{2} \sum_{i a b}\langle p i \| a b\rangle^2 f\left(\epsilon_{p i}^{a b}\right)+\frac{1}{2} \sum_{i j a}\langle p a \| i j\rangle^2 f\left(\epsilon_{p a}^{i j}\right)\\
&= \int d\omega\, \beta(\omega) f(\omega)
\end{align}
where $f(\omega) \equiv \frac{e^{-i \omega t}+i \omega t-1}{\omega^2} $ and we identify the cumulant kernel as
\footnote{To get from eqn.~\ref{eq:beta_def} to eqn.~\ref{eq:beta_2nd}, we have used the identity $\operatorname{Im} \frac{1}{x + i \eta} = -\pi \delta(x)$ as $\eta \to 0^+$.}
\begin{align}
    \beta(\omega) &= -\frac{1}{\pi} \operatorname{Im} \Sigma_{pp}^{(2)}\left(\omega+\epsilon_p\right) 
\label{eq:beta_def}\\
\\
&=\frac{1}{2} \sum_{i a b}\langle p i \| a b\rangle^2 \delta\left(\omega-\epsilon_{p i}^{a b}\right)+\frac{1}{2} \sum_{i j a}\langle p a \| i j\rangle^2 \delta\left(\omega-\epsilon_{p a}^{i j}\right) \label{eq:beta_2nd}
\end{align}
A connection can be made between the cumulant kernel $\beta(\omega)=\sum_q g_q^2 \delta(\omega-\omega_q)$ for the 2nd-order self energy  to that for electrons coupled to
bosonic excitations at the frequencies $\omega_q\equiv \epsilon_{pq}^{rs}$ in the quasi-boson approximation
with coupling coefficients $g_q \equiv \langle p q \| r s\rangle$.
\subsubsection{Equivalence between the second order self-energy and the CC retarded Green's function}
When both the IP and EA branches are included, the CC GF can be written in frequency space as
\footnote{A diagrammatic analysis shows that only three non-zero terms when $p, q \in o c c$ survive, which allows us to move from eqn.~\ref{eq:ccgf_expanded_2} to eqn.~\ref{eq:ccgf_expanded_3}.}
\begin{tcolorbox}
    The retarded single-particle Green's function in the time domain is defined as
\begin{equation}
    G_{pq}^R(t-t') = -i \, \Theta(t-t') 
    \langle 0 | \{ a_p(t), a_q^\dagger(t') \} |0\rangle .
\label{spgf}
\end{equation}

Fourier transforming and inserting a resolution of identity over $(N\!\pm\!1)$-electron eigenstates gives the Lehmann representation for both the IP and EA parts:
\begin{align}
    G_{pq}^R(\omega) 
    &= \sum_n \frac{ \langle 0 | a_p(t) | n^{N+1} \rangle \langle n^{N+1} | a_q^\dagger(t') |0\rangle }
      {\omega - (E_n^{N+1} - E_0^N) + i\delta} 
    + \sum_m \frac{ \langle 0 | a_q^\dagger(t') | m^{N-1} \rangle \langle m^{N-1} | a_p(t) |0\rangle }
      {\omega + (E_m^{N-1} - E_0^N) + i\delta}.
\end{align}

In coupled-cluster theory, the exact, correlated ground state can be written as $|\Psi_0\rangle = e^T |\Phi\rangle$ and $\langle \Psi_0| = \langle \Phi | (1+\Lambda) e^{-T}$ and defining the similarity-transformed operators
\begin{equation}
    \bar{H}_N = e^{-T} H_N e^{T}, \qquad
    \bar{a}_p(t) = e^{-T} a_p(t) e^{T}, \qquad
    \bar{a}_q^\dagger(t') = e^{-T} a_q^\dagger(t') e^{T}.
\end{equation}

we can write
\begin{align}
    G_{pq}^R(\omega) 
    &= \langle \Phi | (1+\Lambda)\,
    \bar{a}_q^\dagger(t') \,
    \frac{1}{\omega + i\delta + \bar{H}_N} \,
    \bar{a}_p(t)
    |\Phi\rangle
    + \langle \Phi | (1+\Lambda)\,
    \bar{a}_p(t) \,
    \frac{1}{\omega + i\delta - \bar{H}_N} \,
    \bar{a}_q^\dagger(t')
    |\Phi\rangle .
\end{align}
Now, if we start again with Eqn.~\ref{spgf} and decide just to consider the retarded Green's function for one core orbital $c$, it is just diagonal and reads
\begin{align}
    G_{c}^{R}(t) & = -i \Theta(t) e^{iE_0t} \left<0\left| a_c e^{-iHt} a_c^\dagger \right| 0 \right> -i \Theta(t) e^{-iE_0t}\left<0\left| a_c^\dagger e^{iHt} a_c \right| 0 \right> \\
    & = -i \Theta(t) e^{-iE_0t}\left<N-1\left| e^{iHt} \right| N-1 \right>
\end{align}
Note that we could only do this because we were able to make the separable approximation to the ground state $\left| 0 \right> \simeq a_c^\dagger \left| N-1 \right>$, where $\left| N-1 \right>$ is the exact $N-1$ wavefunction with the core electron separated from it. We are just able to make this approximation for core states because they are localized and thus weakly correlated, so their removal won't relax the exact wavefunction too much. This is not the case for valence states, which are highly correlated, so the separable approximation would not make sense.
\end{tcolorbox}
\begin{align}
G_{pq}^R (\omega) &= \left\langle \Phi \left| (1+\Lambda) \bar{a^{\dagger}_q}
(\omega + \bar{H}_N + i\delta)^{-1} \bar{a_p} \right| \Phi \right\rangle + \left\langle \Phi \left| (1+\Lambda) \bar{a_p}
(\omega - \bar{H}_N + i\delta)^{-1} \bar{a^{\dagger}_q} \right| \Phi \right\rangle \\
&= \langle\Phi|\left(1+\Lambda_2\right)\left(a_q^{\dagger}+\left(a_q^{\dagger} T_2\right)_C\right) X_p(\omega)|\Phi\rangle+\langle\Phi|\left(1+\Lambda_2\right)\left(a_p+\left(a_p T_2\right)_C\right) Y_q(\omega)|\Phi\rangle \label{eq:ccgf_expanded_2}\\
&= \langle\Phi| a_q^{\dagger} X_{1, p}(\omega)|\Phi\rangle+\langle\Phi| \Lambda_2\left(a_q^{\dagger} T_2\right)_C X_{1, p}(\omega)|\Phi\rangle+\langle\Phi| \Lambda_2 a_p Y_{2, q}(\omega)|\Phi\rangle \label{eq:ccgf_expanded_3} \\
&= x^q(\omega)_p-\frac{1}{2} \sum_{i j a b} \lambda_{i j}^{a b} t_{a b}^{q j} x^i(\omega)_p-\frac{1}{2} \sum_{i a b} \lambda_{p i}^{a b} y_{a b}^i(\omega)_q
\end{align}
where to get eqn.~\ref{eq:ccgf_expanded_2} we limited the CC expansion to doubles, i.e. $T\approx T_2=\frac{1}{4} \sum_{i j a b} t_{i j}^{a b} a_a^{\dagger} a_b^{\dagger} a_j a_i$ and $\Lambda\approx\Lambda_2=\frac{1}{4} \sum_{i j a b} \lambda_{i j}^{a b} a_i^{\dagger} a_j^{\dagger} a_b a_a$, and expanded the $\bar{a}_p = a_p + [a_p,T_2]$ and $\bar{a}_q^{\dagger} = a_q^{\dagger} + [a_q^{\dagger},T_2]$ operators into their connected forms. We also defined the $X_p(\omega)\equiv (\omega + \bar{H}_N + i\delta)^{-1} \bar{a_p}$ and $Y_q(\omega)\equiv (\omega - \bar{H}_N + i\delta)^{-1} \bar{a_q}^{\dagger}$ operators that have the components
\begin{align}
    X_p(\omega) & =\sum_i x^i(\omega)_p a_i+\frac{1}{2!} \sum_{i j, a} x_a^{i j}(\omega)_p a_a^{\dagger} a_j a_i=X_{1, p}(\omega)+X_{2, p}(\omega) \\
Y_q(\omega) & =\sum_a y_a(\omega)_q a_a^{\dagger}+\frac{1}{2!} \sum_{i, a b} y_{a b}^i(\omega)_q a_a^{\dagger} a_b^{\dagger} a_i=Y_{1, q}(\omega)+Y_{2, q}(\omega)
\end{align}
\emph{This seems similar to second RPA theory, probably because it is.}
At this point, we can form a perturbation series defined by a perturbation parameter $\xi$, e.g. $t_{p q}^{r s}=t_{p q}^{(0) r s}+\xi t_{p q}^{(1) r s}+\xi^2 t_{p q}^{(2) r s}$, etc. By keeping only terms up to second order we get:
\begin{align}
G_{p q}^{(2)R}(\omega) &= x^{(2) q}(\omega)_p-\frac{1}{2} \sum_{i j a b} \lambda_{i j}^{(1) a b} t_{a b}^{(1) q j} x^{(0) i}(\omega)_p-\frac{1}{2} \sum_{i a b}\left(\lambda_{p i}^{(1) a b} y_{a b}^{(1) i}(\omega)_q+\lambda_{p i}^{(2) a b} y_{a b}^{(0) i}(\omega)_q\right) \\
&= x^{(0) p}(\omega)_p \delta_{p q}+x^{(2) q}(\omega)_p-\frac{1}{2} \sum_{i a b} \lambda_{p i}^{(1) a b}\left(t_{a b}^{(1) q i} x^{(0) p}(\omega)_p+y_{a b}^{(1) i}(\omega)_q\right) \\
&= \frac{\delta_{pq}}{(\omega-\epsilon_p)} + \frac{1}{(\omega-\epsilon_p)} \left[ \frac{1}{2}\sum_{ija} \frac{v^{qa}_{ij}v^{pa}_{ij}}{(\omega+\epsilon_a-\epsilon_i-\epsilon_j)} + \frac{1}{2}\sum_{iab} \frac{v^{pi}_{ab}v^{qi}_{ab}}{(\omega+\epsilon_i-\epsilon_a-\epsilon_b)} \right] \frac{1}{(\omega-\epsilon_q)} \\
&\equiv G_{pq}^{R(0)} (\omega) + G_{pq}^{R(0)} (\omega) \Sigma_{pq}^{(2)}(\omega) G_{pq}^{R(0)} (\omega)
\end{align}
 where we used the simplifications $x^{(1) q}(\omega)_p=0$ and $x^{(0) q}(\omega)_p=x^{(0) p}(\omega)_p \delta_{p q}$ and in the perturbation analysis, we identified that $G_{p q}^{(0) R}(\omega)=x^{(0) q}(\omega)_p= \frac{1}{(\omega-\epsilon_q)}$.
% Here we skip the derivation of each of the coefficients in term of the two-particle integrals and HF eigenvalues and simply list expressions:
% $$
% \begin{gathered}
% x^{(0) p}(\omega)_p=\frac{1}{\left(\omega-\epsilon_p\right)} \\
% x^{(2) q}(\omega)_p=\frac{1}{2\left(\omega-\epsilon_q\right)}\left[\sum_{i j a} v_{i j}^{q a} x_a^{(1) i j}(\omega)_p+\frac{1}{\left(\omega-\epsilon_p\right)} \sum_{i a b} v_{a b}^{p i} t_{a b}^{(1) q i}\right] \\
% x_a^{(1) i j}(\omega)_p=\frac{v_{p a}^{i j}}{\left(\omega-\epsilon_p\right)\left(\omega+\epsilon_a-\epsilon_i-\epsilon_j\right)} \\
% t_{a b}^{(1) i j}=\lambda_{i j}^{(1) a b}=\frac{v_{a b}^{i j}}{\left(\epsilon_i+\epsilon_j-\epsilon_a-\epsilon_b\right)}=\frac{v_{a b}^{i j}}{\epsilon_{a b}^{i j}} \\
% x_a^{(1) i j}(\omega)_p=\frac{v_{p a}^{i j}}{\left(\omega-\epsilon_p\right)\left(\omega+\epsilon_a-\epsilon_i-\epsilon_j\right)}
% \end{gathered}
% $$
% \begin{align}
% \implies G_{pq}^{R(2)} (\omega) &= \frac{\delta_{pq}}{(\omega-\epsilon_p)} + \frac{1}{(\omega-\epsilon_p)} \left[ \frac{1}{2}\sum_{ija} \frac{v^{qa}_{ij}v^{pa}_{ij}}{(\omega+\epsilon_a-\epsilon_i-\epsilon_j)} + \frac{1}{2}\sum_{iab} \frac{v^{pi}_{ab}v^{qi}_{ab}}{(\omega+\epsilon_i-\epsilon_a-\epsilon_b)} \right] \frac{1}{(\omega-\epsilon_q)}.
% \end{align}

\subsubsection{Real-time EOM-CC Cumulant GF}
We restrict the discussion to the retarded
core-hole Green's function for a given deep core level $p=c$, $G^R_c=G_{cc}$
given by
\begin{align}
G_{c}^{R}(t) &= -i \Theta(t-t')
\left<0\left| \left\{a_c(t), a_c^\dagger(t') \right\} \right| 0 \right>\\
&= -i \Theta(t) 
  e^{iE_0t} \left<0\left| a_c e^{-iHt} a_c^\dagger \right| 0 \right> + -i \Theta(t) 
e^{-iE_0t}\left<0\left| a_c^\dagger e^{iHt} a_c \right| 0 \right> \\
&= -i \Theta(t) 
  e^{iE_0t} \left<N-1\left| a_c a_c e^{-iHt} a_c^\dagger a_c^\dagger \right| N-1 \right> + -i \Theta(t) 
e^{-iE_0t}\left<N-1\left| a_c a_c^\dagger e^{iHt} a_c a_c^\dagger \right| N-1 \right> \\
&= -i \Theta(t) 
  e^{-iE_0t}\left<N-1\left| e^{iHt} \right| N-1 \right> \\
&= -i \Theta(t) e^{-iE_0 t} \left<N-1 | N-1, t \right> 
\label{eq:gc_t} 
\end{align}
where we have used the separable approximation to the ground state $\left| 0
\right> \simeq a_c^\dagger \left| N-1 \right>$, which is reasonable for
core excitations. And then at the end we have defined $\left| N-1, t \right> =
e^{iHt} \left| N-1 \right>$, which is a solution to $-i \frac{d\left| N-1, t \right>}{dt} = H \left| N-1, t \right>$. The next step is to assume a time-dependent, CC ansatz for
$\left| N-1, t \right> = N(t) e^{T(t)} \left| \phi \right>$, where $\left| \phi \right> = a_c \left| N \right>$ is the reference determinant with a core hole, $N(t)$ is a \emph{scalar} normalization factor, and $T(t)$ is the time-dependent cluster operator acting only on the $N-1$ electron Fock space. Inserting this ansatz into
the differential equation for $\left| N-1, t \right>$ and left multiplying 
by $e^{-T(t)}$, we obtain the coupled EOM 
\footnote{%
In going eqn.~\ref{de_1} to eqn.~\ref{de_2}, we used:
\begin{align*}
e^{-T(t)}\frac{d}{dt}\left( N(t) e^{T(t)} \right)
&= e^{-T(t)}\left( \dot{N}(t) e^{T(t)} + N(t) \dot{T}(t) e^{T(t)} \right) \\
&= \dot{N}(t) e^{-T(t)} e^{T(t)} + N(t) \left( \dot{T}(t) + \frac{1}{2!} [\dot{T}(t), T(t)] + \frac{1}{3!} [[\dot{T}(t), T(t)], T(t)] + \ldots \right) \\
& \approx \dot{N}(t) + N(t) \dot{T}(t) \\
&= N(t)\left( \frac{\dot{N}(t)}{N(t)} + \dot{T}(t) \right) \\
&= N(t)\left( \frac{d}{dt}\ln N(t) + \dot{T}(t) \right)
\end{align*}
where we have used the Baker-Campbell-Hausdorff expansion and the truncation is consistent with CCSD.
}
\begin{align}
    -i \frac{d\left[N(t) e^{T(t)} \left| \phi \right>\right]}{dt} & = H N(t) e^{T(t)} \left| \phi \right> \\
    -i e^{-T(t)}{\frac{d\left[N(t) e^{T(t)} \right]}{dt}} \left| \phi \right>& = N(t) \underbrace{e^{-T(t)} H e^{T(t)}}_{\bar{H}(t)} \left| \phi \right> 
\label{de_1}\\
    -i N(t) \left( \frac{d\ln N(t)}{dt} + \frac{d T(t)}{dt} \right) \left| \phi \right>& = N(t) \bar{H}(t) \left| \phi \right> 
\label{de_2}
\\
    -i \left( \frac{d\ln N(t)}{dt} + \frac{d T(t)}{dt} \right) \left| \phi \right>& = \left( \bar{H}_N(t) + E^{N-1} \right) \left| \phi \right>
\label{de_3}
\end{align}
 where we have defined a normal-order, similarity transformed Hamiltonian as $\bar{H}_N(t) = \bar{H}(t) - E^{N-1}$, where $E^{N-1} = \left< \phi | \bar{H} | \phi \right>$. Projecting on the reference $\left< \phi \right|$ and excited determinants $\left< \phi_{ij}^{ab} \right|$, respectively, we obtain the coupled EOMs for the normalization factor and the cluster amplitudes, respectively:
\begin{align}
\label{eq-dlnndt}
-i \frac{d \ln N(t)}{dt} = \left< \phi \left| \bar{H}_N(t) \right| \phi \right>
+ E^{N-1} \\
\implies N(t) = e^{i E^{N-1} t} e^{i \int_0^t \left< \phi \left| \bar{H}_N(t') \right| \phi \right> dt'}
\label{eq:nt}
\end{align}
\begin{equation}
\label{eq-dtdt}
-i \left< \phi_{ij...}^{ab...} \left| \frac{d T(t)}{dt} \right| \phi \right> =
\langle \phi_{ij...}^{ab...} \left| \bar{H}_N(t) \right| \phi \rangle.
\end{equation}
In order to further evaluate, we need to introduce some additional approximations. First, we assume that the ground state is uncorrelated, i.e.
$\left| N-1 \right> \simeq a_c \left| \Phi \right> = \left| \phi \right>$,
so that
\begin{equation}
\begin{split}
\left<N-1\right| \left. N-1, t \right> =&
N(t) \left<N-1\left| e^{iHt}\right| \phi \right> \\
=&N(t) \left< \phi \left| \left( 1+ iHt + \frac{(iHt)^2}{2!} + \ldots \right) \right| \phi \right> \\
=&N(t) \left( 1+ \left< \phi \left| R(t) \right| \phi \right> \right) \\
=&N(t).
\end{split}
\end{equation}
where $R(t)$ is the excitation operator that collects all excited terms in the series expansion, so it has expectation value $\left< \phi \left| R(t) \right| \phi \right> = 0$. Now, if we insert eqn.~\ref{eq:nt} into eqn.~\ref{eq:gc_t}, we see that the Green's function is given by
\begin{align}
G_c^R(t) &= -i \Theta(t) e^{-iE_0 t} N(t) \\
&= -i \Theta(t) e^{-i(E_0 - E^{N-1}) t} e^{i \int_0^t \left< \phi \left| \bar{H}_N(t') \right| \phi \right> dt'} \\
&= -i \Theta(t) e^{-i \epsilon_c t} e^{C_c^R(t)}
\label{eq:gc_final}
\end{align}
In the last line, we take $E_0 \equiv E_{HF}$ as the reference energy of the $N$ electron system and so we have $E_0-E^{N-1} \simeq \epsilon_c$, as expected from Koopmans' theorem. And importantly, we have identified the cumulant as
\begin{equation}
\label{eqn:cum_t_f}
C_c^{R}(t) = i \int_0^t \left< \phi \left| \bar{H}_N(t) \right| \phi\right> dt'.
\end{equation}
\begin{tcolorbox}
Now, the known Landau form for the cumulant is
\begin{align}
C_L(t) & = \int d\omega \frac{\beta(\omega)}{\omega^2} \left(e^{-i\omega t} + i\omega t - 1\right) \\
\implies C_L''(t) & = -\int d\omega \beta(\omega) e^{-i\omega t} \\
\end{align}
But now if we do the same thing by differentiating eqn.~\ref{eqn:cum_t_f} twice, we have
\begin{align}
C_c'' (t) & = i \frac{d}{dt} \left< \phi \left| \bar{H}_N(t) \right| \phi \right> \\
\end{align}
So we can identify that
\begin{equation}
\int d\omega \beta(\omega) e^{-i\omega t} = -i \frac{d}{dt} \left< \phi \left| \bar{H}_N(t) \right| \phi \right>
\end{equation}
Taking the inverse Fourier transform, we find a form for the CC cumulant kernel as
\begin{align}
\beta(\omega) &= \frac{1}{2\pi} \int_{-\infty}^{\infty} dt e^{i\omega t} \left[-i \frac{d}{dt} \left< \phi \left| \bar{H}_N(t) \right| \phi \right> \right] \\
&= \frac{1}{\pi} \mathrm{Re} \int_0^{\infty} dt e^{-i\omega t} \left[-i \frac{d}{dt} \left< \phi \left| \bar{H}_N(t) \right| \phi \right> \right]
\end{align}
\color{red}{The above relation is not derived yet.}
\color{black}
 Recall, that in the $GW$+C approach, we had $\beta(\omega)=\frac{1}{\pi}\left|\operatorname{Im} \Sigma_{p p}(\omega+\epsilon_p)\right|$. \emph{Therefore, we can identify that there is a connection, but it is unclear currently how to explore it.}
\end{tcolorbox}
So given the differential equation for the logarithm of the normalization factor in eqn.~\ref{eq-dlnndt} and comparing with eqn.~\ref{eq:gc_final}, we see that the cumulant obeys the differential equation
\begin{equation}
\label{eqn:matel1}
\begin{split}
-i\frac{d C_c^R(t)}{dt} &= \left< \phi \left| \bar{H}_N(t) \right| \phi \right> \\
&= \sum_{ia} f_{ia} t_i^a +
\frac{1}{2} \sum_{ijab} v_{ij}^{ab} t_j^b t_i^a,
\end{split}
\end{equation}
\color{red} {The above relation is not derived yet. Supposedly it requires some tedious
algebra and diagrammatic analysis.} \color{black} We can also use eqn.~\ref{eq-dtdt} to write the equation of motion for the cluster amplitudes, where for the singles, it is given by
% \begin{equation}
% \label{eq:rt_eom_ccs}
% -i \dot {t}_i^a(t) = \left< \phi_{i}^{a} \left| \frac{d T(t)}{dt} \right| \phi \right>
% = \left< \phi_{i}^{a} \right| \bar{H}_N(t) \left| \phi \right>.
% \end{equation}
% but shouldn't this be
\begin{equation}
\label{eq:rt_eom_ccs}
-i \dot {t}_i^a(t) \equiv -i \left< \phi_{i}^{a} \left| \frac{d T(t)}{dt} \right| \phi \right>
= \left< \phi_{i}^{a} \right| \bar{H}_N(t) \left| \phi \right>.
\end{equation}
I choose to not continue further for now.
\subsection{Annotating Noojien DSO-GF paper}
In the supermatrix formulation, MP2 tells us that we have to diagonalize:
\begin{align}
A_{p q}^{\text {MP2 }}(\omega)= & \epsilon_{p} \delta_{p q}+\Sigma_{p q}^{(2)}(\omega) \\
= & \epsilon_{p} \delta_{p q}+\frac{1}{2} \sum_{l, c, d} \frac{V_{p l[c d]} V_{c d[q l]}}{\omega+\epsilon_{l}-\epsilon_{c}-\epsilon_{d}}
-\frac{1}{2} \sum_{k, l, d} \frac{V_{p d[k l]} V_{k l[q d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega}
\end{align}
whereas in their diagonal second-order Green's function (DSO-GF) approach, they diagonalize:
\begin{align}
A_{i j}^{\mathrm{DSO}-\mathrm{GF}}(\omega)=& U_{i j}-\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} W_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega} \\
= & \epsilon_{i} \delta_{ij}+\sum_{c, d, l} V_{i l c d}\left(2 t_{j l}^{c d}-t_{j l}^{d c}\right) -\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} V_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega} \\
% = & \epsilon_{i} \delta_{ij}+\sum_{c, d, l} V_{i l c d}\left(t_{j l}^{c d}\right) -\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} V_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega} \\
% = & \epsilon_{i} \delta_{ij}+\sum_{c, d, l} \Biggl(\left< i l | cd\right> - \left< il |dc\right>\Biggr)\Biggl(2 \frac{\Bigl(\left< cd | jl\right> - \left< cd |lj\right>\Bigr)}{\epsilon_{j}+\epsilon_{l}-\epsilon_{c}-\epsilon_{d}} - \frac{\Bigl(\left< dc | jl\right> - \left< dc|lj\right>\Bigr)}{\epsilon_{j}+\epsilon_{l}-\epsilon_{c}-\epsilon_{d}}\Biggr)\\
% & -\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} V_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega} \\
= & \epsilon_{i} \delta_{i j}+\frac{1}{2} \sum_{l, c, d} V_{i l[c d]} t_{j l}^{[c d]}  -\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} V_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega} \\
= & \epsilon_{i} \delta_{i j}+\frac{1}{2} \sum_{l, c, d} V_{i l[c d]} \frac{V_{c d[j l]}}{\epsilon_{j}+\epsilon_{l}-\epsilon_{c}-\epsilon_{d}} -\frac{1}{2} \sum_{k, l, d} \frac{W_{i d[k l]} V_{k l[j d]}}{\epsilon_{k}+\epsilon_{l}-\epsilon_{d}-\omega}
\end{align}
where the CC doubles amplitudes are replaced by MBPT(2) values:
\begin{align*}
& t_{i j}^{a b}=\frac{V_{a b i j}}{\epsilon_{i}+\epsilon_{j}-\epsilon_{a}-\epsilon_{b}}
\end{align*}
and $V_{a b i j}$ denotes a nonantisymmetrized two-electron integral in "1212" notation and the $\epsilon_{p}$ denote canonical Hartree-Fock orbital eigenvalues. The brackets indicate antisymmetrization. 

% intermediates
% \begin{align*}
% & U_{k i}=\epsilon_{i} \delta_{k i}+\sum_{c, d, l} V_{k l c d}\left(2 t_{i l}^{c d}-t_{i l}^{d c}\right),  \tag{5}\\
% & U_{a c}=\epsilon_{a} \delta_{a c}-\sum_{k, l, d} V_{k l c d}\left(2 t_{k l}^{a d}-t_{l k}^{a d}\right), \\
% & W_{k l i d}=V_{k l i d}, \\
% & W_{k a c i}=V_{k a c i}+\sum_{l, d} V_{k l c d}\left(2 t_{i l}^{a d}-t_{l i}^{a d}\right)-\sum_{l, d} V_{k l d c} t_{i l}^{a d}, \\
% & W_{k b i d}=V_{k b i d}-\sum_{c, l} V_{k l c d} t_{i l}^{c b},  \tag{6}\\
% & W_{k l i j}=V_{k l i j}+\sum_{c, d} V_{k l c d} t_{i j}^{c d}, \\
% & W_{k b i j}=V_{k b i j}+\sum_{l, d} V_{k l i d}\left(2 t_{l j}^{d b}-t_{j l}^{d b}\right)-\sum_{l, d} V_{l k i d} t_{l j}^{d b} \\
% & \quad+\sum_{c, d} V_{b k d c} t_{j i}^{d c}-\sum_{l, c} V_{l k j c} t_{l i}^{b c} .
% \end{align*}
% and also we have







\section{Cumulant expansion for electron-phonon interactions}
\subsection{Annotating PJ's SC-CE paper}
\label{sec:pj_ce}
 The time-ordered form of the electron Green's function for one electron can be written as the power series expansion of an exponential ansatz
\begin{align}
\mathcal{G}_k(t)&=\mathcal{G}_k^{(0)}(t)\left\langle a_k T e^{-i \int_0^t d \tau V({\tau})} a_k^\dag\right\rangle
\label{6.5}\\
&=\mathcal{G}_k^{(0)}(t)\left\langle T e^{-i \int_0^t d \tau V({\tau})}\right\rangle \\
&=\mathcal{G}_k^{(0)}(t) \left\langle \sum_{n=0}^{\infty} \frac{(-i)^n}{n!} \int_0^t d t_1 \cdots \int_0^t d t_n T\left[V ( t _ { 1 } ) \cdots V \left(t_n\right)\right] \right\rangle \\
% &=\mathcal{G}_k^{(0)}(t) \left\langle \sum_{n=0}^{\infty} \frac{(-i)^n}{n!} \int_0^t d t_1 \cdots \int_0^t d t_n T\left[ V\left(t_j\right)\right] \right\rangle \\
&=\mathcal{G}_k^{(0)}(t) \left\langle \sum_{n=0}^{\infty} \frac{(-i)^n}{n!} \int_0^t d t_1 \cdots \int_0^t d t_n T\left[\prod_{j=1}^n \sum_{q_j} g_{q_j, k_j} a_{k_j+q_j}^{\dagger}\left(t_j\right) a_{k_j}\left(t_j\right) A_{q_j}\left(t_j\right)\right] \right\rangle \\
&=\mathcal{G}_k^{(0)}(t) \left\langle \sum_{n=0}^{\infty} T \left[\frac{(-i)^n}{n!} \int_0^t d t_1 \cdots \int_0^t d t_n \prod_{j=1}^n \sum_{q_j} g_{q_j, k_j} a_{k_j+q_j}^{\dagger} a_{k_j}e^{-it_j(\epsilon_{k_j}-\epsilon_{k_j + q_j})} A_{q_j}\left(t_j\right)\right] \right\rangle 
\end{align}
where $k_j = k + \sum_{i=j+1}^n q_i$ and $\sum_i q_i=0$. The interpretation of the above expression is that the electron starts in state $k$ at time $0$, and then scatters off $n$ phonons, each with momentum $q_j$, before returning to state $k$ at time $t$. $A_q(t)=b_q e^{-i \omega_q t}+b_{-q}^\dagger e^{i \omega_q t}$, where $b_q$ and $b_q^\dagger$ are the annihilation and creation operators for a phonon of momentum $q$ and frequency $\omega_q$ with $[b_q, b_{q^{\prime}}^{\dagger}]=\delta_{q q^{\prime}}$. If we define the vertex operator $\Gamma_{q k}(t)=g_{q k} e^{-i t \epsilon_k} e^{q \cdot \frac{d}{d k}} e^{i t \epsilon_k}$ we can rewrite the electron Green's function as an exponential,
\begin{equation}
\mathcal{G}_k(t)=\mathcal{G}_k^{(0)}(t)\left\langle T e^{-i \sum_q \int_0^t d \tau \Gamma_{q k}(\tau) A_q(\tau)}\right\rangle
\end{equation}
 where the remaining trace is only over the bosonic degrees of freedom. Assuming harmonic bosons, we can use $\left\langle e^B \right\rangle = e^{\left\langle B^2\right\rangle / 2}$ with the definition
\begin{equation}
    B=-i \sum_q \int_0^t d \tau \Gamma_{q k}(\tau) A_q(\tau)
\end{equation}
where our $B$ is linear in the bosonic operators $A_q$, so the identity applies. Then, 
\begin{align}
\left\langle T e^S\right\rangle & \equiv \left\langle T e^B\right\rangle = \exp\left(\frac{1}{2}\left\langle T B^2\right\rangle\right) \\
\implies S & =\frac{1}{2}\left\langle T B^2\right\rangle \\
& =\frac{1}{2}(-i)^2 \sum_{q q^{\prime}} \int_0^t d \tau \int_0^t d \tau^{\prime} \Gamma_{q k}(\tau) \Gamma_{q^{\prime} k}\left(\tau^{\prime}\right)\left\langle T A_q(\tau) A_{q^{\prime}}\left(\tau^{\prime}\right)\right\rangle \\
& =-\frac{1}{2} \sum_{q q^{\prime}} \int_0^t d \tau \int_0^t d \tau^{\prime} \Gamma_{q k}(\tau) \Gamma_{q^{\prime} k}\left(\tau^{\prime}\right)\left[i D_q^{(0)}\left(\tau-\tau^{\prime}\right) \delta_{q,-q^{\prime}}\right] \\
& = -i \sum_q \int_0^t d \tau \int_0^t d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \Gamma_{-q k}(\tau) \Gamma_{q k}\left(\tau^{\prime}\right) 
\end{align}
To find a self consistent expression for $S$, we use the Feynman operator ordering theorem, which states that given a functional of time-dependent operators $F[\hat{A}(\tau), \hat{B}(\tau), \ldots]$ with $\tau \in[0, t]$, which in our case is $e^{S[\Gamma (\tau)]}$, and with a unitary operator of the form $\hat{U}\left(\tau^{\prime}\right)=T \exp \left[\int_0^{\tau^{\prime}} d \tau \hat{P}(\tau)\right]$, then
\begin{equation}
\hat{U}(t) F[\hat{A}(\tau), \hat{B}(\tau), \ldots] =T\left[\exp \left(\int_0^t d \tau \hat{P}(\tau)\right) F\left[\hat{U}(\tau) \hat{A}(\tau) \hat{U}^{-1}(\tau), \ldots\right]\right] .
\end{equation}
We choose $\hat{P}(\tau)=-i\left[\epsilon_k+\frac{d}{d \tau} \phi_k(\tau)\right]$ and
so the transformed $S$ is given by
\begin{align}
    \bar{S}
&= -i \int_0^t d \tau\left(\epsilon_k+\frac{d}{d \tau} \phi_k(\tau)\right) -i \sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \bar{\Gamma}_{-q k}(\tau) \bar{\Gamma}_{q k}\left(\tau^{\prime}\right)
\end{align}
with the transformed vertex operators $\bar{\Gamma}_{q k}(\tau)\equiv  \hat{U}(\tau)\Gamma_{q k}(\tau)\hat{U}^{-1}(\tau)=g_{q k} e^{-i \phi_k(\tau)} e^{q \cdot \frac{d}{d k}} e^{+i \phi_k(\tau)}$. The Green's function can then be written as
\begin{align}
    \mathcal{G}_k(t)&=i\Theta(t) e^{i \phi_k(t)} T \left[\exp (-i \int_0^t d \tau(\epsilon_k+\frac{d}{d \tau} \phi_k(\tau)))\right. \\
& \left.\times \exp \left(-i \sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \bar{\Gamma}_{-q k}(\tau) \bar{\Gamma}_{q k}\left(\tau^{\prime}\right)\right)\right] \notag \\
&=i\Theta(t) e^{i \phi_k(t)} \exp\left(\sum_{n=1}^{\infty} \frac{1}{n!} T\left[\bar{S}^n\right]_c\right) \\
&=i\Theta(t) e^{C_k(t)}
\end{align}
where
\begin{equation}
    C_k(t)=i\phi_k(t) + \sum_{n=1}^{\infty} \frac{1}{n!} T\left[\bar{S}^n\right]_c
\label{a7}
\end{equation}
where the notation $[\cdot \cdot \cdot]_c$ denotes the cumulant of an operator, and $T[\bar{S}]_c=T[\bar{S}]$ with subsequent terms given by $T\left[\bar{S}^n\right]_c=T\left[\bar{S}^n\right]-\sum_{m=1}^{n-1} \frac{(n-1)!}{m!(n-m-1)!} T\left[\bar{S}^m\right] T\left[\bar{S}^{n-m}\right]_c$. Then, evaluating \ref{a7} with $\phi_k(t)=C_k(t)$ to leading order produces
\begin{align}
    C_k(t)&=-i \epsilon_k t - i \frac{g^2}{N}\sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) e^{-C_k(\tau)+C_{k-q}(\tau)-C_{k-q}\left(\tau^{\prime}\right)+C_k\left(\tau^{\prime}\right)} \label{12} \\
\implies \dot{C}_k(t)&=-i \epsilon_k - i \frac{g^2}{N} \sum_q \int_0^t d \tau D_q^{(0)}(t-\tau) e^{-C_k(t)+C_{k-q}(t)-C_{k-q}(\tau)+C_k(\tau)} \label{13}
\end{align}
with the bare phonon propagator $D_q^{(0)}(t)= -i\left[\left(1+N_q\right) e^{-i \omega_q|l|}+N_q e^{\left|\omega_q\right| l \mid}\right]$ and the Bose occupation factor $N_q=\left[\exp \left(\beta \omega_q\right)-1\right]^{-1}$.  Eqn~\ref{12} can be recast as a self-consistent equation for the interacting Green's function by considering
\begin{align}
\frac{d \mathcal{G}_k(t)}{d t}&= \frac{d}{d t}\left[-i \Theta(t) e^{C_k(t)}\right] \\
&= \dot{C_k}(t) \mathcal{G}_k(t) \\
&= -i \epsilon_k \mathcal{G}_k(t) - i \frac{g^2}{N} \sum_q \int_0^t d \tau \mathcal{G}_k(t) D_q^{(0)}(t-\tau) e^{-C_k(t)+C_{k-q}(t)-C_{k-q}(\tau)+C_k(\tau)} \\
&= -i \epsilon_k \mathcal{G}_k(t) - i \frac{g^2}{N} \sum_q \int_0^t d \tau \mathcal{G}_k(t) D_q^{(0)}(t-\tau) \frac{\mathcal{G}_{k-q}(t) \mathcal{G}_k(\tau)}{\mathcal{G}_{k-q}(\tau) \mathcal{G}_k(t)} \\
&=-i \epsilon_k \mathcal{G}_k(t) - i \frac{g^2}{N} \sum_q \int_0^t d \tau D_q^{(0)}(t-\tau) \frac{\mathcal{G}_k(\tau) \mathcal{G}_{k-q}(t)}{\mathcal{G}_{k-q}(\tau)}\label{a9}\\
\implies \frac{1}{\mathcal{G}_k(t)} \frac{d \mathcal{G}_k(t)}{d t}&={-i \epsilon_k} - i \frac{g^2}{N} \sum_q \int_0^t d \tau D_q^{(0)}(t-\tau) \frac{\mathcal{G}_{k-q}(t)}{\mathcal{G}_{k-q}(\tau)} \frac{\mathcal{G}_k(\tau)}{\mathcal{G}_k(t)} \label{a8} \\
\implies \frac{d \ln \mathcal{G}_k(t)}{d t}-\frac{d \ln \mathcal{G}_k^{(0)}(t)}{d t}&=- i \frac{g^2}{N} \sum_q \int_0^t d \tau D_q^{(0)}(t-\tau) \frac{\mathcal{G}_{k-q}(t)}{\mathcal{G}_{k-q}(\tau)} \frac{\mathcal{G}_k(\tau)}{\mathcal{G}_k(t)} \\
\implies \frac{d \ln \left[\mathcal{G}_k(t) / \mathcal{G}_k^{(0)}(t)\right]}{d t}&=- i \frac{g^2}{N} \sum_q \int_0^t d \tau D_q^{(0)}(t-\tau) \frac{\mathcal{G}_{k-q}(t)}{\mathcal{G}_{k-q}(\tau)} \frac{\mathcal{G}_k(\tau)}{\mathcal{G}_k(t)} \\
\implies ln \left[\mathcal{G}_k(t) / \mathcal{G}_k^{(0)}(t)\right] &=- i \frac{g^2}{N} \sum_q \int_0^t d \sigma \int_0^\sigma d \tau D_q^{(0)}(\sigma-\tau) \frac{\mathcal{G}_{k-q}(\sigma)}{\mathcal{G}_{k-q}(\tau)} \frac{\mathcal{G}_k(\tau)}{\mathcal{G}_k(\sigma)} \\
\implies \mathcal{G}_k(t) &=\mathcal{G}_k^{(0)}(t) \exp \left[i \sum_q \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) \frac{\mathcal{G}_{k-q}(\sigma)}{\mathcal{G}_{k-q}(\tau)} \frac{\mathcal{G}_k(\tau)}{\mathcal{G}_k(\sigma)}\right] \\
\implies \mathcal{G}_k^{(n+1)}(t)
&=\mathcal{G}_k^{(0)}(t)
\exp\!\left[
i\!\sum_q
\int_0^t d\sigma\!\!\int_0^\sigma d\tau\,
\left|g_{q k}\right|^2 D_q^{(0)}(\sigma\!-\!\tau)
\frac{\mathcal{G}_{k-q}^{(n)}(\sigma)}{\mathcal{G}_{k-q}^{(n)}(\tau)}
\frac{\mathcal{G}_k^{(n)}(\tau)}{\mathcal{G}_k^{(n)}(\sigma)}
\right]
\end{align}
where the last equation admits a form for an iterative solution of this self-consistent equation. For $n=0$, we insert the bare Green's function, and get the second order cumulant,
\begin{align}
    \mathcal{G}_k^{(1)}(t)&=\mathcal{G}_k^{(0)}(t) \exp \left[i \sum_q \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) \frac{\mathcal{G}_{k-q}^{(0)}(\sigma)}{\mathcal{G}_{k-q}^{(0)}(\tau)} \frac{\mathcal{G}_k^{(0)}(\tau)}{\mathcal{G}_k^{(0)}(\sigma)}\right] \\
&=\mathcal{G}_k^{(0)}(t) \exp \left[i \sum_q \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) e^{-i\left(\epsilon_{k-q}-\epsilon_k\right)(\sigma-\tau)}\right] \\
&\equiv\mathcal{G}_k^{(0)}(t) \exp \left[C_2(k, t)\right]
\end{align}
For $n=1$, we have
\begin{align}
    \mathcal{G}_k^{(2)}(t)&=\mathcal{G}_k^{(0)}(t) \exp \left[i \sum_q \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) \frac{\mathcal{G}_{k-q}^{(1)}(\sigma)}{\mathcal{G}_{k-q}^{(1)}(\tau)} \frac{\mathcal{G}_k^{(1)}(\tau)}{\mathcal{G}_k^{(1)}(\sigma)}\right] \label{iterative_step} \\
&=\mathcal{G}_k^{(0)}(t) \exp \left[i \sum_q \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) \frac{\mathcal{G}_{k-q}^{(0)}(\sigma)}{\mathcal{G}_{k-q}^{(0)}(\tau)} \frac{\mathcal{G}_k^{(0)}(\tau)}{\mathcal{G}_k^{(0)}(\sigma)}\right. \notag \\
&\left.\times e^{C_2(k, \tau)+C_2(k-q, \sigma)-C_2(k, \sigma)-C_2(k-q, \tau)}\right] \\
&=\mathcal{G}_k^{(0)}(t) \exp \left[\sum_{n=0}^{\infty} \frac{-i}{n!} \sum_q \int_0^t d \sigma \int_0^\sigma d \tau \left|g_{q k}\right|^2 D_q^{(0)}(\sigma-\tau) \mathcal{G}_{k-q}^{(0)}(\sigma-\tau) \mathcal{G}_k^{(0)}(\tau-\sigma)\right. \label{moment_expansion}\\
& \left.\times\left[C_2(k, \tau)+C_2(k-q, \sigma)-C_2(k, \sigma)-C_2(k-q, \tau)\right]^n\right] \notag \\
&=\mathcal{G}_k^{(0)}(t) \exp \left(\sum_{m=1}^{\infty} C_{2n}^{(2)}(k, t)\right)
\end{align}
where $C_{2n}^{(2)}(k, t)$ is the approximation to the $2n$th cumulant produced by the second iteration.
Because the second iteration produces cumulants of all orders, further iterations require expanding the exponent into moments. For iterations $n \geq 2$, we use
\begin{align}
    \mathcal{G}_{\mathbf{k}}^{(n+1)}(t)= & \mathcal{G}_{\mathbf{k}}^{(0)}(t) \exp \left(-i \sum_{\mathbf{q}} \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2\right. \\
& \left.\times D_{\mathbf{q}}^0(\sigma-\tau) \mathcal{G}_{\mathbf{k}}^{(0)}(\tau-\sigma) \mathcal{G}_{\mathbf{k}-\mathbf{q}}^{(0)}(\sigma-\tau) e^{F^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)}\right) \notag
\end{align}
introducing the notation 
\begin{equation}
    F^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau) = F_2^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)+F_4^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)+\cdots
\end{equation}
where
\begin{equation}
    F_i^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau) = C_i^{(n)}(\mathbf{k}-\mathbf{q}, \sigma)-C_i^{(n)}(\mathbf{k}-\mathbf{q}, \tau) -C_i^{(n)}(\mathbf{k}, \sigma)+C_i^{(n)}(\mathbf{k}, \tau)
\end{equation}
The procedure for constructing the approximation to the $n$th iteration of the $m$th cumulant is given by the moment expansion
\begin{equation}
    \sum_{m=0}^{\infty} \lambda^{2 m} W_{2 m}^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)=\exp \left(\sum_{m=1}^{\infty} \lambda^{2 m} F_{2 m}^{(n)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)\right)
% ^{\sum_{m-1}^{\infty}, \lambda^{2 m}, F_{2 m}^{(2)}(\mathbf{k}, \mathbf{q}, \sigma, \tau)},
\end{equation}
where we can get explicit expressions by matching the orders of $\lambda$ on both sides.
Our experience with equation \eqref{moment_expansion} suggests that each iteration introduces another power of $g^2$ to all of the approximated cumulants, and since the $n$th-order cumulant is defined as being proportional to $g^n$, the $n$th iteration cannot alter any of the approximated cumulants of order lower than $n$. Because of this, and the fact that the approximate cumulant for a given order is an integral over lower-order approximations, the iterative method is actually recursive. So alternatively, we can write
\begin{equation}
    C_{2 n}^{\mathrm{SC}-\mathrm{CE}}(\mathbf{k}, t)= -i \sum_{\mathbf{q}} \int_0^t d \sigma \int_0^\sigma d \tau\left|g_{q k}\right|^2 D_{\mathbf{q}}^{(0)}(\sigma-\tau) \mathcal{G}_{\mathbf{k}}^{(0)}(\tau-\sigma) \mathcal{G}_{\mathbf{k}-\mathbf{q}}^{(0)}(\sigma-\tau) W_{2 n-2}(\mathbf{k}, \mathbf{q}, \sigma, \tau)
\end{equation}
To determine what is actually solved, at this point consider again equation \eqref{a9}, where, if we define $y_k(t)=e^{C_k(t)}$, we can rewrite it as
\begin{align}
\frac{d y_k(t)}{d t}= & -i \sum_q \int_0^t d \tau\left|g_{q k}\right|^2 D_q^{(0)}(t-\tau) e^{i(\epsilon_k-\epsilon_{k-q})(t-\tau)} \frac{y_k(\tau) y_{k-q}(t)}{y_{k-q}(\tau)} \label{C1}
\end{align}
This is a VIDE, which can be solved numerically using the appropriate methods.
\subsection{Annotation of Littlewood's CE paper}
\subsubsection{Power series ansatze}
They use a power series expansion of the cumulant, instead of the usual exponential ansatz. This has the function of making sure that the term involving the $g^{2n}$ EPI constant can only be found in the $n$th-order cumulant. So the retarded Green's function is given by
\begin{equation}
    G(n,t) = G_o(n,t) \mathcal{P}(n,t) = G_o(n,t)\sum_{k=0}^\infty g^{2k} C_k(n,t)
\end{equation}
To properly construct the electron self energy, they replace it by power series ansatz in order to re-introduce self-consistency from the start.
%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{equation}
    \begin{aligned}
        -i\Sigma(t) &= g^2 \sum_{n=\pm}\,\sum_{N= \pm} \mathcal{D}(N,t)\underbrace{G_0(n, t)\mathcal{P}(n,t)}_{G(n,t)}\\
    &=g^2 \sum_{n=\pm}-i\Sigma_0(n,t)\mathcal{P}(n,t)
\end{aligned}
\label{Power corrected self energy}
\end{equation}
where $\Sigma _0(n,t) \equiv -i\mathcal{D}(N,t)G_0(n, t)$.
\subsubsection{Plugging into the Dyson equation}
 Now, we can plug into the temporal Dyson equation:
\begin{align}
G(m,t-t_0) &= G_0(m,t-t_0) + \iint dt_1 dt_2 \, G_0(m,t-t_2) \, \Sigma(t_2-t_1) \, G(m,t_1-t_0)\\
G_0(m,t-t_0) \mathcal{P}(m,t-t_0) &= G_0(m,t-t_0) -ig^2 \sum_{n=\pm}\iint dt_1 dt_2 \, G_0(m,t-t_2) \, \Sigma_0(n, t_2-t_1) \\
&\times \mathcal{P}(n,t_2-t_1) \, G_0(m,t_1-t_0) \, \mathcal{P}(m,t_1-t_0) \notag \\
G_0(m,t) \mathcal{P}(m,t) &= G_0(m,t) -ig^2 \sum_{n=\pm}\iint dt_1 dt_2 \,G_0\left(m, t\right) e^{i \varepsilon_m\left(t_2-t_1\right)}  \, \Sigma_0(n, t_2-t_1) \\
&\times \mathcal{P}(n,t_2-t_1) \mathcal{P}(m,t_1-t_0) \notag \\
\mathcal{P}(m,t) &= 1 -ig^2 \sum_{n=\pm}\int_0^t dt_2 \int_0^{t_2} d\tau e^{i \varepsilon_m \tau}  \, \Sigma_0(n, \tau) \mathcal{P}(n,\tau) \mathcal{P}(m,t_2 - \tau) \notag \\
\end{align}
where in the final line we have defined $\tau = t_2 - t_1$ and set $t_0=0$. Also, the temporal contraction property due to the boundary value dependence on time is used, which is only valid when the diagonal approximation is made.
There are two distinct terms in this equation: a self correction term $P_{SC}$ that occurs when $n=m$ and an inter-band scattering term $P_{IC}$ that occurs when $n\neq m$. The contraction property is valid for the former but not the latter. So\
\begin{equation}
    \mathcal{P}(m,t) =  1 + P_{SC} + P_{IC}
\end{equation}
with
\begin{align}
    P_{SC}&=-ig^2\int\displaylimits_{0}^{t}dt_2 \int\displaylimits_{0}^{t_2}d{\tau}\, e^{i\varepsilon_{m}\tau}\Sigma_0(m,\tau)\mathcal{P}(m,t_2)\\
    P_{IC}&= -ig^2\int\displaylimits_{0}^{t}dt_2 \int\displaylimits_{0}^{t_2}d\tau\, e^{i\varepsilon_{m}\tau} \,\Sigma_0(n,\tau)\mathcal{P}(n,\tau)\mathcal{P}(m,t_2-\tau)
\end{align}
For numerical solution, they start with an initial guess of $\mathcal{P} = 1$ on the right and self consistently compute better values for $\mathcal{P}$ on the left until it converges. It also might be useful to know that we can write
\begin{equation}
    \begin{aligned}
    &C_{k}(m,t) = -i\int\displaylimits_{0}^{t}dt_2 \int\displaylimits_{0}^{t_2}d\tau \Bigg[\!e^{i\varepsilon_m\tau}\, \Sigma_o(m,\tau)C_{k-1}(m,t_2) +\sum_{n\neq m}\sum_{l=0}^{k}  e^{i\varepsilon_{m}\tau}\,\Sigma_o(n,\tau)\,C_{l}(n,\tau)\,C_{k-1-l}(m,t_2-\tau)\Bigg]\\
    \end{aligned}
    \label{recursive equation}
\end{equation}
\subsection{Annotation of Dunn paper}
\subsubsection{Exact identities}
The given Hamiltonian is 
\begin{align}
    H &= \sum_k \epsilon_k a_k^\dagger a_k + \frac{1}{2} \sum_q (P_q^\dagger P_q + \omega_q^2 Q_q^\dagger Q_q) + \sum_{q} \gamma_q Q_q \rho_q^\dagger \\
&= H_{\mathrm{el}} + H_{\mathrm{ph}} + H_{\mathrm{int}} \\
&= \sum_k \epsilon_k a_k^\dagger a_k + \sum_q \omega_q \left(b_q^\dagger b_q + \frac{1}{2}\right) + \sum_{qk} \gamma_q \sqrt{\frac{1}{2\omega_q}} (b_q + b_{-q}^\dagger) a_k^\dagger a_{k+q} \langle k | e^{-i q \cdot r} | k+q \rangle \\
&= \sum_k \epsilon_k a_k^\dagger a_k + \sum_q \omega_q b_q^\dagger b_q + \sum_{qk} g_{qk} (b_q + b_{-q}^\dagger) a_k^\dagger a_{k+q}
\end{align}
where we have introduced bosonic second quantization operators $Q_q= \sqrt{\frac{1}{2 \Omega_q}}\left(b_q+b_{-q}^{\dagger}\right)$ and $P_q=i \sqrt{\frac{\Omega_q}{2}}\left(b_{-q}^{\dagger}-b_q\right)$, which correspond to the position and momentum, respectively, of a harmonic oscillator with frequency $\Omega_q$. The electron density operator is given by $\rho_q=\sum_k a_{k+q}^{\dagger} a_k \langle k+q| e^{i q \cdot r}|k\rangle$, where the matrix element is between Bloch states. The electron-boson coupling constant is then given by $g_{q k}=\gamma_q \sqrt{\frac{1}{2 \Omega_q}}\langle k| e^{-i q \cdot r}|k+q\rangle$. \emph{Garnet started with such an electron boson Hamiltonian to start his AB theory, so maybe we want to do something similar.} Without any interaction, the electron annihilation operator is
\begin{equation}
    a_k(t) = e^{-i \epsilon_k t} a_k
\end{equation}
 In the presence of this interaction, the EOM for the electron annihilation operator is given by
\begin{align}
    \frac{d a_k(t)}{d t} &= -i \epsilon_k a_k(t) - i \sum_q g_{q k} Q_q(t) a_{k+q}(t) \\
\implies a_k(t) &= e^{-i \epsilon_k t} T \exp \left[-i \int_0^t d \tau \sum_q Q_q(\tau) \Gamma_{q k}(\tau)\right] a_k \\
\end{align} 
So the idea is that as time evolves when we are including the interaction, the electronic and bosonic processes become inseparable.
\begin{tcolorbox}
The above is derived. Start by introducing a rotated operator.
\begin{align}
    \tilde{a}_k(t)&=e^{i \epsilon_k t} a_k(t) \\
\implies \frac{d \tilde{a}_k(t)}{d t}&=i \epsilon_k e^{i \epsilon_k t} a_k(t)+e^{i \epsilon_k t} \frac{d a_k(t)}{d t} \\
&=i \epsilon_k e^{i \epsilon_k t} a_k(t)+e^{i \epsilon_k t}\left(-i \epsilon_k a_k(t)-i \sum_q g_{q k} Q_q(t) a_{k+q}(t)\right) \\
&=-i \sum_q g_{q k} e^{i \epsilon_k t} Q_q(t) a_{k+q}(t) \\
&=-i \sum_q g_{q k} Q_q(t) e^{i\left(\epsilon_k-\epsilon_{k+q}\right) t} \tilde{a}_{k+q}(t) \\
&=-i \sum_q g_{q k} Q_q(t) e^{i\left(\epsilon_k-\epsilon_{k+q}\right) t} e^{q \cdot \frac{d}{d k}} \tilde{a}_k(t) \\
&= -i \sum_q Q_q(t) \Gamma_{q k}(t) \tilde{a}_k(t) \\
\implies \tilde{a}_k(t)&=T \exp \left[-i \int_0^t d \tau \sum_q Q_q(\tau) \Gamma_{q k}(\tau)\right] \tilde{a}_k \\
\implies a_k(t)&=e^{-i \epsilon_k t} T \exp \left[-i \int_0^t d \tau \sum_q Q_q(\tau) \Gamma_{q k}(\tau)\right] a_k
\end{align}
where we defined the vertex operator $\Gamma_{q k}(t)=g_{q k} e^{i \epsilon_k t} e^{q \cdot \frac{d}{d k}} e^{-i \epsilon_k t} = g_{q k} e^{i\left(\epsilon_k-\epsilon_{k+q}\right) t} e^{q \cdot \frac{d}{d k}} $, which uses
$f(k+q)=\sum_{n=0}^{\infty} \frac{\left(q \cdot \nabla_k\right)^n}{n!} f(k)=e^{q \cdot \nabla_k} f(k)$ so thatt $e^{q \cdot \frac{d}{d k}}$ can be understood as a translation operator in $k$-space.
\end{tcolorbox}
% \subsubsection{Retarded green's function}
The causal Green's function for a insulator, where the probability of an electron conduction state being occupied is negligible, is
\begin{align}
    G_k(t) &= i \operatorname{Tr}\left[\rho T\left(a_k(t) a_k^\dagger\right)\right] \\
&= i \Theta(t) \operatorname{Tr}\left[\rho a_k(t) a_k^\dagger\right] + i \Theta(-t) \operatorname{Tr}\left[\rho a_k^\dagger a_k(t)\right] \\
&= i \Theta(t) \operatorname{Tr}\left[\rho a_k(t) a_k^\dagger\right] \\
&= i \Theta(t) e^{-i \epsilon_k t} \operatorname{Tr}\left[\rho T \exp \left(-i \sum_q \int_0^t d \tau Q_q(\tau) \Gamma_{q k}(\tau)\right)\right]_0 \quad \text{trace over zero electron states} \\
% &= i \Theta(t) e^{-i \epsilon_k t} \operatorname{Tr}\left[\rho T \left(\exp \left(-i \sum_q \int_0^t d \tau b_q e^{-i \Omega_q \tau} \Gamma_{q k}(\tau)\left(2 \Omega_q\right)^{-1 / 2}\right)\right.\right. \\
&= i \Theta(t) e^{-i \epsilon_k t} \operatorname{Tr}\left[\rho T \left(\exp \left(-i \sum_q \int_0^t d \tau \frac{b_q (\tau) + b_{-q}^\dagger (\tau)}{\sqrt{2 \Omega_q}} \Gamma_{q k}(\tau)\right)\right)\right]_0 \\
&= i \Theta(t) e^{-i \epsilon_k t} \operatorname{Tr}\left[\rho T \left(\exp \left(\underbrace{-i \sum_q \int_0^t d \tau \frac{b_q(\tau) \Gamma_{q k}(\tau)}{\sqrt{2 \Omega_q}}}_{A}\right)\right.\right. \\
&\left.\left.\quad \times \exp \left(\underbrace{-i \sum_q \int_0^t d \tau \frac{b_{-q}^\dagger(\tau) \Gamma_{-q k}(\tau)}{\sqrt{2 \Omega_q}}}_{B}\right)\right)\right]_0  \\
&= i \Theta(t) e^{-i \epsilon_k t} \left\langle 1 +T(A+B) + \frac{1}{2} T(A^2 + 2AB + B^2) + \cdots \right\rangle_\rho \quad \text{with} \quad \rho \propto e^{-\beta H_{\text{ph}}}  \\
&= i \Theta(t) e^{-i \epsilon_k t} \left\langle 1+T AB + \ldots \right\rangle_\rho \quad \text{(vacuum buubles and disconnected terms vanish)} \label{ce:exp} \\
&= i \Theta(t) e^{-i \epsilon_k t} T \exp \left[ i \sum_q \int_0^t d \tau \int_0^\tau d \tau' D_q(\tau - \tau') \Gamma_{q k}(\tau) \Gamma_{-q k}(\tau') \right] \label{final_ce}
% &= i \Theta(t) e^{-i \epsilon_k t} \exp \left[ \sum_q \int_0^t d \tau \int_0^t d \tau' D_q(\tau - \tau') \Gamma_{q k}(\tau) \Gamma_{-q k}(\tau') \right]
% &= - i \Theta(t) e^{-i \epsilon_k t} \sum_{q,q'} \int_0^t d \tau \int_0^t d \tau'\; \frac{1}{\sqrt{2\Omega_q 2\Omega_{q'}}} \Gamma_{qk}(\tau)\Gamma_{-q'k}(\tau') \, \langle T\, b_q(\tau)\, b_{-q'}^\dagger(\tau') \rangle_\rho  \\
% &= i \Theta(t) e^{-i \epsilon_k t} \exp\!\left[
% \sum_q \int_0^t d\tau \int_0^t d\tau'\;
% \frac{\Gamma_{qk}(\tau)\Gamma_{-qk}(\tau')}{2\Omega_q e^{i\Omega_q(\tau-\tau')}}\,
% \Big((1+N_q)\Theta(\tau-\tau') + N_q\Theta(\tau'-\tau)\Big)
% \right]
\end{align}
where the free phonon Green function is
\begin{equation}
    D_q(\tau - \tau') = \frac{i}{2 \Omega_q} \left( (1 + N(\Omega_q)) e^{-i \Omega_q |\tau - \tau'|} + N(\Omega_q) e^{+i \Omega_q |\tau - \tau'|} \right)
\end{equation}
and $N(\Omega_q)$ is the phonon occupation number
\begin{equation}
    N(\Omega_q) = \frac{1}{\exp \left( \frac{\Omega_q}{k T} \right) - 1}
% \left( \exp \left( \frac{\Omega_q}{k T} \right) - 1 \right)^{-1}
\end{equation}
% where $D_4\left(\tau-\tau^{\prime}\right)$ is the free phonon Green function
% $$
% D_q\left(\tau-\tau^{\prime}\right)=\frac{i}{2 \Omega_q}\left(\left(1+N\left(\Omega_q\right)\right) \mathrm{e}^{-i \Omega_q\left|\tau-\tau^{\prime}\right|}+N\left(\Omega_q\right) \mathrm{e}^{+\left|\Omega_q\right| \tau-\tau^{\prime} \mid}\right)
% $$
% and $N\left(\Omega_q\right)$ is the phonon occupation number
% $$
% N\left(\Omega_q\right)=\left(\exp \left(\Omega_q / k T\right)-1\right)^{-1}
% $$    
% \begin{tcolorbox}
% At \ref{ce:exp}, we have two options for the time ordering: either the $\tau$ in $A$ is less than or equal to the $\tau'$ in $B$ or $\tau \geq \tau'$; both terms will contribute to the final trace, so we need to add them up, as we move to convert the expansion of connected terms back into an exponential.
% With 
%     $\tau \geq \tau^{\prime}$,
% the contribution is
% \begin{equation}
%     \exp \left(-\sum_q \frac{\Gamma_{q k}(\tau) \Gamma{ }_{-q k}\left(\tau^{\prime}\right)}{2 \Omega_q}\left(1+N\left(\Omega_q\right)\right) e^{-i \Omega_q\left(\tau-\tau^{\prime}\right)}\right)
% \end{equation}
% whereas for $\tau<\tau^{\prime}$, we get
% \begin{equation}
%     \exp \left(-\sum_q \frac{\Gamma_{-q k}\left(\tau^{\prime}\right) \Gamma_q(\tau)}{2 \Omega_q} N\left(\Omega_q\right) e^{+i \Omega_q\left(\tau^{\prime}-\tau\right)}\right)
% \end{equation}
% and combining these gives \ref{final_ce}.
% We just found that
% \begin{align}
% G_k(t)&= i \Theta(t) e^{-i \epsilon_k t} T \exp(S) \\
% &= i \Theta(t) e^{-i \epsilon_k t} \exp \left( i A_k(t) \right)
% \end{align}
\subsubsection{Approximations}
The exact result for the Green function is
\begin{align}
    G_k(t)&= i \Theta(t) e^{-i \epsilon_k t} T \exp \left[ S \right] \label{eq:exact_G} \\
% &= i \Theta(t) \exp \left( -i \epsilon_k t - i \log [T \exp (S)] \right) \\
&\equiv i \Theta(t) \exp \left( i A_k(t) \right) \\
&= i \Theta(t) \exp \left( -i \epsilon_k t - i \sum_{n=1}^{\infty} \frac{1}{n!} T\left[S^n\right]_c \right) 
% &= i O(t) \mathrm{e}^{-i G_{k^{\prime}}} \prod_{n=1}^N \mathrm{e}^{r\left(S^n\right]_e}
\end{align}
where we found $S = i \sum_q \int_0^t d \tau \int_0^\tau d \tau' D_q(\tau - \tau') \Gamma_{q k}(\tau) \Gamma_{-q k}(\tau')$, so the action function 
\begin{align}
    A_k(t) &= -\epsilon_k t - i \log [T \exp (S)] \\
&= -\epsilon_k t - i \sum_{n=1}^{\infty} \frac{1}{n!} T\left[S^n\right]_c
\end{align}
with $T\left[S^n\right]_c = T\left[S^n\right]-\sum_{m=1}^{n-1} \frac{(n-1)!}{m!(n-m-1)!} T\left[S^{m}\right] T\left[S^{n-m}\right]_c$, where $T[S]_c=T[S]$.
We showed earlier that only the connected terms survive, i.e. this is why we have $ [T S^n ]_c$; 
this final form is amenable to approximation. So to Nth order, we can write
\begin{equation}
G_k(t) = i \Theta(t) e^{-i \epsilon_k t} \prod_{n=1}^N e^{T\left[S^n\right]_c}
\end{equation}
A telling comparison with \ref{eq:exact_G} shows that we managed to replace the time-ordered exponential by a product of exponentials, where the time-ordering is done in the arguments and only involves connected terms. \footnote{Note that in PJ's paper, he pursued the fully self consistent approach where $A_k(t)=-i C_k(t)$ and
\begin{align}
    C_k(t)&=i\phi_k(t) + \sum_{n=1}^{\infty} \frac{1}{n!} T\left[\bar{S}^n\right]_c \\
&= -i \epsilon_k t - i \frac{g^2}{N}\sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) e^{-C_k(\tau)+C_{k-q}(\tau)-C_{k-q}\left(\tau^{\prime}\right)+C_k\left(\tau^{\prime}\right)} + O(g^4) \\
\label{a7}
\end{align}
}
\begin{tcolorbox}
    The diagrammatic explanation of what this cluster expansion does is that unlike usual perturbation theory, which sums a finite subset of diagrams exactly and does not treat the rest, this cluster expansion treats an infinite subset of diagrams approximately. And illustrative example of this phenomenon is that in this procedure, we are effectively substituting the renormalized energy for a multi-boson process as $\epsilon_{k+q_1+q_2} \rightarrow \epsilon_{k+q_1} + \epsilon_{k+q_2} - \epsilon_k$, which incurs the error of $(q_1 \cdot q_2)/m$ for a parabolic band with mass $m$ because
\begin{align}
    \epsilon_{k+q_1+q_2} = \frac{|k+q_1+q_2|^2}{2 m} &= \frac{|k|^2 + |q_1|^2 + |q_2|^2 + 2 k \cdot q_1 + 2 k \cdot q_2 + 2 q_1 \cdot q_2}{2 m} \\
\epsilon_{k+q_1} + \epsilon_{k+q_2} - \epsilon_k &= \frac{|k|^2 + |q_1|^2 + 2 k \cdot q_1}{2 m} + \frac{|k|^2 + |q_2|^2 + 2 k \cdot q_2}{2 m} - \frac{|k|^2}{2 m} \\
\implies \epsilon_{k+q_1+q_2} - \left( \epsilon_{k+q_1} + \epsilon_{k+q_2} - \epsilon_k \right) &= \frac{q_1 \cdot q_2}{m}
\end{align}
So the procedure is valid for either small $q$ values (which corresponds to low energy or high wavelength excitations as is typical in large polarons) or large band mass $m$ (remember that the single particle energies are given by $\epsilon_k = \frac{|k|^2}{2 m}$, so a large $m$ means a flat band). Also, obviously it works when $\Gamma_k$ is large, which is when the peaks are very broad, so fine resolution is not needed. It can also be considered to be applicable when ( $2 N$ )th order perturbation theory is good for $\epsilon _k$ and $\Gamma_k$. In any case, $G_{\mathrm{k}}(\omega)$ should be determined accurately by the cluster expansion if $\omega$ is far from the region of the renormalized energy.
\end{tcolorbox}
\subsubsection{Examples}
Now, we can write down the first and second order corrections in the cluster expansion for the action function as
\begin{align}
    A_k^{(1)}(t) &= -i T[S] \\
&= -i^2 \sum_q \int_0^t d \tau \int_0^\tau d \tau' D_q(\tau - \tau') T\left[ \Gamma_{q k}(\tau) \Gamma_{-q k}(\tau') \right] \\
&= \sum_q \int_0^t d \tau \int_0^\tau d \tau' \left| g_{q k} \right|^2 D_q(\tau - \tau') e^{i (\epsilon_k - \epsilon_{k + q})(\tau - \tau')}
\end{align}
and then
\begin{align}
A_k^{(2)}(t) &= -\frac{i}{2}  T\left[S^2\right]_c\\
&= -\frac{i}{2} \left( T\left[S^2\right] - T\left[S\right] T\left[S\right] \right) \\
 &= i \sum_{q_1} \sum_{q_2} \int_0^t d \tau_1 \int_0^{\tau_1} d \tau_2 \int_0^{\tau_2} d \tau_3 \int_0^{\tau_3} d \tau_4 \left[ D_{q_1}(\tau_1 - \tau_3) D_{q_2}(\tau_2 - \tau_4) \right. \\
&\times \left( g_{q_1 k} g_{q_2 k + q_1} g_{q_2 k}^* g_{q_1 k + q_2}^* e^{i \left( \left\{ \epsilon_k (\tau_1 - \tau_4) - \epsilon_{k + q_1} (\tau_1 - \tau_2) - \epsilon_{k + q_1 + q_2} (\tau_2 - \tau_3) - \epsilon_{k + q_2} (\tau_3 - \tau_4) \right\} \right.} \right. \\
&\left. - |g_{q_1 k} g_{q_2 k}|^2 e^{i \left( (\epsilon_k - \epsilon_{k + q_1})(\tau_1 - \tau_3) + (\epsilon_k - \epsilon_{k + q_2})(\tau_2 - \tau_4) \right)} \right) + D_{q_1}(\tau_1 - \tau_4) D_{q_2}(\tau_2 - \tau_3) \\
&\times \left( |g_{q_1 k} g_{q_2 k + q_1}|^2 e^{i \left( \epsilon_k (\tau_1 - \tau_4) - \epsilon_{k + q_1} (\tau_1 - \tau_2) - \epsilon_{k + q_1 + q_2} (\tau_2 - \tau_3) - \epsilon_{k + q_2} (\tau_3 - \tau_4) \right)} \right. \\
&\left. \left. - |g_{q_1 k} g_{q_2 k}|^2 e^{i \left( (\epsilon_k - \epsilon_{k  + q_2})(\tau_1 - \tau_4) + (\epsilon_k - \epsilon_{k + q_1})(\tau_2 - \tau_3) \right)} \right) \right]
\end{align}
so in the second order cluster approximation $G_k(\omega)$ is given by
\begin{equation}
G_k(\omega )=i \int_0^{\infty} d t e^{i \omega t} \exp \left[ i \left( -\epsilon_k t + A_k^{(1)}(t) + A_k^{(2)}(t) \right) \right]
\end{equation}
% 4.1 The Cluster Expansion

% In the long time limit the second order cluster expansion ([24] and [25]) just yields the fourth order perturbation expression for the renormalized energy and this, of course, confirms the doubts about this asymptotic region. Nevertheless the cluster expansion produces an accurate $G_{\Delta}(\omega)$ over the whole range if $\Gamma_k \gtrsim \Omega$. The inverse life time of a polaron is of order $\alpha N(\Omega)$ and so a sufficient criterion for the validity of the above theory is
% $$
% \alpha N(\Omega) \gtrsim 1
% $$

% DUNN: ELECTRON-PHONON INTERACTIONS
% 329

% The normalization constant $\operatorname{Im}\left(\Delta_k\right)$ for a slow polaron is of order $1 / 2 \alpha(1+N(\Omega))$ and the asymptotic region is again negligible if
% $$
% \alpha(1+N(\Omega)) \gtrsim 2
% $$

% Therefore if either of these conditions is satisfied the approximation procedure is valid.
% For a stationary polaron the fourth order perturbation result for the renormalized energy is very good (Sheng and Dow 1971) for $\alpha \lesssim 6$ and so in this special case the approximation procedure should produce accurate results even if [36] and [37] are not satisfied.

% In the expression [24] for the first order contribution to the action function the integrations over the phonon wave vector $q$ can be carried out explicitly for the polaron interaction:
% $$
% A_k^{(1)}(t)=-(1-i) \alpha\left(\frac{\Omega}{\delta_k}\right)^{i / 2} \Omega^3 t \int_0^t \mathrm{~d} \tau \frac{(t-\tau)}{\sqrt{\tau}} D(\tau)\left(\mathrm{C}\left(\sqrt{\frac{2}{\pi} \delta_k t}\right)+i \mathrm{~S}\left(\sqrt{\frac{2}{\pi} \delta_k t}\right)\right)
% $$
% where C and S are Fresnel integrals (Abramowitz and Stegun 1964, p. 300).
% The wave vector integrations can also be carried out explicitly for the second order contribution in the case of a stationary polaron:
% [39]
% $$
% \begin{aligned}
% A_0{ }^{(2)}(t) & =-\frac{4 \alpha^2}{\pi} \Omega^5\left[\int_0^t \mathrm{~d} \tau \int_0^\tau \mathrm{d} \tau^{\prime} D(\tau) D\left(\tau^{\prime}\right)(t-\tau)\left(\tau-\tau^{\prime}\right)\left(\frac{1}{\tau^{\prime}} \arcsin \left(1 \sqrt{\frac{\tau^{\prime}}{\tau}}\right)-\frac{1}{\sqrt{\tau \tau^{\prime}}}\right)\right. \\
% & \left.+\int_0^t \mathrm{~d} t_1 \int_0^{t_t} \mathrm{~d} \tau \int_0^\tau \mathrm{d} \tau^{\prime} D(\tau) D\left(\tau^{\prime}\right)\left(\frac{1}{\tau-\tau^{\prime}} \arcsin \left(\frac{\tau-\tau^{\prime}}{\sqrt{\tau\left(t_1-\tau^{\prime}\right)}}\right)-\frac{1}{\sqrt{\tau\left(t_1-\tau^{\prime}\right)}}\right)\right]
% \end{aligned}
% $$

% If $k \neq 0$ then the second order contribution is not so simple.
% 4.2 The Numerical Results

% In the case of a stationary polaron the numerical result for the long time limit of the action function is
% $$
% \begin{aligned}
% A_0(t) & \rightarrow \Omega\left[\alpha(1+N(\Omega))+\alpha^2(0.0159-0.190 N(\Omega)(1+N(\Omega)))+i \alpha N(\Omega)\right] \\
% & +\left[(\alpha / 2) N(\Omega)+\alpha^2 0.830 N(\Omega)(1+N(\Omega))+i(\alpha / 2)(1+N(\Omega))+i \alpha^2 0.020(1+2 N(\Omega))\right]
% \end{aligned}
% $$

% The error in the quoted numbers is typically $1-3$ in the last figure.
% This renormalized energy agrees with the zero temperature value computed by Sheng and Dow (1971).

% In the limit $\Omega t \ll 1$ the result is
% [41]
% $$
% \begin{aligned}
% & A_0(t) \rightarrow \alpha(1+i) \sqrt{2 / \pi}(\Omega t)^{3 / 2}(2 / 3(1+N(\Omega))-i 2 / 15(\Omega t) \ldots) \\
% & \quad-\alpha^2(\Omega t)^3\left(5.51 \times 10^{-3}+2.20 \times 10^{-3} N(\Omega)(1+N(\Omega))-i 4.14 \times 10^{-3}(1+2 N(\Omega)) \Omega t\right)
% \end{aligned}
% $$
% and in fact it can be shown that in this limit the $n$th term in the cluster expansion is proportional to $(\Omega t)^{3 n / 2}$.

The cluster expansion for the action function works well except for the long time limit, but we want it to be well resolved for all times in order to capture the full frequency range. If we use the Feynman operator ordering theorem as in section \ref{sec:pj_ce}, the action function can now be expressed as
\begin{align}
    A_k(t) &= \phi_k(t) - i \log [T \exp (\bar{S})] \\
&= \phi_k(t) - i \sum_{n=1}^{\infty} \frac{1}{n!} T\left[\bar{S}^n\right]_c
\end{align}
where $\phi_k(t)$ can be chosen so as to improve the approximation with 
\begin{equation}
    \bar{S} = -i \int_0^t d \tau\left(\epsilon_k+\frac{d}{d \tau} \phi_k(\tau)\right) -i \sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \bar{\Gamma}_{-q k}(\tau) \bar{\Gamma}_{q k}\left(\tau^{\prime}\right)
\end{equation}
 using the transformed vertex operators
\begin{align}
    \bar{\Gamma}_{q k}(\tau)&\equiv  \hat{U}(\tau)\Gamma_{q k}(\tau)\hat{U}^{-1}(\tau)\\
&=g_{q k} e^{-i \phi_k(\tau)} e^{q \cdot \frac{d}{d k}} e^{+i \phi_k(\tau)}
\end{align}
and the bare bosonic propagator 
\begin{equation}
    D_q^{(0)}(t)= -i\left[\left(1+N_q\right) e^{-i \omega_q|l|}+N_q e^{\left|\omega_q\right| l \mid}\right]
\end{equation}
with the Bose occupation factor $N_q=\left[\exp \left(\beta \omega_q\right)-1\right]^{-1}$. . But Dunn chooses $\phi_k(t)= -\epsilon_k t$, where $\epsilon_k$ is a (as yet undetermined) renormalized energy. With $\dot{\phi}_k = -\epsilon_k \implies  \epsilon_k + \dot{\phi}_k = 0$, the action function to first order in the cluster expansion becomes
\begin{align}
    A_k(t) &\approx \phi_k(t) - i T[\bar{S}]_c \\
&= -\epsilon_k t - i \langle \bar{S} \rangle \\
&= -\epsilon_k t - \sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \langle \bar{\Gamma}_{-q k}(\tau) \bar{\Gamma}_{q k}\left(\tau^{\prime}\right) \rangle  \\
&= -\epsilon_k t - \sum_q \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) \langle g_{-q k} g_{q k} e^{-i \phi_k(\tau)} e^{-q \cdot \frac{d}{d k}} e^{+i \phi_k(\tau)} e^{-i \phi_k\left(\tau^{\prime}\right)} e^{+q \cdot \frac{d}{d k}} e^{+i \phi_k\left(\tau^{\prime}\right)} \rangle \\
&= -\epsilon_k t - \sum_q |g_{qk}|^2 \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) e^{i \epsilon_k \tau} e^{-i \epsilon_{k-q} \tau} e^{i \epsilon_{k-q} \tau^{\prime}} e^{-i \epsilon_k \tau^{\prime}}  \\
&= -\epsilon_k t - \sum_q |g_{qk}|^2 \int_0^t d \tau \int_0^\tau d \tau^{\prime} D_q^{(0)}\left(\tau-\tau^{\prime}\right) e^{i\left(\epsilon_k-\epsilon_{k-q}\right)\left(\tau-\tau^{\prime}\right)} \\
&= -\epsilon_k t + i \sum_q |g_{qk}|^2 \int_0^t d \Delta (t - \Delta) \left[ \left(1 + N_q \right) e^{i\left(\epsilon_k - \epsilon_{k - q} - \Omega_q\right) \Delta} + N_q e^{i\left(\epsilon_k - \epsilon_{k - q} + \Omega_q\right) \Delta} \right] \\
&= -\epsilon_k t + i \sum_q |g_{qk}|^2 \left[ \left(1 + N_q \right) \frac{e^{i t b_{-}} - 1 - i t b_{-}}{b_{-}^2} + N_q \frac{e^{i t b_{+}} - 1 - i t b_{+}}{b_{+}^2} \right]
\end{align}
where we have set $\Delta \equiv \tau - \tau^{\prime} \in [0, t]$ and $b_{\mp} = \epsilon_k - \epsilon_{k - q} \mp \Omega_q$. The solution resembles the Landau form of the cumulant of $C(t)=\int d \omega \frac{\beta(\omega)}{\omega^2}\left[e^{-i \omega t}+i \omega t-1\right]$. This is not a coincidence because the action function is supposed to contain the cumulant by design. Then, $\epsilon_k$ can be identified from the long time behavior
\begin{align}
    \epsilon_k &\equiv -\lim_{t \rightarrow \infty} \frac{d}{d t} \operatorname{Re} \left( A_k(t) \right) \\
&= -\lim_{t \rightarrow \infty} \operatorname{Re} \left( \frac{d}{d t} \left[ -\epsilon_k t + i \sum_q |g_{qk}|^2 \left[ \left(1 + N_q \right) \frac{e^{i t b_{-}} - 1 - i t b_{-}}{b_{-}^2} + N_q \frac{e^{i t b_{+}} - 1 - i t b_{+}}{b_{+}^2} \right] \right] \right) \\
&= -\lim_{t \rightarrow \infty} \left[ -\epsilon_k^{(0)}-\sum_q\left|g_{q k}\right|^2\left[\left(1+N_q\right) \Re\left(\frac{e^{i t b_{-}}-1}{b_{-}}\right)+N_q \Re\left(\frac{e^{i t b_{+}}-1}{b_{+}}\right)\right] \right] \\
&= \epsilon_k^{(0)} - \sum_q\left|g_{q k}\right|^2\left[\left(1+N_q\right) \mathcal{P}\left(\frac{1}{b_{-}}\right)+N_q \mathcal{P}\left(\frac{1}{b_{+}}\right)\right] \\
% &= \epsilon_k - \lim_{t \rightarrow \infty} \frac{d}{d t} \operatorname{Re} \left[ i \sum_q |g_{qk}|^2 \left[ \left(1 + N_q \right) \frac{e^{i t b_{-}} - 1 - i t b_{-}}{b_{-}^2} + N_q \frac{e^{i t b_{+}} - 1 - i t b_{+}}{b_{+}^2} \right] \right] \\
% &= \epsilon_k - \operatorname{Re} \sum_q |g_{qk}|^2 \left[ \left(1 + N_q \right) \frac{- e^{i t b_{-}} +1}{b_{-}} + N_q \frac{- e^{i t b_{+}} + 1}{b_{+}} \right]_{t \rightarrow \infty} \\
&= \epsilon_k^{(0)} - \mathcal{P} \sum_q\left|g_{q k}\right|^2\left[\frac{1+N_q}{\epsilon_k-\epsilon_{k+q}-\Omega_q}+\frac{N_q}{\epsilon_k-\epsilon_{k+q}+\Omega_q}\right]
\end{align}


which gives a self-consistent condition for $\epsilon_k$. \footnote{This is only self consistent in the energy, which PJ did not like.  The self consistent choice was $\phi_k(t)=-iC_k(t)$ in PJ's paper.} We could do the penultimate step because $\lim_{t \rightarrow \infty}\frac{e^{i b t} -1 }{b} = i\int_0^\infty d \tau e^{i \tau b}= i \pi \delta(b) - \mathcal{P}\left( \frac{1}{b} \right)$, where $\mathcal{P}$ denotes the Cauchy principal value.

% 5.1 The Polaron Model

% In the polaron case the renormalized excitation energy $W\left({E}_k\right)=E_k-E_0$ is the solution of the integral equation
% $$
% \begin{aligned}
% W({E})={E}-\frac{\alpha \Omega^{3 / 2}}{2 \pi} {g} \int_0^{\infty} \mathrm{d} x & {\left[\frac { 1 } {  { E } ^ { 1 / 2 } } \operatorname { l o g } | \frac { x ^ { 1 / 2 } +  { E } ^ { 1 / 2 } } { x ^ { 1 / 2 } -  { E } ^ { 1 / 2 } } | \left(\frac{1+N(\Omega)}{W(x)-W(\delta)+\Omega}\right.\right.} \\
% & \left.\left.+\frac{N(\Omega)}{W(x)-W({E})-\Omega}\right)-\frac{2}{x^{1 / 2}}\left(\frac{1+N(\Omega)}{W(x)+\Omega}+\frac{N(\Omega)}{W(x)-\Omega}\right)\right]
% \end{aligned}
% $$

% There are several points that can be determined about the solution of this equation. There is a threshold (i.e., a discontinuity in the slope) which occurs at precisely one phonon energy above $E_0$ :
% $$
% W\left({G}_1\right)=\Omega
% $$

% Furthermore as this threshold is approached from below the slope tends to zero
% $$
% W^{\prime}\left(G_{r^{-}}\right)=0
% $$

% This is the correct threshold behavior for the excitation energy (Larsen 1966).
% If ${E} \lesssim {E}$, the important region of the integral is $x \approx 0$ and so it is sufficient to replace $W(x)$ by $x / m^*$ where $m^*$ is the polaron mass. The excitation energy is then determined by the equation
% $$
% \begin{aligned}
% W({E}) & ={E}-\alpha \Omega(1+N(\Omega))\left(\frac{m^* \Omega^{1 / 2}}{{E}^{1 / 2}} \arctan \left(\sqrt{\frac{\delta / m^*}{\Omega-W({E})}}\right)-m^{* 1 / 2}\right) \quad W({E}) \leqslant \Omega \\
% & ={E}-\alpha \Omega(1+N(\Omega))\left(\frac{m^* \Omega^{1 / 2}}{2 {E}^{1 / 2}} \pi-m^{* 1 / 2}\right) \quad W({E})>\Omega
% \end{aligned}
% $$

% This is similar to the Tamm-Dancoff dispersion formula (Whitfield and Puff 1965) except for the inclusion of the polaron mass $m$ * which is determined by equating the coefficient of the term linear in $\delta$ to $1 / m^*$ :
% [54]
% $$
% m^*=1+\frac{\alpha(1+N(\Omega))}{6}\left[\left(1+\left(\frac{\alpha}{12}(1+N(\Omega))\right)^2\right)^{1 / 2}+\frac{\alpha(1+N(\Omega))}{12}\right]
% $$

% The polaron energy shift $E_0$ is obtained by inserting these results into [45]. The numerical values of $E_0$ and $m^*$ for zero temperature are shown in Table 1 and the polaron energy dispersion is plotted in Fig. 6.

% There have been several previous attempts to determine the polaron dispersion relation at zero temperature but all seem to have some obvious flaws: in the Tamm-Dancoff approximation the slope vanishes at the phonon threshold but this threshold is not one phonon energy above $E_0$; in the improved Tamm-Dancoff approximation (Whitfield and Puff 1965) the correct threshold behavior is obtained, $W^{\prime}\left(\mathcal{E}_1-\right)=0$ and $W\left(\mathcal{E}_1\right)=\Omega$, but the polaron energy shift $E_0$ is outside known limits; Larsen (1966) also obtains the correct threshold behavior but his $E_0$, although an improvement on that of Whitfield and Puff, is just the weak interaction limit $-\alpha \Omega$.
% Numerical values for the polaron mass and energy shift at zero temperature are given in Table I together with upper and lower bounds for the energy shift (Larsen 1968; Lieb and Yamazaki 1958) and the Lee et al. (1953) result for the polaron mass.

% The cluster approximation and the improved cluster approximation are compared in Fig. 7 and in Fig. 8 the imaginary part of the Green function is shown for several free particle energies.
% 5.3 Further Improvements

% Another, and probably better, method is to choose the function in [42]-[44] to be the action function itself. The cluster theorem [45] then implies an exact self-consistency condition on the action function
% $$
% \sum_{n=1}^{\infty} \frac{1}{n!} T\left[S^n\right]_e
% $$
% and an approximate procedure is to take only a finite number of terms in this series and to solve the equation for $A_{\mathrm{A}}(t)$.

% In the lowest order ( $N=1$ ) the resulting integral equation is
% $$
% \begin{aligned}
% A_k(t)=-{E}_k l+\sum_q\left|g_{q k}\right|^2 \int_0^t \mathrm{~d} \tau \int_0^\tau \mathrm{d} \tau^{\prime} D_q\left(\tau-\tau^{\prime}\right) & \\
% & \quad \quad \times \exp \left[-i\left(A_k(\tau)-A_k\left(\tau^{\prime}\right)-A_{k+q}(\tau)+A_{k+q}\left(\tau^{\prime}\right)\right)\right]
% \end{aligned}
% $$

% We have not yet attempted to solve this equation.
\section{My derivations}
\subsection{Writing spectral functions for the UEG}
\subsubsection{Noninteracting case}
We can start by writing down the form for the retarded non-interacting Green's function of a state $p$ in time domain as
\begin{equation}
    G^R_{0,p}(t) = -i \Theta(t) e^{-i \left(\epsilon_p - \varepsilon_F \right)t}
\end{equation}
where $\varepsilon_F$ is the Fermi energy. I am operating at zero temperature, so in my HF code, this means that $\varepsilon_F$ is just the energy of the highest occupied molecular orbital; for this system of the UEG at $r_s = 4$ with 14 electrons in 19 orbitals it is just the energy of orbital 6 (with orbitals numbered from 0). A broadening parameter of $\eta = 0.2$ eV is used (this coincides with what Joonho and Garnet used). The HF single particle energies I get from my code do not take the Madelung correction into account. In that case, Joonho's paper tells us that for the spectral function of these occupied orbitals, we need to apply a constant frequency shift of
\begin{equation}
\Delta _{IP} = -\frac{\xi}{2}    
\end{equation}
where $\xi=-2 \times 2.837297 \times\left(\frac{3}{4 \pi}\right)^{1 / 3} N^{-1 / 3} r_{\mathrm{s}}^{-1}$ Hartrees. For my system, this means that $\frac{\xi}{2} = -4.97$ eV. But this is confusing because it would mean that the shift for the occupied orbitals is positive $+4.97$ eV, which is counter-intuitive, as this would imply that the HF peak for the Fermi state occurs at a positive frequency. To obtain my plots, I assume that this was a typo, and instead apply a shift of $-\Delta_{IP} = +\frac{\xi}{2} = -4.97$ eV to the occupied orbitals. In RHF, the retarded second order self-energy in the frequency domain is given by
\begin{align}
{\Sigma}^{c,(2),R}(p, \omega) &= \frac{1}{2} \sum_{iab} \frac{\left< pi \left| \right| ab \right>^2}{\omega - \epsilon_{a} - \epsilon_{b} + \epsilon_{i} + i \eta} + \frac{1}{2} \sum_{ija} \frac{\left< pa \left| \right| ij \right>^2}{\omega - \epsilon_{i} - \epsilon_{j} + \epsilon_{a} + i \eta}\\
&\overset{\text{RHF}}{=} \frac{1}{2} \sum_{iab} \frac{\left( 2\left<pi|ab\right> - \left<pi|ba\right>\right)^2}{\omega - \epsilon_{a} - \epsilon_{b} + \epsilon_{i} + i \eta} + \frac{1}{2} \sum_{ija} \frac{\left( 2\left<pa|ij\right> - \left<pa|ji\right>\right)^2}{\omega - \epsilon_{j} - \epsilon_{i} + \epsilon_{a} + i \eta}\\
& = \frac{2\pi}{V} \left( \sum_{\mathbf{k}_i \in O; \,\mathbf{k}_a , \mathbf{k}_b \in V} \frac{\left[ \frac{2\delta_{\mathbf{k}_p - \mathbf{k}_a , \mathbf{k}_b - \mathbf{k}_i}}{|\mathbf{k}_p - \mathbf{k}_a|^2} - \frac{\delta_{\mathbf{k}_p - \mathbf{k}_b , \mathbf{k}_a - \mathbf{k}_i}}{|\mathbf{k}_p - \mathbf{k}_b|^2} \right]^2 }{\omega - \epsilon_{\mathbf{k}_a} - \epsilon_{\mathbf{k}_b} + \epsilon_{\mathbf{k}_i} + i \eta}  + \sum_{\mathbf{k}_i,\mathbf{k}_j \in O;\, \mathbf{k}_a \in V} \frac{\left[ \frac{2\delta_{\mathbf{k}_p - \mathbf{k}_i , \mathbf{k}_j - \mathbf{k}_a}}{|\mathbf{k}_p-\mathbf{k}_i|^2} - \frac{\delta_{\mathbf{k}_p - \mathbf{k}_j , \mathbf{k}_i - \mathbf{k}_a}}{|\mathbf{k}_p - \mathbf{k}_j|^2} \right]^2 }{\omega - \epsilon_{\mathbf{k}_i} - \epsilon_{\mathbf{k}_j} + \epsilon_{\mathbf{k}_a} + i \eta} \right)
\label{eq:self_energy_2nd_order}
\end{align}
where $\mathbf{k}_b = \mathbf{k}_p  + \mathbf{k}_i - \mathbf{k}_a$ in the first sum and $\mathbf{k}_j = \mathbf{k}_p - \mathbf{k}_i + \mathbf{k}_a$ in the second sum due to momentum conservation. 
\subsubsection{GW spectral function}
Consider
\begin{align}
    \Sigma_k (\omega ) &= G_{0,k}^{-1}(\omega ) - G_k^{-1}(\omega ) \\
    \implies G_k(\omega ) &= \frac{1}{G_{0,k}^{-1}(\omega ) - \Sigma_k(\omega )} \\
    &= \frac{1}{\omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega ) - i \operatorname{Im} \Sigma_k (\omega )} \times \frac{\left( \omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega ) + i \operatorname{Im} \Sigma_k (\omega )\right)}{\left( \omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega ) + i \operatorname{Im} \Sigma_k (\omega )\right)} \\
    &= \frac{\omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega ) + i \operatorname{Im} \Sigma_k (\omega )}{\left(\omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega )\right)^2 + \left(\operatorname{Im} \Sigma_k (\omega )\right)^2}
\end{align}
We want $-\frac{1}{\pi} \operatorname{Im} G_k(\omega )$, so
\begin{align}
    \operatorname{Im} G_k(\omega ) &= \frac{\operatorname{Im} \Sigma_k (\omega )}{\left(\omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega )\right)^2 + \left(\operatorname{Im} \Sigma_k (\omega )\right)^2} \\
\end{align}
Thus, the spectral function is
\begin{equation}
    A(\omega ) = -\frac{1}{\pi} \operatorname{Im} G_k(\omega ) = -\frac{1}{\pi} \frac{\operatorname{Im} \Sigma_k (\omega )}{\left(\omega - \epsilon_k - \operatorname{Re} \Sigma_k (\omega )\right)^2 + \left(\operatorname{Im} \Sigma_k (\omega )\right)^2}
\end{equation}
This means we can write down the second order cumulant in the time domain as
\begin{align}
C_{pp}^{(2)}(t) &\equiv i \int \frac{d\omega}{2\pi} \frac{ \tilde{\Sigma}_{pp}^{c,(2)}\left(\omega+\epsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t} \\
 &= \frac{1}{2} \sum_{iab} \left< pi \left| \right| ab \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pi}^{ab}\right)} + \frac{1}{2} \sum_{ija} \left< pa \left| \right| ij \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pa}^{ij}\right)} \\
% \label{eq:cumulant_2nd_1}
&= \frac{1}{2}\sum_{iab} \frac{\left< pi \left| \right| ab \right>^2}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
+\frac{1}{2}\sum_{ija} \frac{\left< pa \left| \right| ij \right>^2}{\left(\epsilon_{pa}^{ij}\right)^2}
\left(e^{-i \epsilon_{pa}^{ij} t} +i \epsilon_{pa}^{ij} t -1 \right) \\
&= \frac{2\pi}{V} \left( \sum_{\mathbf{k}_i \in O; \,\mathbf{k}_a , \mathbf{k}_b \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p - \mathbf{k}_a|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_b|^2} \right]^2 }{\left(\varepsilon_{pi}^{ab}\right)^2}
\left(e^{-i \varepsilon_{pi}^{ab} t} +i \varepsilon_{pi}^{ab} t -1 \right) \right. \\
& \left. + \sum_{\mathbf{k}_i,\mathbf{k}_j \in O;\, \mathbf{k}_a \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p-\mathbf{k}_i|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_j|^2} \right]^2 }{\left(\varepsilon_{pa}^{ij}\right)^2}
\left(e^{-i \varepsilon_{pa}^{ij} t} +i \varepsilon_{pa}^{ij} t -1 \right) \right)
\label{eq:cumulant_2nd_final}
\end{align}
where
$\epsilon_{pi}^{ab} = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i}$
and
$\epsilon_{pa}^{ij} = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}$, but for the UEG, $\varepsilon_{pi}^{ab} = \epsilon_{\mathbf{k}_a} + \epsilon_{\mathbf{k}_b} - \epsilon_{\mathbf{k}_p} - \epsilon_{\mathbf{k}_i}$ and $\varepsilon_{pa}^{ij} = \epsilon_{\mathbf{k}_i} + \epsilon_{\mathbf{k}_j} - \epsilon_{\mathbf{k}_p} - \epsilon_{\mathbf{k}_a}$. When we took the single particle energies from HF, the Madelung correction was never included, so I need to find out if we need to include it here.
\subsubsection{Interacting case}
Now, the form for the retarded interacting Green's function in the time domain is
\begin{equation}
    G_{pp}(t) = -i \Theta(t) e^{-i \left(\epsilon_p - \varepsilon_F \right)t} e^{C_{pp}(t)}
\end{equation}
\subsubsection{Explanation of one-shot plots}
Recall
\begin{align}
G_{pp}(\omega) & = \int_{-\infty}^{\infty} dt e^{i \omega t} G_{pp}(t)
\label{Gpp1}
\\
& = -i Z_p^{QP} \int_0^{\infty} dt e^{i(\omega - \epsilon_p^{QP}) t} e^{\sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t}} 
\label{Gpp2}
\\
& = -i Z_p^{QP} \int_0^{\infty} dt\, e^{i(\omega - \epsilon_p^{QP}) t} \left(1 + \sum_{i\nu} \zeta_{pi\nu} e^{-i\Delta_{pi\nu} t} + \sum_{a\nu} \zeta_{pa\nu} e^{-i\Delta_{pa\nu} t} +\ldots \right) \\
% &= -i Z_p^{QP} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP}) t]}\label{Gpp3} \\
% &\quad - i Z_p^{QP} \sum_{i\nu} \zeta_{pi\nu} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP} - \Delta_{pi\nu}) t]} \\
% &\quad - i Z_p^{QP} \sum_{a\nu} \zeta_{pa\nu} \int_0^{\infty} dt\, e^{[-\eta + i(\omega - \epsilon_p^{QP} - \Delta_{pa\nu}) t]} + \ldots \\
&= \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i\nu} \frac{Z_p^{QP} \zeta_{pi\nu}}{\omega - \epsilon_p^{QP} - \Delta_{pi\nu} + i\eta} + \sum_{a\nu} \frac{Z_p^{QP} \zeta_{pa\nu}}{\omega - \epsilon_p^{QP} - \Delta_{pa\nu} + i\eta} + \ldots\\
% & =-i Z_p^{Q P} \int_0^{+\infty} d r e^{\left[-\eta+i\left(\omega-\varepsilon_p^{Q P}\right)\right]} \\
% & -\mathrm{i} Z_p^{\mathrm{OP}} \sum_{i v} \zeta_{p i v} \int_0^{+\infty} \mathrm{d} r e^{\left\{-\eta+i\left[\omega-\left(\epsilon_p^{\mathrm{OP}}+\Delta_{p i v}\right)\right]\right\}^{\prime}}-\mathrm{i} Z_p^{\mathrm{OP}} \sum_{a v} \zeta_{p a v} \int_0^{+\infty} \mathrm{d} r e^{\left(-\eta+i\left[\omega-\left(\epsilon_p^{\mathrm{OP}}+\Delta_{p \omega v}\right)\right]\right\}^{\prime}} \\
& \approx \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i\nu} \frac{Z_{pi\nu}^{sat}}{\omega - \epsilon_{pi\nu}^{sat} + i\eta} + \sum_{a\nu} \frac{Z_{pa\nu}^{sat}}{\omega - \epsilon_{pa\nu}^{sat} + i\eta}
\label{Gpp4}
\end{align}
 $G_{pp}(\omega)$ is computed via \ref{Gpp4} in the schemes which I call first order. This is what Loos does. On the other hand, $G_{pp}(\omega)$ is computed via \ref{Gpp2} in the schemes which I call to infinite order. As you can see, there are two different flavors of infinite order, which only differ in how the real-time cumulant is computed. Analytic to infinite order does
\begin{align}
	 C_{pp}(t) &= i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}^c\left(\omega+\epsilon_p^{HF}\right)}{(\omega + i \eta)^2} e^{-i \omega t}
\label{eq:Cpp_0} \\
% &= i \int \frac{d\omega}{2\pi} \frac{1}{(\omega + i \eta)^2} e^{-i \omega t} \left[ \sum_{i\nu} \frac{M_{pi\nu}^2}{\omega + \underbrace{\epsilon_p^{HF} - \epsilon_i + \Omega_\nu + i \eta}_{-\Delta_{pi\nu}}} + \sum_{a\nu} \frac{M_{pa\nu}^2}{\omega + \underbrace{\epsilon_p^{HF} - \epsilon_a - \Omega_\nu + i \eta}_{-\Delta_{pa\nu}}} \right] \\
% & =\mathrm{i} \sum_{i v} M_{p i v}^2 \int \frac{\mathrm{~d} \omega}{2 \pi} e^{-\mathrm{i} \omega t} \frac{1}{[\omega+\mathrm{i} \eta]^2} \frac{1}{\omega-\Delta_{p i v}} +\mathrm{i} \sum_{a v} M_{p a v}^2 \int \frac{\mathrm{~d} \omega}{2 \pi} e^{-\mathrm{i} \omega t} \frac{1}{[\omega+\mathrm{i} \eta]^2} \frac{1}{\omega-\Delta_{p a v}}
% \label{eq:Cpp_1}
% \\
&= \sum_{i\nu} \zeta_{pi\nu} \left[ e^{-i\Delta_{pi\nu} t} - 1 + i\Delta_{pi\nu} t \right] + \sum_{a\nu} \zeta_{pa\nu} \left[ e^{-i\Delta_{pa\nu} t} - 1 + i\Delta_{pa\nu} t \right]
\label{eq:Cpp_2}
\end{align}
whereas numerical to infinite order computes using the Landau form
\begin{equation}
    C_{pp}(t) = \int d \omega \frac{\beta_{pp}(\omega)}{\omega^2} \left( e^{-i \omega t} + i \omega t -1 \right)
\label{eq:cumulant_beta_repeat}
\end{equation}
with $\beta_{pp}(\omega) = \frac{1}{\pi} |\operatorname{Im} \Sigma_{pp}(\omega + \epsilon_p^{HF})|$ using the basic Riemann sum for the frequency integration. In both cases, we then plug the cumulant into
\begin{equation}
    G_{pp}(t) = -i \Theta(t) e^{-t \left(i\epsilon_p + \eta\right)t} e^{C_{pp}(t)}
\end{equation}
and then use the DFT to get $A_{pp}(\omega)$.
\subsubsection{Choosing the right shift for my spectral functions}
My interpretation of your discussion is that when I have included the G=0 component in my HF reference, all I have to do is to plot $A_{pp}(\omega+\xi/2)$ for HF, MP2, and MP2+C alike, since I am only computing the spectral function for occupied states. Is that correct?
\subsubsection{Updated results}
As we discussed on Friday, now, I have a RHF reference which includes the G=0 component. I fixed the bug and now it matches with the G=0 excluded reference exactly. Therefore, now the MP2 correlation energy is the same, irrespective of whether G=0 is included or not. I am plotting $A_{pp}(\omega+\xi/2)$ for all my spectral functions. This is because I needed to plot $A_{pp}(\omega+\xi/2)$ for HF in order to match the reference, so I do the same for MP2 and MP2+C; other than this, nothing else gets shifted. 
\subsubsection{Update}
If we choose
\begin{align}
    \xi = -2 \times 2.837297 \times\left(\frac{3}{4 \pi}\right)^{1 / 3} N^{-1 / 3} r_{\mathrm{s}}^{-1}
\end{align}
then I implemented the direct term of my ERIs as 
\begin{equation}
    v(\mathbf{q}) = \begin{cases} \frac{4 \pi}{\mathbf{q}^2 V} & \mathbf{q} \neq 0 \\ 0 & \mathbf{q} = 0 \end{cases}
\end{equation}
and the exchange terms as
\begin{equation}
    v(\mathbf{q}) = \begin{cases} \frac{4 \pi}{\mathbf{q}^2 V} & \mathbf{q} \neq 0 \\ -\xi & \mathbf{q} = 0 \end{cases}
\end{equation}
for use in the self energy as
\begin{align}
    \Sigma^{(2)}_{pp}(\omega)
    & = \sum_{iab} \frac{\left<pi|ab\right>\left(2\left<pi|ab\right> - \left<pi|ba\right>\right)}{\omega - \epsilon_a - \epsilon_b + \epsilon_i + i \eta} + \sum_{ija} \frac{\left<pa|ij\right>\left(2\left<pa|ij\right> - \left<pa|ji\right>\right)}{\omega - \epsilon_i - \epsilon_j + \epsilon_a + i \eta}
\end{align}
\subsubsection{Correct poles with G=0 included}
I have changed the definition of $\xi$ to
\begin{align}
    \xi = -1 \times 2.837297 \times\left(\frac{3}{4 \pi}\right)^{1 / 3} N^{-1 / 3} r_{\mathrm{s}}^{-1}
\end{align}
so omitting the factor of 2 as was suggested. This produces the results that I provide with no manual shift ever done. I present two varieties of cumulants. The Landau form of the cumulant is
\begin{align}
    C_{pp}(t) &\equiv i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}\left(\omega+\varepsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t}
\label{eq:Cpp_0_updated} \\
\end{align}
Then the cumulant ansatz for the time domain interacting Green's function is
\begin{equation}
    G_{pp}(t) = -i \Theta(t) e^{-t(i \varepsilon_p +\eta)} e^{C_{pp}(t)}
\label{eq:Gpp_time_updated}
\end{equation}
When I present MP2+C; $G_0$ via HF, $\varepsilon _p\equiv \epsilon_p^{HF}$ in both \ref{eq:Cpp_0_updated} and \ref{eq:Gpp_time_updated}, and $\Sigma _{pp}(\omega)$ is built from the set $\{\epsilon_p^{HF}\}$. When I present MP2+C; $G_0$ via SRG-MP2, $\varepsilon _p\equiv \epsilon_p^{SRG-MP2}$ in both \ref{eq:Cpp_0_updated} and \ref{eq:Gpp_time_updated}, and $\Sigma _{pp}(\omega)$ is built from the set $\{\epsilon_p^{SRG-MP2}\}$. So the former does not solve Dyson's equation before adding the cumulant correction (it is a true one shot scheme), while the latter solves Dyson's equation at the SRG-MP2 level before adding the cumulant correction.
\subsubsection{Why we need the G=0 component in the ERIs of the MP2 self-energy}
It is instructive to start by understanding why having the G=0 component in the ERIs is irrelevant for computing the MP2 correlation energy. The MP2 correlation energy can be written as
\begin{align}
    E_{c}^{MP2} = \frac{1}{4} \sum_{ijab} \frac{|\left<\bm{k}_i \bm{k}_j|\bm{k}_a \bm{k}_b\right> - \left<\bm{k}_i \bm{k}_j|\bm{k}_b \bm{k}_a\right>|^2}{\epsilon_{\bm{k}_i} + \epsilon_{\bm{k}_j} - \epsilon_{\bm{k}_a} - \epsilon_{\bm{k}_b}}
\end{align}
Because $i,j$ are occupied and $a,b$ are virtual, and the correlation energy always has an OV pair at a ERI center, we will never encounter a zero momentum transfer at any center. Now, the MP2 self-energy is given by
\begin{align}
    % \Sigma_{pq}^{(2)}(\omega) =& \frac{1}{2} \sum_{iab} \frac{\langle pi || ab \rangle \langle ab || qi \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \frac{1}{2} \sum_{ija} \frac{\langle pa || ij \rangle \langle ij || qa \rangle}{\omega + \epsilon_a - \epsilon_i - \epsilon_j} \\
    \Sigma^{(2)}_{pq}(\omega) = \frac{1}{2} \sum_{iab} \frac{\langle \bm{k}_p \bm{k}_i|\bm{k}_a \bm{k}_b \rangle \langle \bm{k}_a \bm{k}_b|\bm{k}_q \bm{k}_i \rangle}{\omega + \epsilon_{\bm{k}_i} - \epsilon_{\bm{k}_a} - \epsilon_{\bm{k}_b}} + \frac{1}{2} \sum_{ija} \frac{\langle \bm{k}_p \bm{k}_a|\bm{k}_i \bm{k}_j \rangle \langle \bm{k}_i \bm{k}_j|\bm{k}_q \bm{k}_a \rangle}{\omega + \epsilon_{\bm{k}_a} - \epsilon_{\bm{k}_i} - \epsilon_{\bm{k}_j}}
\end{align}
If you take a look at the second summation (the 2h1p one), you can see that if $p$ is occupied, then it is possible, for example, to have $\bm{k}_p = \bm{k}_i$, and hence a zero momentum transfer at the ERI center. Thus, if we do not include the G=0 component from the ouset in HF, we mistreat the situation where there might be a zero momentum transfer at an ERI center, and thus miss contributions to the self-energy.
\subsubsection{Solution to the problem of the shifted poles}
Tim's notes write that the many-body Hamiltonian based on the Ewald potential can be re-written as
\begin{align}
H= & -\sum_{i=1}^N \frac{1}{2} \nabla_i^2-\sum_{i=1}^N \sum_{A=1}^M z_A\left[v_{\mathrm{E}}\left(r_i, R_A\right)-v_{\mathrm{M}}\right] +\sum_{i=1}^N \sum_{j>i}^N\left[v_{\mathrm{E}}\left(r_i, r_j\right)-v_{\mathrm{M}}\right] 
\label{H_ewald} \\
& +\sum_{A=1}^M \sum_{B>A}^M z_A z_B\left[v_{\mathrm{E}}\left(R_A, R_B\right)-v_{\mathrm{M}}\right] +\frac{v_{\mathrm{M}}}{2}\left(N-\sum_A z_A\right)^2 \notag
\end{align}
where the final term vanishes for a neutral system. The shifted Ewald potential $v_{\mathrm{s}}(r) \equiv v_{\mathrm{E}}(r)-v_{\mathrm{M}}$ has the Fourier components
\begin{equation}
    v_{\mathrm{s}}(G)= \begin{cases}4 \pi / \Omega G^2 & G \neq 0 \\ -v_{\mathrm{M}} & G=0\end{cases}.
\label{vs_G}
\end{equation}
Because this is the homogeneous electron gas, there are no nuclei, so the second and fourth and last part of the final parentheses in \eqref{H_ewald} vanish. Thus, the Hamiltonian reduces to
\begin{equation}
H= -\sum_{i=1}^N \frac{1}{2} \nabla_i^2 +\sum_{\bm{G}} v_{\mathrm{s}}(G) + \frac{v_{\mathrm{M}}}{2} N^2
\label{H_ewald_simplified}
\end{equation}
Now, the IP is defined as the energy difference between the N and N-1 electron systems, so if the final term in \ref{H_ewald_simplified} did not exist, we could say that the IPs are equivalent to the occupied MO energies by Koopmans' theorem. However, because of the final term, we have that
\begin{equation}
    IP = -\left(E(N-1) - E(N)\right) = \epsilon_{\mathrm{i}}  - \frac{v_{\mathrm{M}}}{2}
\end{equation}
So the IPs should be shifted by $-v_{\mathrm{M}}/2$ to get the correct result. This is what I was doing to get the good looking results before this conversation all started.
\subsection{What are the implications of including the G=0 component for spectral functions?}
\subsubsection{Deriving orbital energies}
We know the form when G=0 is excluded, so with respect to that we don't modify the Coulomb matrix at all, but just the exchange matrix.
% The exchange potential is defined with
% \begin{align}
% K_{n \vec{k}}^\sigma(\vec{r}) \underbrace{\phi_{j k^*}(\vec{r})}_{A O} & =\left\{\int d^2 \vec{r}^{\vec{r}} \psi_{n \vec{k}}^{\sigma *}\left(\overrightarrow{r^*}\right) \frac{1}{\left|\vec{r}-\vec{r}^{\vec{r}}\right|} \phi_{j k^*}\left(\overrightarrow{r^*}\right)\right\} \underbrace{\psi_{n \vec{k}}^\sigma(\vec{r})}_{M O} \\
% K^\sigma(\vec{r}) & =\sum_{\vec{k}} \sum_{n, o c c} K_{n \vec{k}}^\sigma(\vec{r}) . \quad \text { (total exchange potential) }
% \end{align}
We are at the GPT, so we can neglect the $\vec{k}$ dependence of quantities. Thus, in the plane wave basis, we have
\begin{align}
K_{ p q}^\sigma & =\int_{\Omega} d^2 \vec{r} \phi_{p}^*(\vec{r}) K^\sigma(\vec{r}) \phi_{q }(\vec{r}) \\
& =\int_{\Omega} d^2 \vec{r} \phi_{p}^*(\vec{r}) \sum_{n, o c c}\left\{\int d^2 \vec{r}^{\prime} \psi_{n}^{\sigma *}\left(\vec{r^{\prime}}\right) \frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|} \phi_{q}\left(\vec{r^{\prime}}\right)\right\} \psi_{n}^\sigma(\vec{r}) \\
& =\int_{\Omega} d^2 \vec{r} \phi_{p }^*(\vec{r}) \sum_{n, o c c}\left\{\int d^2 \vec{r}^{\prime} \phi_{n }^{\sigma *}\left(\vec{r^{\prime}}\right) \frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|} \phi_{q }\left(\vec{r^{\prime}}\right)\right\} \phi_{n }^\sigma(\vec{r})
\label{K_exchange_initial} \\
&=\sum_{ij} P_{ ji}^\sigma \underbrace{\left< p_{} i_{} | j_{} q_{} \right>}_{*} \label{K_exchange_final} 
\end{align}
where we can do the simplification that leads to \ref{K_exchange_initial} because for the UEG, the MOs are the AOs. Now,
\begin{align}
* 
% &= \frac{1}{\Omega^2} \int_{\Omega} d^2 \vec{r} e^{i\left(\vec{G}_j-\vec{G}_p\right) \cdot \vec{r}}\left\{\int d^2 \vec{r}^{\prime} \frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|} e^{i\left(\vec{G}_q-\vec{G}_i\right) \cdot \vec{r}^{\prime}}\right\} \\
&= \frac{1}{\Omega^2} \int_{\Omega} d^2 \vec{r}  e^{i\left(\vec{G}_j-\vec{G}_p\right) \cdot \vec{r}}\left\{e^{i\left(\vec{G}_q-\vec{G}_i\right) \cdot \vec{r}}\right\}\left\{\int d^2 \vec{r}^{\prime} \frac{1}{\left|\vec{r}^{\prime}-\vec{r}\right|} e^{i\left(\vec{G}_q-\vec{G}_i\right) \cdot |\vec{r}^{\prime}-\vec{r}|}\right\} \\
&= \frac{1}{\Omega^2} \int_{\Omega} d^2 \vec{r}\left\{e^{i\left(\vec{G}_j-\vec{G}_p\right) \cdot \vec{r}}\right\}\left\{e^{i\left(\vec{G}_q-\vec{G}_i\right) \cdot \vec{r}}\right\} \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|}\left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + v_{\mathrm{M}}\Omega\delta_{\vec{G}_q,\vec{G}_i}\right) \\
% &= \frac{1}{\Omega^2} \cdot \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} + \Omega v_{\mathrm{M}}\right) \int_{\Omega} d^2 \vec{r} e^{i\left(\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right) \cdot \vec{r}} \\
% &= \frac{1}{\Omega^2} \cdot \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_q,\vec{G}_i}\right) \int_{\Omega} d^2 \vec{r} e^{i\left(\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right) \cdot \vec{r}} \\
% &= \frac{4 \pi}{\Omega\left|\vec{G}_q-\vec{G}_i\right|} \delta\left[\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right].
&= \frac{1}{\Omega} \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_q,\vec{G}_i}\right) \delta\left[\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right] \\
% &= \frac{1}{\Omega} \left(\frac{4 \pi}{\left|\vec{Q}\right|} \left(1-\delta_{\vec{Q},0}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{Q},0}\right) 
\end{align}
% where to get to the final line, we define the momentum transfer vector $\vec{Q}$ and demand that $\vec{Q}\equiv\vec{G}_q-\vec{G}_i = \vec{G}_p - \vec{G}_j$.
 Thus, the exchange matrix elements become
\begin{align}
% K_{ p q}^\sigma&= \frac{1}{\Omega}  \sum_{i j} P_{j i}^\sigma \frac{1}{\left|\left(\vec{G}_q-\vec{G}_i\right)\right|} \delta\left[\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right] \label{K_exchange_inter} \\
K_{ p q}^\sigma&= \frac{1}{\Omega}  \sum_{i j} P_{j i}^\sigma \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_q,\vec{G}_i}\right) \delta\left[\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right] \label{K_exchange_inter} \\
% &  =\frac{4 \pi}{\Omega} \sum_{\vec{Q}} P_{ p-\vec{Q}, q-\vec{Q}}^q \label{K_exchange_final}
&= \frac{1}{\Omega}  \sum_{i j} P_{p-(q-i), q -(q-i)}^\sigma \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_q,\vec{G}_i}\right) \delta\left[\left(\vec{G}_j-\vec{G}_p\right)+\left(\vec{G}_q-\vec{G}_i\right)\right] 
% &  =\frac{1}{\Omega} \sum_{\vec{Q}} P_{ p-\vec{Q}, q-\vec{Q}}^\sigma \left(\frac{4 \pi}{\left|\vec{Q}\right|} \left(1-\delta_{\vec{Q},0}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{Q},0}\right)
\end{align}
% where in the final line, we have defined the momentum transfer vector $\vec{Q}$, demanding that $\vec{Q}\equiv\vec{G}_q-\vec{G}_i = \vec{G}_p - \vec{G}_j$. 
Given that the kinetic and Coulomb matrices are unchanged, we can write the Fock matrix for the UEG as
\begin{align}
F_{ p q}^\sigma & = H_{ p q}^{\mathrm{kin}} + J_{ p q}^\sigma + K_{ p q}^\sigma \\
& = \delta_{ p q} \frac{|\vec{G}_p|^2}{2} +\frac{\delta_{pq}}{\Omega} \sum_{q-i} n^\sigma_{p-(q-i)} \left(\frac{4 \pi}{\left|\vec{G}_q-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_q,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_q,\vec{G}_i}\right) \\
& = \delta_{ p q} \frac{|\vec{G}_p|^2}{2} +\frac{\delta_{pq}}{\Omega} \sum_{i\in occ} \left(\frac{4 \pi}{\left|\vec{G}_p-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_p,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_p,\vec{G}_i}\right) 
\end{align}
where we have defined $n^\sigma_{p} \equiv P_{pp}^\sigma$ as the occupation number of orbital $p$ with spin $\sigma$, but because we are at zero temperature, $n^\sigma_{p}=0$ (unoccupied) or $1$ (occupied). Because the Fock matrix is diagonal, we can read off the orbital energies as
\begin{align}
\epsilon_{ p}^\sigma & = \frac{|\vec{G}_p|^2}{2} +\frac{1}{\Omega} \sum_{i\in occ} \left(\frac{4 \pi}{\left|\vec{G}_p-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_p,\vec{G}_i}\right) + \Omega v_{\mathrm{M}}\delta_{\vec{G}_p,\vec{G}_i}\right) \\
& = \frac{|\vec{G}_p|^2}{2} +\frac{1}{\Omega} \sum_{i\in occ} \frac{4 \pi }{\left|\vec{G}_p-\vec{G}_i\right|} \left(1-\delta_{\vec{G}_p,\vec{G}_i}\right) + v_{\mathrm{M}}n^\sigma_{p}
\end{align}
Thus, occupied orbitals get a shift of $v_{\mathrm{M}}$, while unoccupied orbitals are unchanged.
\subsubsection{Deriving IPs}
\subsection{Self-consistent cumulant with second-order self-energy}
\subsubsection{Basis transformation}
We want to evaluate the quantities in the sine-cosine basis, as this is simpler. But in the end, we will want the spectral function in the plane wave basis, and thus we need the Green's function in that basis. Now, the retarded Greens function in the time domain with the broadening factor $\eta$ can be written as
\begin{equation}
    G_{pp}(t) = -i \Theta(t) e^{-t(i \epsilon_p +\eta)} e^{C_{pp}(t)}
\end{equation}
where the cumulant is defined as
\begin{align}
    C_{pp}(t) &\equiv i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}\left(\omega+\epsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t} \\
 &= \frac{1}{2} \sum_{iab} \left< pi \left| \right| ab \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pi}^{ab}\right)} + \frac{1}{2} \sum_{ija} \left< pa \left| \right| ij \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pa}^{ij}\right)} \\
% \label{eq:cumulant_2nd_1}
&\overset{RHF}{=} \sum_{iab} \frac{(pa|ib)\left(2(pa|ib)- (pb|ia)\right)}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
\\&+\sum_{ija} \frac{(pi|aj)\left(2(pi|aj)- (pj|ai)\right)}{\left(\epsilon_{pa}^{ij}\right)^2} \left(e^{-i \epsilon_{pa}^{ij} t} +i \epsilon_{pa}^{ij} t -1 \right)
\end{align}
with $\epsilon_{pi}^{ab} = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i}$
and
$\epsilon_{pa}^{ij} = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}$. 
\subsubsection{Self-consistency}
Everything I present in the plots is one-shot. When I speak of GF2+C with analytic frequency integration, I am building the cumulant as
\begin{align}
    C_{pp}(t) &=\sum_{iab} \frac{(pa|ib)\left(2(pa|ib)- (pb|ia)\right)}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
\\&+\sum_{ija} \frac{(pi|aj)\left(2(pi|aj)- (pj|ai)\right)}{\left(\epsilon_{pa}^{ij}\right)^2} \left(e^{-i \epsilon_{pa}^{ij} t} +i \epsilon_{pa}^{ij} t -1 \right) \nonumber
\end{align}
with $\epsilon_{pi}^{ab} = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i}$ and
$\epsilon_{pa}^{ij} = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}$.
 As can be seen, this gives qualitatively the same result as GF2+C with numerical frequency integration, where I instead build the cumulant as
\begin{equation}
    C_{pp}(t) = \int d \omega \frac{\beta_{pp}(\omega)}{\omega^2} \left( e^{-i \omega t} + i \omega t -1 \right)
\label{eq:cumulant_beta}
\end{equation}
with $\beta_{pp}(\omega) = \frac{1}{\pi} |\operatorname{Im} \Sigma_{pp}(\omega + \epsilon_p)|$ with the self-energy defined in chemists notation as
\begin{align}
    \Sigma^{(2)}_{pq}(\omega)
    & = \sum_{iab} \frac{(pa|ib)\Big(2(qa|ib) - (qb|ia)\Big)}{\omega - \epsilon_a - \epsilon_b + \epsilon_i + i \eta} + \sum_{ija} \frac{\left( (pi|aj)(2(qi|aj) - (qj|ai)) \right)}{\omega - \epsilon_i - \epsilon_j + \epsilon_a + i \eta} 
\end{align}
or in physicists notation as
\begin{align}
    \Sigma^{(2)}_{pq}(\omega)
    & = \sum_{iab} \frac{\left<pi|ab\right>\left(2\left<qi|ab\right> - \left<qi|ba\right>\right)}{\omega - \epsilon_a - \epsilon_b + \epsilon_i + i \eta} + \sum_{ija} \frac{\left<pa|ij\right>\left(2\left<qa|ij\right> - \left<qa|ji\right>\right)}{\omega - \epsilon_i - \epsilon_j + \epsilon_a + i \eta}
\end{align}
If I remember correctly, our idea for a self consistent scheme was to solve equation \ref{eq:cumulant_beta} using
\begin{equation}
    \Sigma_{pp}(\omega) = \frac{1}{G^0_{pp}(\omega)} - \frac{1}{G_{pp}(\omega)}
% \left(G^0_{pp}(\omega)\right)^{-1} - \left(G_{pp}(\omega)\right)^{-1}
\end{equation}
In the initial trials, I have not been getting any useful results with the above. However, I notice that I only use under 1e4 frequency grid points. Should I try to get this scheme to work with something like 1e6 grid points or were you thinking of something different?
\newpage
This self-energy can then be used to compute a new cumulant $C_{pp}(t)$ as
\begin{align}
    C_{pp}(t) &= i \int \frac{d\omega}{2\pi} \frac{ \Sigma_{pp}\left(\omega+\epsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t} \\
&= i \int \frac{d\omega}{2\pi} \frac{\omega + i \eta - \frac{1}{G_{pp}(\omega + \epsilon_p)}}{(\omega + i \eta)^2} e^{-i \omega t} \\
&= i \int \frac{d\omega}{2\pi} \frac{\omega + i \eta}{(\omega + i \eta)^2} e^{-i \omega t} - i \int \frac{d\omega}{2\pi} \frac{1}{G_{pp}(\omega + \epsilon_p)(\omega + i \eta)^2} e^{-i \omega t} \\
&= i \int \frac{d\omega}{2\pi} \frac{e^{-i \omega t}}{\omega + i \eta} - i \int \frac{d\omega}{2\pi} \frac{1}{G_{pp}(\omega + \epsilon_p)(\omega + i \eta)^2} e^{-i \omega t} \\
&= \Theta(t)e^{-\eta t} - i \int \frac{d\omega}{2\pi} \frac{1}{G_{pp}(\omega + \epsilon_p)(\omega + i \eta)^2} e^{-i \omega t}
\end{align}
where we can use some quadrature to perform the latter integral. This cumulant can then be used to compute $G_{pp}(t)$ using the usual recipe, and then Fourier transformed to obtain $G_{pp}(\omega)$, which can then be used to compute a new self-energy, and so on, until convergence is reached. We still need to determine what measure will be used to determine if self-consistency has been reached.
\begin{equation}
    \begin{pmatrix}
|{\bm{K}_p}\rangle \\
|{\bm{-K}_p}\rangle
    \end{pmatrix}
= \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & i \\
1 & -i
\end{bmatrix}
\begin{pmatrix}
|\alpha_p\rangle \\
|\beta_p\rangle
\end{pmatrix}
\implies |\bm{K}_p\rangle = \frac{1}{\sqrt{2}} \left( |\alpha_p\rangle + i |\beta_p\rangle \right)
\end{equation} 
So the self energy (and also the cumulant as well as the Green's function) can be expressed as
\begin{align}
    \Sigma_{p p}(\omega)&\equiv\langle p| \hat{\Sigma}(\omega)|p\rangle \\
&= \frac{1}{2} \left( \langle \alpha_p| + -i \langle \beta_p| \right) \hat{\Sigma}(\omega) \left( |\alpha_p\rangle + i |\beta_p\rangle \right) \\
&= \frac{1}{2} \left( \Sigma_{\alpha_p \alpha_p}(\omega) + \Sigma_{\beta_p \beta_p}(\omega) + i \Sigma_{\alpha_p \beta_p}(\omega) - i \Sigma_{\beta_p \alpha_p}(\omega) \right)
\end{align}
Suppose that $p$ is the Fermi state, which in our case has wavevector $(1,0,0)$ and the complement is $(-1,0,0)$; in the plane wave basis, they may have non-consecutive indices, like 6 and 1, respectively. The sine-cosine basis is expressed as linear combinations of the two, so the sine and cosine states will now be in a consecutive order, say 5 and 6. I need to check that nothing changes if instead they occupy indices 1 and 2. Also, it is worth checking whether $\Sigma_{\alpha\beta} = \Sigma_{\beta\alpha}$ in the sine-cosin basis. If so, check if $\Sigma_{\alpha\alpha}=\Sigma_{\beta\beta}$ because, if so, that means the self-energy in the plane-wave basis might be equivalent to the self-energy in thee sine-cosine basis. 
To derive a form for $C_{pp}^{(2)}(t)$, start by equating the cumulant ansatz for the Green's function the Dyson equation, which gives
\begin{align}
C_{pp}^{(2)}(t) &\equiv i \int \frac{d\omega}{2\pi} \frac{ \tilde{\Sigma}_{pp}^{c,(2)}\left(\omega+\epsilon_p\right)}{(\omega + i \eta)^2} e^{-i \omega t} \\
 &= \frac{1}{2} \sum_{iab} \left< pi \left| \right| ab \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pi}^{ab}\right)} + \frac{1}{2} \sum_{ija} \left< pa \left| \right| ij \right>^2 \int \frac{d\omega}{2\pi} \frac{i e^{-i \omega t}}{\omega^2\left(\omega-\epsilon_{pa}^{ij}\right)} \\
% \label{eq:cumulant_2nd_1}
&\overset{RHF}{=} \sum_{iab} \frac{(pa|ib)\left(2(pa|ib)- (pb|ia)\right)}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
\\&+\sum_{ija} \frac{(pi|aj)\left(2(pi|aj)- (pj|ai)\right)}{\left(\epsilon_{pa}^{ij}\right)^2}
\left(e^{-i \epsilon_{pa}^{ij} t} +i \epsilon_{pa}^{ij} t -1 \right) \\
&\overset{SC}{=} \sum_{\tilde{p}}^{p_{\bm{K}}, p_{\bm{-K}}} \Bigg(\sum_{iab} \frac{(\tilde{p}i|ab)\left(2(\widetilde{p}i|ab)- (\widetilde{p}b|ia)\right)}{\left(\epsilon_{\widetilde{p}i}^{ab}\right)^2}
\left(e^{-i \epsilon_{\widetilde{p}i}^{ab} t} +i \epsilon_{\widetilde{p}i}^{ab} t -1 \right) \\& + \sum_{ija} \frac{(\tilde{p}i|aj)\left(2(\widetilde{p}i|aj)- (\widetilde{p}j|ai)\right)}{\left(\epsilon_{\widetilde{p}a}^{ij}\right)^2}
\left(e^{-i \epsilon_{\widetilde{p}a}^{ij} t} +i \epsilon_{\widetilde{p}a}^{ij} t -1 \right)\Bigg)  
\label{eq:cumulant_2nd_final}
\end{align}
where
$\epsilon_{pi}^{ab} = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i}$
and
$\epsilon_{pa}^{ij} = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}$. At this point we can stop and notice that if we want to determine use the sine-cosine basis for the evaluation of the self energy in the definition of the cumualant, we just need to do
\begin{equation}
    \Sigma_{p p}(\omega)=\langle p| \hat{\Sigma}(\omega)|p\rangle=\sum_{\alpha, \beta} U_{p \alpha} \Sigma_{\alpha \beta}^{(\mathrm{sc})}(\omega) U_{p \beta}^*,
\end{equation}
Now, we are told that this unitary transformation that allows us to move between the plane wave and sine-cosine basis is given by
\begin{align}
\mathbf{U} &= \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & 1 \\
 -i & i
\end{bmatrix}
\implies
\begin{bmatrix}|\mathbf{K},s \rangle \\
|\mathbf{K},c \rangle
\end{bmatrix} = \mathbf{U}^\dag \begin{bmatrix} |\mathbf{K} \rangle \\
|-\mathbf{K} \rangle
\end{bmatrix}
\end{align}
for a $\mathbf{K}\neq 0$ state from the plane wave basis.
\subsection{Derivation of second-order self-energy using RHF reference}
To derive this, we can start with the definition (we will just deal with the 2p1h channel for simplicity)
\begin{align}
    \Sigma_{pp}^{(2)}(\omega) =& \frac{1}{2}\sum_{iab} \frac{\langle pi || ab \rangle \langle ab || pi \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots \\
&= \frac{1}{2}\sum_{iab} \frac{\left( \langle pi | ab \rangle - \langle pi | ba \rangle \right)\left( \langle ab | pi \rangle - \langle ab | ip \rangle \right)}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots \\
&= \frac{1}{2}\sum_{iab} \frac{\langle pi | ab \rangle \langle ab | pi \rangle - \langle pi | ab \rangle \langle ab | ip \rangle - \langle pi | ba \rangle \langle ab | pi \rangle + \langle pi | ba \rangle \langle ab | ip \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots 
\end{align}
% But if we swap the dummy indices for the third term, we see that $\langle pi | ba \rangle \langle ab | qi \rangle = \langle qi | ab \rangle \langle ba | pi \rangle=\langle qi | ab \rangle \langle ab | ip \rangle$, which we can group together with the second term. Similarly, for the fourth term, we can swap $a \leftrightarrow b$ to get $\langle pi | ba \rangle \langle ab | ip \rangle = \langle pi | ab \rangle \langle ba | ip \rangle = \langle pi | ab \rangle \langle ab | pi \rangle$, which we can group together with the first term. Now assigning a spin variable to each center, this gives
But if we swap the dummy indices for the third term, we see that $\langle pi | ba \rangle \langle ab | pi \rangle = \langle pi | ab \rangle \langle ba | pi \rangle=\langle pi | ab \rangle \langle ab | ip \rangle$, which we can group together with the second term. Similarly, for the fourth term, we can swap $a \leftrightarrow b$ to get $\langle pi | ba \rangle \langle ab | ip \rangle = \langle pi | ab \rangle \langle ba | ip \rangle = \langle pi | ab \rangle \langle ab | pi \rangle$, which we can group together with the first term. Now assigning a spin variable to each center, this gives
\begin{align}
    \Sigma_{p^{+ }p^{+ }}^{(2)}(\omega) =& \frac{1}{2}\sum_{iab} \sum_{\beta\gamma \sigma }\frac{2 \langle p^{+} i^{\beta} | a^{\gamma } b^{\sigma } \rangle \langle a^{\gamma} b^{\sigma} | p^{+} i^{\beta} \rangle - 2 \langle p^{+} i^{\beta} | a^{\gamma} b^{\sigma} \rangle \langle b^{\sigma } a^{\gamma} | p^{+} i^{\beta} \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots \\
    =& \sum_{iab} \frac{2 \langle p i | a b \rangle \langle a b | p i \rangle - \langle p i | a b \rangle \langle b a | p i \rangle}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots \\
    =& \sum_{iab} \frac{\langle p i | a b \rangle \left( 2 \langle a b | p i \rangle - \langle b a | p i \rangle \right)}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \ldots
\end{align}
where in the first expression, because to start with the index $p$ is already constrained to have spin $+$, so $a$ must be $+$ as well, and we can accept 2 combinations of spin for the two-electron integrals ($\beta , \gamma = +,-$), while in the second expression, we can only accept 1 combinations of $\beta , \gamma = +$. For the expression of the off-diagonal self-energy, we can just accept Szabo's form in 3.79.
% &= \sum_{iab} \frac{\left( \langle pi | ab \rangle - \langle pi | ba \rangle \right)\left( \langle ab | pi \rangle - \langle ab | ip \rangle \right)}{\omega + \epsilon_i - \epsilon_a - \epsilon_b} + \sum_{ija} \frac{\left( \langle pa | ij \rangle - \langle pa | ji \rangle \right)\left( \langle ij | pa \rangle - \langle ij | ap \rangle \right)}{\omega + \epsilon_a - \epsilon_i - \epsilon_j} \\
In Joonho's paper, they say that 
% $$
% \begin{aligned}
% & \langle p q \mid r s\rangle=\frac{1}{\Omega} \frac{4 \pi}{\left|\mathbf{K}_p-\mathbf{K}_r\right|^2} \delta_{\mathbf{K}_p-\mathbf{K}_r, \mathbf{K}_q-\mathbf{K}_a} \\
% & \times\left(1-\delta_{\mathbf{K}_p \mathbf{K}_r}\right)
% \end{aligned}
% $$
\begin{equation}
\left< pq | rs \right> = \frac{1}{\Omega} \frac{4 \pi}{\left|\mathbf{K}_p-\mathbf{K}_r\right|^2} \delta_{\mathbf{K}_p-\mathbf{K}_r, \mathbf{K}_q-\mathbf{K}_s} \times\left(1-\delta_{\mathbf{K}_p , \mathbf{K}_r}\right)
\end{equation}
but I notice that I get the "better" results for the GF2 poles (i.e. closer to the exact result for $r_s=4$), if instead it is
\begin{equation}
\left< pq | rs \right> = \frac{1}{\Omega} \frac{4 \pi}{\left|\mathbf{K}_p-\mathbf{K}_r\right|^2} \delta_{\mathbf{K}_p-\mathbf{K}_r, \mathbf{K}_s-\mathbf{K}_q} \times\left(1-\delta_{\mathbf{K}_p , \mathbf{K}_r}\right).
\end{equation}
Making this change, also makes the MP2 energy match that obtained from the sine-cosine basis. I also notice that this is the momentum conservation condition that iPie suggests in the below function for the two-electron integrals in the plane wave basis. This is also the condition that seems suggested in the review. 
\newpage
\begin{equation}
    i+j=a+b \implies i-a = b - j
\end{equation}
To make things simpler, instead of working in the plan wave bases, we can transform to the sine-cosine basis. I need to make sure that I am consistent with this basis choice, though. Below, I go through the logic, to ensure consistency.


\subsubsection{Second-order self-energy in sine-cosine basis}
The retarded, closed shell expression given by Szabo is
\begin{align}
    \Sigma^{(2)}_{pq}(\omega) &= \sum_{iab} \frac{\langle ab | pi \rangle \Big(2 \langle qi | ab \rangle - \langle iq | ab \rangle\Big)}{\omega - \epsilon_a - \epsilon_b + \epsilon_i + i \eta} + \sum_{ija} \frac{\langle ij | pa \rangle \Big(2 \langle qa | ij \rangle - \langle aq | ij \rangle\Big)}{\omega - \epsilon_i - \epsilon_j + \epsilon_a + i \eta} \\
    & = \sum_{iab} \frac{(pa|ib)\Big(2(qa|ib) - (qb|ia)\Big)}{\omega - \epsilon_a - \epsilon_b + \epsilon_i + i \eta} + \sum_{ija} \frac{\left( (pi|aj)(2(qi|aj) - (qj|ai)) \right)}{\omega - \epsilon_i - \epsilon_j + \epsilon_a + i \eta} 
\end{align}
Now, for the purposes of the diagonal cumulant, we want to be able to compute $\Sigma ^{(2)}(\tilde{p}, \omega)$, where $\tilde{p}$ is the state index in the plane wave basis. Because we want to compute the above expressions using the standard quantum chemistry methods, instead of directly computing $\Sigma^{(2)}_{\tilde{p}\tilde{p}}(\omega)$, we can transform to the sine-cosine basis as
\begin{align}
{\Sigma}^{(2),R}_{pq}(\omega) & = \sum_{m n} U_{p m} {\Sigma}^{(2),R}_{mn}(\omega) U_{n q}^{\dagger} \\
\end{align}
But we must take into account the correct mapping between the plane wave and sine-cosine basis, leading to
\begin{equation}
{\Sigma}^{(2),R}(p, \omega)\equiv{\Sigma}^{(2),R}_{pp}(\omega)=\frac{1}{2}\left( \Sigma ^{(2),R}_{c c}(\omega )+\Sigma^{(2),R}_{s s}(\omega )\right)+\frac{i}{2}\left(\Sigma^{(2),R}_{s c}(\omega )-\Sigma^{(2),R}_{c s}(\omega )\right)
% \Sigma_{c c}^{\prime}+\Sigma_{s s}^{\prime}\right)+\frac{i}{2}\left(\Sigma_{s c}^{\prime}-\Sigma_{c s}^{\prime}\right)
\end{equation}
where $c$ and $s$ refer to the cosine and sine functions, respectively. 
% But this expression does not take into account the Madelung correction. To include this, we can shift all single particle energies in the energy denominators by $-\frac{\xi}{2}$ Hartrees. So the corrected expression becomes
% \begin{align}
% {\Sigma}_{\text{Mad}}^{c,(2),R}(p, \omega) &= \frac{2\pi}{V} \left( \sum_{\mathbf{k}_i \in O; \,\mathbf{k}_a , \mathbf{k}_b \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p - \mathbf{k}_a|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_b|^2} \right]^2 }{\omega - (\epsilon_{\mathbf{k}_a} - \frac{v_M}{2}) - (\epsilon_{\mathbf{k}_b} - \frac{v_M}{2}) + (\epsilon_{\mathbf{k}_i} - \frac{v_M}{2}) + i \eta}  \right.\\
% & \left. + \sum_{\mathbf{k}_i,\mathbf{k}_j \in O;\, \mathbf{k}_a \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p-\mathbf{k}_i|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_j|^2} \right]^2 }{\omega - (\epsilon_{\mathbf{k}_i} - \frac{v_M}{2}) - (\epsilon_{\mathbf{k}_j} - \frac{v_M}{2}) + (\epsilon_{\mathbf{k}_a} - \frac{v_M}{2}) + i \eta} \right) \\
% &= \frac{2\pi}{V} \left( \sum_{\mathbf{k}_i \in O; \,\mathbf{k}_a , \mathbf{k}_b \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p - \mathbf{k}_a|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_b|^2} \right]^2 }{\left(\omega + \frac{v_M}{2}\right) - \epsilon_{\mathbf{k}_a} - \epsilon_{\mathbf{k}_b} + \epsilon_{\mathbf{k}_i} + i \eta}  \right.\\
% & \left. + \sum_{\mathbf{k}_i,\mathbf{k}_j \in O;\, \mathbf{k}_a \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p-\mathbf{k}_i|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_j|^2} \right]^2 }{\left(\omega + \frac{v_M}{2}\right) - \epsilon_{\mathbf{k}_i} - \epsilon_{\mathbf{k}_j} + \epsilon_{\mathbf{k}_a} + i \eta} \right) \nonumber \\
% \implies \Sigma_{\text{Mad}}^{c,(2),R}(p, \omega - \frac{v_M}{2}) &= \frac{2\pi}{V} \left( \sum_{\mathbf{k}_i \in O; \,\mathbf{k}_a , \mathbf{k}_b \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p - \mathbf{k}_a|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_b|^2} \right]^2 }{\omega - \epsilon_{\mathbf{k}_a} - \epsilon_{\mathbf{k}_b} + \epsilon_{\mathbf{k}_i} + i \eta}  + \sum_{\mathbf{k}_i,\mathbf{k}_j \in O;\, \mathbf{k}_a \in V} \frac{\left[ \frac{2}{|\mathbf{k}_p-\mathbf{k}_i|^2} - \frac{1}{|\mathbf{k}_p - \mathbf{k}_j|^2} \right]^2 }{\omega - \epsilon_{\mathbf{k}_i} - \epsilon_{\mathbf{k}_j} + \epsilon_{\mathbf{k}_a} + i \eta} \right)
% \end{align}
% and we have that $-2 \times 2.837297 \times\left(\frac{3}{4 \pi}\right)^{1 / 3} N^{-1 / 3} r_{\mathrm{s}}^{-1}=\xi = -2 v_M$, so $\frac{v_M}{2} = -\frac{\xi}{4}$.
It will be more convenient to work in the sine-cosine basis, here. The transformation that allows us to move between the plane wave and sine-cosine basis is given by
\begin{align}
\mathbf{U} &= \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & 1 \\
 -i & i
\end{bmatrix}
\implies
\begin{bmatrix}|\mathbf{K},s \rangle \\
|\mathbf{K},c \rangle
\end{bmatrix} = \mathbf{U}^\dag \begin{bmatrix} |\mathbf{K} \rangle \\
|-\mathbf{K} \rangle
\end{bmatrix}
\end{align}
for a $\mathbf{K}\neq 0$ state from the plane wave basis.
But we are just interested in computing the self energy for the state $\Sigma (\mathbf{K}, \omega)$, so we just care about
\begin{align}
\begin{bmatrix}
    s \\ c
\end{bmatrix}
&= \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & 1 \\
 -i & i
\end{bmatrix} \begin{bmatrix}
    1 \\ 0
\end{bmatrix} = \frac{1}{\sqrt{2}} \begin{bmatrix}
1 \\ -i
\end{bmatrix}
\end{align}
After some algebra, we are left with the fact that
\begin{equation}
{\Sigma}^{c,(2),R}(p, \omega)=\frac{1}{2}\left(\Sigma_{c c}^{\prime}+\Sigma_{s s}^{\prime}\right)+\frac{i}{2}\left(\Sigma_{s c}^{\prime}-\Sigma_{c s}^{\prime}\right)
\end{equation}
% \subsubsection{GF2 Poles}
% To determine this, we want to solve the QP equation, which involves optimizing the objective function defined as
% \begin{equation}
% \omega - \varepsilon_p - \operatorname{Re}\left[\Sigma^{c,(2),R}(p, \omega)\right] = 0
% \end{equation}
% But due to the Madelung correction, we actually want to solve
% \begin{equation}
% \omega - \left( \varepsilon_p - \frac{v_M}{2} \right) - \operatorname{Re}\left[\Sigma^{c,(2),R}(p, \left(\omega + \frac{v_M}{2}\right)\right] = 0
% \end{equation}
% It can be shown that the frequency dependent spectral function can be expressed in terms of the self-energy as follows:
% \begin{align}
% A(p, \omega) &= \frac{1}{\pi} \frac{\left|\Sigma^{\prime \prime}(p, \omega)\right|}{\left[\omega+\mu-\varepsilon_{p}-\Sigma^{\prime}(p, \omega)\right]^2+\left[\Sigma^{\prime \prime}(p, \omega)\right]^2}
% \end{align}
% where $\Sigma ^c (p, \omega) = \Sigma^{\prime}(p, \omega) + i \Sigma^{\prime \prime}(p, \omega)$.
\subsection{Derivation of the analytic form for GF2+C}
We can start with
\begin{equation}
    C_{pp}^{(2)}(t) = \frac{1}{2}\sum_{iab} \frac{\left< pi \left| \right| ab \right>^2}{\left(\Delta_{pa}^{\mu}\right)^2}
\left(e^{-i \Delta_{pa}^{\mu} t} +i \Delta_{pa}^{\mu} t -1 \right)
+\frac{1}{2}\sum_{ija} \frac{\left< pa \left| \right| ij \right>^2}{\left(\Delta_{pi}^{\nu}\right)^2}
\left(e^{-i \Delta_{pi}^{\nu} t} +i \Delta_{pi}^{\nu} t -1 \right)
\end{equation}
We can define $\zeta_{pa\mu} = \frac{\left< pi \left| \right| ab \right>^2}{\left(\Delta_{pa}^\mu\right)^2}$ and $\zeta_{pi\nu} = \frac{\left< pa \left| \right| ij \right>^2}{\left(\Delta_{pi}^\nu\right)^2}$ with $\Delta_{pa}^\mu = \epsilon_{a}+\epsilon_{b}-\epsilon_{p}-\epsilon_{i} - i \eta $ and $\Delta_{pi}^\nu = \epsilon_{i}+\epsilon_{j}-\epsilon_{p}-\epsilon_{a}-i\eta$, where $\mu$ and $\nu$ describe the OV pairs $i \to b$ and $a \to j$, respectively. Then, we can write the retarded Green's function as
\begin{align}
    G(p,t) &= -i \Theta(t) e^{-i \epsilon_p t} \exp \left[ \frac{1}{2}\sum_{i\nu} \zeta_{pi\nu} \left(e^{-i \Delta_{pi}^\nu t} +i \Delta_{pi}^\nu t -1 \right) +\frac{1}{2}\sum_{a\mu} \zeta_{pa\mu} \left(e^{-i \Delta_{pa}^\mu t} +i \Delta_{pa}^\mu t -1 \right) \right] \\
    &= -i \Theta(t) \underbrace{\exp \left\{-\frac{1}{2}\left( \sum_{i\nu} \zeta_{pi\nu} + \sum_{a\mu} \zeta_{pa\mu} \right)\right\}}_{Z_p^{QP}} \times \exp \left\{-i \overbrace{\left( \epsilon_p - \frac{1}{2} \sum_{i\nu} \zeta_{pi\nu} \Delta_{pi}^\nu - \frac{1}{2} \sum_{a\mu} \zeta_{pa\mu} \Delta_{pa}^\mu \right)}^{\epsilon_p^{QP}} t\right\} \\
    & \quad \times \exp \left\{ \frac{1}{2}\left(\sum_{i\nu} \zeta_{pi\nu} e^{-i \Delta_{pi}^\nu t} + \sum_{a\mu} \zeta_{pa\mu} e^{-i \Delta_{pa}^\mu t} \right) \right\} \\
&= -i \Theta(t) Z_p^{QP} e^{-i \epsilon_p^{QP} t} \exp \left\{ \frac{1}{2}\left(\sum_{i\nu} \zeta_{pi\nu} e^{-i \Delta_{pi}^\nu t} + \sum_{a\mu} \zeta_{pa\mu} e^{-i \Delta_{pa}^\mu t} \right) \right\}
% &= -i \Theta(t) \exp \left\{-\frac{1}{2}\left( \sum_{iab} \zeta_{piab} + \sum_{ija} \zeta_{pij a} \right)\right\} \exp \left\{-i \left( \epsilon_p - \frac{1}{2} \sum_{iab} \zeta_{piab} \varepsilon_{pi}^{ab} - \frac{1}{2} \sum_{ija} \zeta_{pij a} \varepsilon_{pa}^{ij} \right) t\right\} \\
% & \quad \times \exp \left\{ \frac{1}{2}\sum_{iab} \zeta_{piab} e^{-i \varepsilon_{pi}^{ab} t} + \frac{1}{2}\sum_{ija} \zeta_{pij a} e^{-i \varepsilon_{pa}^{ij} t} \right\}
\end{align}
where we have defined the quasiparticle weight $Z_p^{QP}$ and the quasiparticle energy $\epsilon_p^{QP}$. 
\begin{tcolorbox}
It is worth checking that we satisfy 
\begin{align}
\epsilon_p^{QP} & = \epsilon_p - \frac{1}{2} \left(\sum_{i\nu} \zeta_{pi\nu} \Delta_{pi}^\nu + \sum_{a\mu} \zeta_{pa\mu} \Delta_{pa}^\mu\right) \\
& = \epsilon_p - \frac{1}{2} \left(\sum_{i\nu} \frac{\left< pa \left| \right| ij \right>^2}{\Delta_{pi}^\nu} + \sum_{a\mu} \frac{\left< pi \left| \right| ab \right>^2}{\Delta_{pa}^\mu}\right) \\
& = \epsilon_p + \Sigma_{pp}^{(2)}( \epsilon_p)
\end{align}
and
\begin{align}
Z_p^{QP} & = \exp\left(-\frac{1}{2}\left[ \sum_{i\nu} \zeta_{pi\nu} - \sum_{a\nu} \zeta_{pa\nu}\right] \right) \\
& = \exp\left(\left[\frac{\partial \Sigma_{pp}^{(2)}(\omega)}{\partial \omega}\right]_{\omega = \epsilon_p^{HF}}\right) \\
\end{align}
where we have used the fact that $\Sigma_{pp}^{(2)}(\omega) = \frac{1}{2} \left(\sum_{i\nu} \frac{\left< pa \left| \right| ij \right>^2}{\omega - \Delta_{pi}^\nu} + \sum_{a\mu} \frac{\left< pi \left| \right| ab \right>^2}{\omega - \Delta_{pa}^\mu}\right) \implies \left[\frac{\partial \Sigma_{pp}^{(2)}(\omega)}{\partial \omega}\right]_{\omega = \epsilon_p^{HF}} = -\frac{1}{2} \left(\sum_{i\nu} \frac{\left< pa \left| \right| ij \right>^2}{\left(\Delta_{pi}^\nu\right)^2} + \sum_{a\mu} \frac{\left< pi \left| \right| ab \right>^2}{\left(\Delta_{pa}^\mu\right)^2}\right)$.
\end{tcolorbox}
Next, we perform the Fourier transform analytically, inserting the positive infinitesimal where appropriate:
\begin{align}
G(p, \omega) &= \int_{-\infty}^{\infty} dt\, e^{i \omega t} G(p,t) \\
&= -i Z_p^{QP} \int_0^{\infty} dt\, e^{i (\omega - \epsilon_p^{QP}) t} \exp \left\{ \frac{1}{2}\left(\sum_{i\nu} \zeta_{pi\nu} e^{-i \Delta_{pi}^\nu t} + \sum_{a\mu} \zeta_{pa\mu} e^{-i \Delta_{pa}^\mu t} \right) \right\} \\
&= -i Z_p^{QP} \int_0^{\infty} dt\, e^{i (\omega - \epsilon_p^{QP}) t} \left( 1 + \frac{1}{2}\sum_{i\nu} \zeta_{pi\nu} e^{-i \Delta_{pi}^\nu t} + \frac{1}{2}\sum_{a\mu} \zeta_{pa\mu} e^{-i \Delta_{pa}^\mu t} + \ldots \right) \\
&= -i Z_p^{QP} \int_0^{\infty} dt\, e^{-\eta + i (\omega - \epsilon_p^{QP}) t}\\
& - \frac{i}{2}Z_p^{QP}\sum_{i\nu} \zeta_{pi\nu} \int_0^{\infty} dt\, e^{-\eta + i (\omega - \epsilon_p^{QP} - \Delta_{pi}^\nu) t}\\
& - \frac{i}{2}Z_p^{QP}\sum_{a\mu} \zeta_{pa\mu} \int_0^{\infty} dt\, e^{-\eta + i (\omega - \epsilon_p^{QP} - \Delta_{pa}^\mu) t} + \ldots \\
&= \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i \eta} + \frac{1}{2} Z_p^{QP} \sum_{i\nu} \frac{\zeta_{pi\nu}}{\omega - \epsilon_p^{QP} - \Delta_{pi}^\nu + i \eta} + \frac{1}{2} Z_p^{QP} \sum_{a\mu} \frac{\zeta_{pa\mu}}{\omega - \epsilon_p^{QP} - \Delta_{pa}^\mu + i \eta} + \ldots
\end{align}
Then, proceeding as in the GW+C case, we can write down the spectral function as
\begin{align}
A(p, \omega) 
& = -\frac{1}{\pi}\left[\frac{\left(\operatorname{Re} Z_p^{QP}\right)\left(\operatorname{Im} \epsilon_p^{QP}\right) + \left(\operatorname{Im} Z_p^{QP}\right)\left(\omega - \operatorname{Re} \epsilon_p^{QP}\right)}{\left(\omega - \operatorname{Re} \epsilon_p^{QP}\right)^2 + \left(\operatorname{Im} \epsilon_p^{QP}\right)^2}\right.\\
& \left. + \sum_{i\nu} \frac{\left(\operatorname{Re} Z_{pi\nu}^{sat}\right)\left(\operatorname{Im} \epsilon_{pi\nu}^{sat}\right) + \left(\operatorname{Im} Z_{pi\nu}^{sat}\right)\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat}\right)}{\left(\omega - \operatorname{Re} \epsilon_{pi\nu}^{sat}\right)^2 + \left(\operatorname{Im} \epsilon_{pi\nu}^{sat}\right)^2} + \ldots \right]
\end{align}
where we have defined the satellite weights and energies as
\begin{align}
Z_{pi\nu}^{sat} & = \frac{1}{2} Z_p^{QP} \zeta_{pi\nu} \\
\epsilon_{pi\nu}^{sat} & = \epsilon_p^{QP} + \Delta_{pi}^\nu
\end{align}
and similarly for the $a\mu$ terms.
To understand how the FFT comes about, we can analytically carry it out. We started with the non-interacting Green's function in the time domain as
\begin{equation}
    G^0_{pp}(t) = -i \Theta(t) e^{-t(i \epsilon_p + \eta)}
\end{equation}
Then, the FFT provides a map between $t_n$ and $\omega_m$ as
\begin{align}
G^0_{pp}(\omega_m) &= -i \sum_{n=0}^{N_T - 1} e^{i \omega_m t_n} e^{-t_n (i \epsilon_p + \eta)} \\
&= -i \sum_{n=0}^{N_T - 1} e^{t_n (i \omega_m - i \epsilon_p - \eta)}
\end{align}
with $t_n = n \Delta t$ with $\Delta t = np.float64(1.0000150001500014)$ and $N_T = 100000$. Then, $\omega_m = \text{np.fft.fftshift(np.fft.fftfreq(len(times), d=dt) * 2.0 * np.pi)}$. I get $\Delta \omega = 2 \pi / (N_T \Delta t) = 6.283139999628673e-05$. 
How is this connected to the standard result for the non-interacting Green's function in frequency space, which is
\begin{equation}
    G^0_{pp}(\omega) = \frac{1}{\omega - \epsilon_p + i \eta}
\end{equation}

\subsection{Taking advantage of connection between EOMs}

We use the formula $\mathcal{L}\{(f*g)(t)\}(s)=\mathcal{L}\{f(t)\}(s) \mathcal{L}\{g(t)\}(s)$ for the Laplace transform of a convolution in the below.
\subsubsection{EOM with the retarded self energy}
We know the retarded Green's function satisfies the equation of motion in the time domain:
\begin{align}
    (i\partial_t - \epsilon_0) G^R(t) - \int_0^t d\tau\, \Sigma^R(t - \tau)\, G^R(\tau) &= 0 \label{eq:eom_retarded} \\
\implies i\mathcal{L}\{ \partial_t G^R(t)\}(s) - \epsilon_0 \mathcal{L} \{ G^R(t)\}(s) - \mathcal{L}\left\{\int_0^t d\tau\, \Sigma^R(t - \tau)\, G^R(\tau)\right\}(s) &= 0 \\
 i \left( s \mathcal{L} \{ G^R(t)\}(s) -G^R(0)\right)- \epsilon_0 \mathcal{L} \{ G^R(t)\}(s) - \mathcal{L}\{\Sigma^R(t)\}(s) \mathcal{L}\{G^R(t)\}(s) &= 0\\
\left[s + i\epsilon_0 + i\mathcal{L}\{\Sigma^R(t)\}(s)\right] \mathcal{L}\{G^R(t)\}(s) &= -i \\
\end{align}
where we used the boundary condition $G^R(0) = -i$.
This implies that
\begin{equation}
    \mathcal{L}\{G^R(t)\}(s) = \frac{-i}{s + i\epsilon_0 + i\mathcal{L}\{\Sigma^R(t)\}(s)}.
\end{equation}
With the standard analytic continuation $s \rightarrow -i\omega + \eta$, we find
\begin{align}
    G^R(-i\omega + \eta) &= \frac{-i}{-i\omega + \eta + i\epsilon_0 + i\mathcal{L}\{\Sigma^R(t)\}(-i\omega + \eta)} \times \frac{i}{i}\\
    &= \frac{1}{\omega - \epsilon_0 - \mathcal{L}\{\Sigma^R(t)\}(-i\omega + \eta) + i\eta} \\
   \implies  G^R(\omega) &= \frac{1}{\omega - \epsilon_0 - \Sigma^R(\omega) + i0^+}
\end{align}
\subsubsection{EOM with the retarded cumulant}
It is also valid to replace the convolution term in \eqref{eq:eom_retarded} with the time derivative of the cumulant. Considering the Laplace transform of just this term, we have
\begin{align}
\mathcal{L}\left\{\dot{C}^R(t)G^R(t)\right\}(s)
&=\int_0^\infty dt\, e^{-s t} \dot{C}^R(t) \left(-i e^{-i \epsilon_0 t} e^{C^R(t)}\right) \\
&= -i \int_0^\infty e^{-t(s + i\epsilon_0)} \frac{d}{dt}\big(e^{C^R(t)}\big)\, dt \label{eq:integration_by_parts}\\
&= i - i(s + i\epsilon_0)\int_0^\infty e^{t(s + i\epsilon_0)} e^{C^R(t)}\,dt \label{id}\\
&= i - i(s + i\epsilon_0)\mathcal{L}\{G^R(t)\}(s)
\end{align}
where we used integration by parts.
\footnote{\begin{align}
\int_0^\infty e^{-t(s + i\epsilon_0)} \frac{d}{dt}e^{C^R(t)}\,dt
&= \left[e^{-t(s + i\epsilon_0)} e^{C^R(t)}\right]_0^\infty 
+ (s + i\epsilon_0)\int_0^\infty e^{-t(s + i\epsilon_0)} e^{C^R(t)}\,dt \\
&= -1 + (s + i\epsilon_0)\int_0^\infty e^{-t(s + i\epsilon_0)} e^{C^R(t)}\,dt
\end{align}}
\subsubsection{EOM from Nakajima-Zwanzig}
The Nakajima-Zwanzig equation for a correlation function $\mathcal{A}(t)$ is given by
\begin{equation}
\dot{\mathcal{A}}(t) = \mathcal{A}(t) {\Omega_1} - \int_{0}^{t} d \tau\, \mathcal{A}(t - \tau) \mathcal{K}_1(\tau) + D(t)
\label{eq:GQME}
\end{equation}
So it is useful to consider the term involving the memory kernel. Its Laplace transform is
\begin{align}
\mathcal{L}\left\{\mathcal{A}(t)*\mathcal{K}_1(t)\right\}(s) &= \mathcal{L}\{\mathcal{A}(t)\}(s) \mathcal{L}\{\mathcal{K}_1(t)\}(s)
\end{align}
In order to make more progress, we would want to equate
\begin{align}
\mathcal{L}\left\{\mathcal{A}(t)*\mathcal{K}_1(t)\right\}(s) &= \mathcal{L}\left\{\dot{C}^R(t)G^R(t)\right\}(s) \\
\implies \mathcal{L}\{\mathcal{A}(t)\}(s) \mathcal{L}\{\mathcal{K}_1(t)\}(s) &= i - i(s + i\epsilon_0)\mathcal{L}\{G^R(t)\}(s) 
\end{align}
It would be nice to solve for $\mathcal{L}\{G^R(t)\}(s) $ in terms of $\mathcal{L}\{\mathcal{K}_1(t)\}(s)$ now, but to do so, we would need to establish a relationship between $\mathcal{L}\{G^R(t)\}(s)$ and $\mathcal{L}\{\mathcal{A}(t)\}(s)$. We know that the relationship between the fermionic retarded Green function $G^R(t) = -i \theta(t) \langle \{ \hat{\mu}(t), \hat{\mu}(0) \} \rangle$ and the autocorrelation function $\mathcal{A}(t)= \langle\hat{\mu}(t) \hat{\mu}(0)\rangle$ of Nakajima-Zwanzig is given by
\begin{align}
G^R(t) &= -i \theta(t) \left[\mathcal{A}(t) + \mathcal{A}(-t)\right]\\
\implies \mathcal{L}\{G^R(t)\}(s) &= -i \mathcal{L}\{ \left[\mathcal{A}(t) + \mathcal{A}(-t)\right]\}(s) \\
&= -i \left[\mathcal{L}\{\mathcal{A}(t)\}(s) + \mathcal{L}\{\mathcal{A}(-t)\}(s)\right] \\
 &\overset{?}{=} -i \mathcal{L}\{ \left[\mathcal{A}(t) + \mathcal{A}^*(t)\right]\}(s) \label{eq:questionable_step}\\
&= -2i \mathcal{L}\{\Re[\mathcal{A}(t)]\}(s) 
% & = -i \theta(t) \left[\mathcal{A}(t) + \mathcal{A}^*(t)\right] \\
% &= -i \theta(t) \left[ \Re\left[\mathcal{A}(t)\right] + i \Im\left[\mathcal{A}(t)\right] + \Re\left[\mathcal{A}^*(t)\right] - i \Im\left[\mathcal{A}(t)\right]\right] \\
% &= -2i \theta(t) \Re\left[\mathcal{A}(t)\right] \\
% \implies \mathcal{L}\{\frac{iG^R(t)}{2}\}(s) &=  \mathcal{L}\{ \Re\left[\mathcal{A}(t)\right]\}(s) \quad \forall t>0 \\
% \frac{i}{2} \int_0^\infty dt\, e^{-s t} G^R(t) &= \int_0^\infty dt\, e^{-s t} \Re\left[\mathcal{A}(t)\right] \\
\end{align}
The last two equalities only hold if the operators $\hat{\mu}(t)$ that make up the autocorrelation function $\mathcal{A}(t)$ are Hermitian. The fermionic second quantization operators are not Hermitian though. Only observables are Hermitian, which is why they were able to use the property leading to equation \eqref{eq:questionable_step} in Eq. 35-36 of \emph{Any type of spectroscopy can be efficiently simulated on a quantum computer}.
\subsection{SC-CE}

\subsubsection{My derivation}
 The cumulant ansatz for the retarded Green's function is:
\begin{equation}
    G^R(t)=\underbrace{-i \theta(t) e^{-i \epsilon_0 t}}_{G_0^R(t)} e^{C^R(t)} .
\end{equation}
Note that because this is for the retarded Green's function, we can assume that $t>0$ when differentiating, so $\theta(t)=1$. 
Differentiating with respect to time gives:
\begin{align}
    \partial_t G^R(t)&=-i\partial_t\left(e^{-i \epsilon_0 t} e^{C^R(t)}\right)\\
    &= -i \epsilon_0 G^R(t) - i \dot{C}^R(t) G^R(t)
\end{align}
% Notice that a product in the time domain is equivalent to a convolution integral in the frequency domain, so $\dot{C}^R(t) G^R(t) = G^R(t)\dot{C}^R(t) = \int_{-\infty}^\infty d \tau G^R\left(t-\tau\right) \dot{C}^R\left(\tau\right) = \int_0^t d \tau G^R\left(t-\tau\right) \dot{C}^R\left(\tau\right)$. We have been able to change the bounds of the integral from $[-\infty, \infty]\rightarrow [0,t]$ because we are dealing with retarded quantities, i.e. $\dot{C}^R\left(\tau\right) = 0 \quad \forall\quad  \tau<0$ and $G^R\left(t-\tau\right) = 0 \quad \forall\quad  \tau>t$.
%  Plugging this in gives:
% \begin{equation}
%     \partial_t G^R(t)=-i \epsilon_0 G^R(t)-\int_0^t d \tau G^R\left(t-\tau\right) \dot{C}^R\left(\tau\right) .
% \end{equation}
 Now, the equation of motion
\footnote{
The Nakajima-Zwanzig equation for a correlation function $\mathcal{A}(t)$ is given by
\begin{equation}
\dot{\mathcal{A}}(t) = \mathcal{A}(t) {\Omega_1} - \int_{0}^{t} d \tau\, \mathcal{A}(t - \tau) \mathcal{K}_1(\tau) + D(t)
\label{eq:GQME}
\end{equation}
Since we know the connection $\int_{0}^{t} d \tau\, \mathcal{A}(t - \tau) \mathcal{K}_1(\tau) = i \dot{C}^R(t) G^R(t) = \int_0^t d \tau G^R(t-\tau) \Sigma^R(\tau)$ and the outer definitions involve convolutions, we might be able to make some progress by demanding equality of their Laplace transforms.}
for the retarded Green's function in the Dyson formulation with the self energy $\Sigma$ is given by
\begin{align}
 \partial_t G^R(t)&=-i \epsilon _0 G^R(t)-i \int_0^t d \tau G^R(t-\tau) \Sigma^R(\tau)
\end{align}
% Equating the two gives an expression for the cumulant derivative:
% \begin{align}
% \dot{C}^R(t)G^R(t) &= \int_0^t d \tau G^R(t-\tau) \Sigma^R(\tau)\\
% &= \int_0^t d \tau G^R(t-\tau) \left[\left(G_0^R(\tau)\right)^{-1} - \left(G^R(\tau)\right)^{-1} \right] \\
% \implies \dot{C}^R(t)&=\int_0^t d \tau G^R(t-\tau) \left[\left(G_0^R(\tau)\right)^{-1} - \left(G^R(\tau)\right)^{-1} \right] \left(G^R(t)\right)^{-1} \\
% &=\int_0^t d \tau G^R(t-\tau) \left(G_0^R(\tau)\right)^{-1} \left(G^R(t)\right)^{-1} - \int_0^t d \tau G^R(t-\tau) \left(G^R(\tau)\right)^{-1} \left(G^R(t)\right)^{-1} \\
% \end{align}
Equating the two gives an expression for the cumulant derivative:
\begin{align}
\dot{C}^R(t)G^R(t) = \int_0^t d \tau G^R(t-\tau) \Sigma^R(\tau)
\end{align}
From here there are two directions I have in mind. Firstly, the Kowalski paper gave the EOM for the retarded core-hole cumulant as $-i\frac{d C_c^R(t)}{dt} = \left< \phi \left| \bar{H}_N(t) \right| \phi \right> = \sum_{ia} f_{ia} t_i^a + \frac{1}{2} \sum_{ijab} v_{ij}^{ab} t_j^b t_i^a$. I could plug this in and see.

 Secondly, we also know that 
\begin{align}
i \dot{C}^R(t) G^R(t) &= \int_{0}^{t} d \tau\, \mathcal{A}(t - \tau) \mathcal{K}_1(\tau)  \\  
\implies \mathcal{L}\left\{i \dot{C}^R(t) G^R(t)\right\}(s) &= \mathcal{L}\left\{\int_{0}^{t} d \tau\, \mathcal{A}(t - \tau) \mathcal{K}_1(\tau)\right\}(s)
\end{align}
where the RHS comes from the Nakajima-Zwanzig equation \eqref{eq:GQME} and $\mathcal{L}\left\{i \dot{C}^R(t) G^R(t)\right\}(s) $ has a known analytical form.
\footnote{
\begin{align}
\mathcal{L}\left\{\dot{C}^R(t)G^R(t)\right\}(s)
&=\int_0^\infty dt\, e^{-s t} \dot{C}^R(t) \left(-i e^{-i \epsilon_0 t} e^{C^R(t)}\right) \\
&= -i \int_0^\infty e^{-t(s + i\epsilon_0)} \frac{d}{dt}\big(e^{C^R(t)}\big)\, dt \label{eq:integration_by_parts}\\
&= i - i(s + i\epsilon_0)\int_0^\infty e^{-t(s + i\epsilon_0)} e^{C^R(t)}\,dt \label{id}\\
&= i - i(s + i\epsilon_0)\mathcal{L}\{G^R(t)\}(s)
\end{align}
where to proceed from \eqref{eq:integration_by_parts} we take $u' = \frac{d}{dt}\big(e^{C^R(t)}\big) \implies u = e^{C^R(t)}$ and $v = e^{-t(s + i\epsilon_0)} \implies v' = - (s + i\epsilon_0)e^{-t(s + i\epsilon_0)}$, so that
\begin{align}
\int_0^\infty e^{-t(s + i\epsilon_0)} \frac{d}{dt}e^{C^R(t)}\,dt
&= \left[e^{-t(s + i\epsilon_0)} e^{C^R(t)}\right]_0^\infty 
+ (s + i\epsilon_0)\int_0^\infty e^{-t(s + i\epsilon_0)} e^{C^R(t)}\,dt \\
&= -1 + (s + i\epsilon_0)\int_0^\infty e^{-t(s + i\epsilon_0)} e^{C^R(t)}\,dt
\end{align}
and then in \eqref{id} we recognize 
\begin{align}
\tilde{G}^R(s)&=\int_0^\infty dt\, e^{-s t} \left(-i e^{-i \epsilon_0 t} e^{C^R(t)}\right) \\
&=-i \int_0^\infty dt\, e^{-t\left(s+i \epsilon_0\right)} e^{C^R(t)}
\end{align}
}
. This Laplace transform might be promising because the RHS is a convolution ($(f*g)(t)=\int_0^t d \tau f(t-\tau) g(\tau)$, with $f(t)=G^R(t)$ and $g(t)=\Sigma^R(t)$) and we know that there is a nice formula for the Laplace transform of a convolution as $\mathcal{L}\{(f*g)(t)\}(s)=\mathcal{L}\{f(t)\}(s) \mathcal{L}\{g(t)\}(s)$. From here on out, we will interchange with the notation that $\mathcal{L}\{f(t)\}(s)=\tilde{f}(s)$. 
Then
\begin{align}
\mathcal{L}\left\{\text{RHS}\right\}(s) &=\tilde{G}^R(s) \tilde{\Sigma}^R(s).
\end{align}
We already know the form of $\tilde{G}^R(s)$, but we need to find $\tilde{\Sigma}^R(s)$. We can start by taking the Laplace transform of $\Sigma^R(t)$:
\begin{align}
\mathcal{L}\{\Sigma^R(t)\}(s)&=\int_0^\infty dt\, e^{-s t} \Sigma^R(t) \\
&=\int_0^\infty dt\, e^{-s t} \left[ \left(G_0^R(t)\right)^{-1} - \left(G^R(t)\right)^{-1} \right]
\end{align}
Given that it is not simple to invert the Green's function analytically in the time domain, we can stop here. \color{red}{But perhaps you can think of certain limits where this inversion is possible to do numerically?} \color{black}Setting $\mathcal{L}\left\{\text{LHS}\right\}(s)=\mathcal{L}\left\{\text{RHS}\right\}(s)$, we have
\begin{align}
i - i(s + i\epsilon_0)\tilde{G}^R(s) &= \tilde{G}^R(s) \tilde{\Sigma}^R(s) \\
\implies \tilde{\Sigma}^R(s)
&= \frac{i}{\tilde{G}^R(s)} - i(s + i\epsilon_0)
\quad\Longleftrightarrow\quad
\tilde{G}^R(s)
= \frac{i}{\tilde{\Sigma}^R(s) + i(s + i\epsilon_0)}. \label{eq:boxed}
\end{align}
So the relationship of $\tilde{G}^R(s)$ to the $C^R(t) $ becomes clear if we define
\begin{align}
&F(z) \equiv \mathcal{L}\{e^{C^R(t)}\}(z)
= \int_0^\infty e^{-z t}\,e^{C^R(t)}\,dt\\
\implies \tilde{G}^R(s) &= -i \int_0^\infty dt\, e^{-t(s + i\epsilon_0)} e^{C^R(t)} = -i F(s + i\epsilon_0)
\end{align}
So with
$z = s + i\epsilon_0$ in \eqref{eq:boxed}, we have
\begin{align}
&-i\,F(z)
= \frac{i}{\tilde{\Sigma}^R(z - i\epsilon_0) + i z}\\
&\implies 
F(z)
= \mathcal{L}\{e^{C^R(t)}\}(z)
= -\,\frac{1}{\tilde{\Sigma}^R(z - i\epsilon_0) + i z}\\
& \implies
C^R(t)
= \ln\!\left[
\mathcal{L}^{-1}_z
\left\{
-\frac{1}{\tilde{\Sigma}^R(z - i\epsilon_0) + i z}
\right\}(t)
\right],
\end{align}
where $\mathcal{L}^{-1}_z$ is the inverse Laplace transform with respect to $z$.

If we pass to the frequency domain by setting
$z = \eta - i\omega$ (with $\eta \to 0^+$),
the boxed relation becomes equivalent to the familiar Dyson form:
\begin{align}
G^R(\omega)
= \frac{1}{\omega - \epsilon_0 - \Sigma^R(\omega)}.
\end{align}
Thus, the Laplace-space identity is the causal/Laplace version of
Dysons equation combined with the cumulant ansatz.

Under the usual GW+cumulant approximations,
one expands around the quasiparticle pole and rewrites
$C^R(t)$ in terms of the satellite spectral weight:
\begin{align}
C^R(t)
= \int_{-\infty}^{\infty}
\frac{d\omega}{\pi}\,
\frac{\Im\,\Sigma^R(\epsilon_0 + \omega)}{\omega^2}
\big(e^{-i\omega t} + i\omega t - 1\big),
\end{align}
which can be recovered by (i) expressing the inverse Laplace kernel
via a spectral representation of $\Sigma^R$, and
(ii) performing the Bromwich integralthis uses analyticity and
retarded boundary conditions.
The result is the well-known closed form used for plasmon satellites
and shake-up structures.

\subsection*{Practical use}

The compact identity
\begin{align}
F(z)
= -\frac{1}{\tilde{\Sigma}^R(z - i\epsilon_0) + i z}
\end{align}
is a convenient starting point for controlled approximations:
\begin{itemize}
  \item \textbf{Low-$t$ expansion:} expand the denominator for large $z$
        to obtain short-time moments of $C^R(t)$.
  \item \textbf{Long-$t$ (satellite) behavior:} analyze the singularity
        structure of the denominator (branch cuts from $\Sigma^R$)
        to extract asymptotics and satellite weights.
\end{itemize}

Maybe the best thing now would be to start with the Landau form of the cumulant and to simplify the notation it is assumed that we deal with retarded quantities only.
\begin{equation}
    C(t)=\int d \omega \frac{\beta(\omega)}{\omega^2}\left[e^{-i \omega t}+i \omega t-1\right]
\end{equation}
where the cumulant kernel is defined as
\begin{align}
    \beta(\omega)&=-\frac{1}{\pi} \operatorname{Im} \Sigma(\omega) \\
    &=\frac{1}{\pi} \operatorname{Im} \left(G_0^{-1}(\omega) - G^{-1}(\omega) \right) \\
\end{align}
 If we partition into a physical and auxiliary space, denoted by $\mathcal{S}$ and $\mathcal{A}$, respectively, $\bm{G}_0(\omega)= \begin{pmatrix} \bm{G}^0_{\mathcal{S}\mathcal{S}}(\omega) & 0 \\ 0 & \bm{G}^0_{\mathcal{A}\mathcal{A}}(\omega) \end{pmatrix}$ and $\bm{G}(\omega)= \begin{pmatrix} \bm{G}_{\mathcal{S}\mathcal{S}}(\omega) & \bm{G}_{\mathcal{S}\mathcal{A}}(\omega) \\ \bm{G}_{\mathcal{A}\mathcal{S}}(\omega) & \bm{G}_{\mathcal{A}\mathcal{A}}(\omega) \end{pmatrix}$, and plug in to get an expression for the cumulant kernel in the partitioned space:
\begin{align}
    \beta_{S S}(\omega)&=\frac{1}{\pi} \operatorname{Im}\left[\mathbf{G}_{S S}^{0,-1}(\omega)-\left(\mathbf{G}_{S S}(\omega)-\mathbf{G}_{S \mathcal{A}}(\omega) \mathbf{G}_{\mathcal{A} \mathcal{A}}^{-1}(\omega) \mathbf{G}_{\mathcal{A} S}(\omega)\right)^{-1}\right]
\end{align}
I don't know if this form is useful.
%     \frac{G^R(t-\tau)}{G^R(t)}=e^{i \epsilon_0 \tau} e^{C^R(t-\tau)-C^R(t)} = e^{i \epsilon_0 \tau} e^{-\int_{t-\tau}^t d t' \dot{C}^R(t')} .
% \end{equation}
% So the final expression for the cumulant derivative is a nonlinear Volterra integro-differential equation (VIDE):
% \begin{align}
%     \dot{C}^R(t)&=\int_0^t d \tau \Sigma^R(\tau) e^{i \epsilon_0 \tau} e^{-\int_{t-\tau}^t d t' \dot{C}^R(t')} \\
%     &=i\int_0^t d \tau \int_0^{\infty} d \tau' \left[G^R(\tau - \tau') W^{>}(\tau')+G^{<}(\tau-\tau') W^R(\tau')\right] e^{i \epsilon_0 \tau} e^{-\int_0^\tau d t' \dot{C}^R(t')} 
% \end{align}
% A VIDE also appeared in PJ's SC-CE and they solved it using differential equation solvers in the time domain.
\subsubsection{One-shot cumulant}
In the first iteration, we set the exponential factor to 1, which gives the time-derivative of the one-shot cumulant:
\begin{equation}
    \dot{C}^{R}_0(t)=\int_0^t d \tau \Sigma^R(\tau) e^{i \epsilon_0 \tau} .
\end{equation}
Note that we can express the second-derivative of the one-shot retarded cumulant as
\begin{equation}
    \ddot{C}^{R}_0= \Sigma^R(t) e^{i \epsilon_0 t} .
\end{equation}
We integrate with respect to time to get the cumulant itself:
\begin{equation}
    C^{R}_0(t)=\int_0^t d t' \int_0^{t'} d \tau \Sigma^R(\tau) e^{i \epsilon_0 \tau} = \int_0^t d \tau \Sigma^R(\tau) e^{i \epsilon_0 \tau} (t-\tau) .
\end{equation}
Now, we perform a Fourier transform to get the frequency-domain cumulant:
\begin{align}
    C^{R}_0(\omega) &= \int_0^\infty dt\, e^{i\omega t} \int_0^t d\tau\, \Sigma^R(\tau) e^{i\epsilon_0 \tau} (t-\tau) \\
    &= \int_0^\infty d\tau\, \Sigma^R(\tau) e^{i\epsilon_0 \tau} \int_\tau^\infty dt\, e^{i\omega t} (t-\tau)
\end{align}
Let $t' = t - \tau$, so $dt = dt'$, and when $t = \tau$, $t' = 0$, and as $t \to \infty$, $t' \to \infty$:
\begin{align}
    \int_\tau^\infty dt\, e^{i\omega t} (t-\tau) &= \int_0^\infty dt'\, e^{i\omega (t'+\tau)} t' \\
    &= e^{i\omega \tau} \int_0^\infty dt'\, e^{i\omega t'} t'
\end{align}
We can evaluate the integral over $t'$ as
\begin{align}
    \int_0^\infty dt'\, e^{i\omega t'} t' & = -\frac{1}{(\omega + i\eta)^2}
\end{align}
where where $\eta$ is the positive infinitesimal convergence factor.

Putting it all together,
\begin{align}
    C^{R}_0(\omega) &= \int_0^\infty d\tau\, \Sigma^R(\tau) e^{i(\omega+\epsilon_0)\tau} \left(-\frac{1}{(\omega + i\eta)^2}\right) \\
    &= -\frac{1}{(\omega + i\eta)^2} \int_0^\infty d\tau\, \Sigma^R(\tau) e^{i(\omega+\epsilon_0)\tau} \\
    &= -\frac{\Sigma^R(\omega+\epsilon_0)}{(\omega + i\eta)^2} 
\end{align}
Now, consider the inverse Fourier transform to get back to the time domain:
\begin{align}
    C^{R}_0(t) &= \int_{-\infty}^{\infty} d\omega\, e^{-i\omega t} C^{R}_0(\omega) \\
    &= \int_{-\infty}^{\infty} d\omega\, e^{-i\omega t} \left(-\frac{\Sigma^R(\omega+\epsilon_0)}{(\omega + i\eta)^2}\right)
\end{align}
\subsection{Fundamental properties of the cumulant}

The interacting Green's function can be written as either a Dyson series
\begin{equation}
    G = G_0 + G_0 \Sigma G_0 + G_0 \Sigma G_0 \Sigma G_0 + G_0 \Sigma G_0 \Sigma G_0 \Sigma G_0 + \ldots
\end{equation}
or using the cumulant ansatz $G = G_0 e^{C}$, where we can formally expand the cumulant $C$ in powers of the interaction strength as $C = \lambda C +\lambda ^2 C + \lambda ^3 C + \mathcal{O}(\lambda^4) \equiv C^{(1)} + C^{(2)} + C^{(3)} + \mathcal{O}(\lambda^4)$. Expanding the exponential gives
\begin{align}
      G&= G_0 \left( 1 + C + \frac{C^2}{2!} + \frac{C^3}{3!} + \ldots \right)\\
&= G_0 \left( 1+C^{(1)}+\frac{1}{2!}\left[\left(C^{(1)}\right)^2+2 C^{(2)}\right]+\frac{1}{3!}\left[\left(C^{(1)}\right)^3+3 C^{(1)} C^{(2)}+3 C^{(2)} C^{(1)}+6 C^{(3)}\right] + \mathcal{O}(\lambda^4) \right) 
\end{align}
To form a relationship between the two, we can connect them order by order in powers of $\lambda$, where the standard PT convention tells us that a $\Sigma $ carries with it a $\lambda$, to get
\paragraph{Zeroth order:}
\begin{align}
    G_{\text{Dyson}}^{(0)} &= G_{\text{Cumulant}}^{(0)} \\
\implies M^{(0)} \equiv G_0 &= G_0 \\
\implies C^{(0)} &= 0
\end{align}

\paragraph{First order:}
\begin{align}
G^{(1)}_{\text{Dyson}} &= G^{(1)}_{\text{Cumulant}} \\
    \implies G_0 \Sigma G_0 &= G_0 C^{(1)} \\
\implies C^{(1)} &= \Sigma G_0 \equiv M^{(1)}
\end{align}
Beyond the first order, we will have to consider products of lower-order terms as well.
\paragraph{Second order:}
\begin{align}
    G^{(2)}_{\text{Dyson}} &= G^{(2)}_{\text{Cumulant}} \\
    \implies G_0 \Sigma G_0 \Sigma G_0 &= G_0 \left( C^{(2)} + \frac{1}{2!}(C^{(1)})^2 \right) \\
&= G_0 \left( C^{(2)} + \frac{1}{2!}M^{(1)} \right) \\
\implies C^{(2)} &= \underbrace{\Sigma G_0 \Sigma G_0}_{M^{(2)}} - \frac{1}{2}(M^{(1)})^2
\end{align}
\paragraph{Third order:}
\begin{align}
    G^{(3)}_{\text{Dyson}} &= G^{(3)}_{\text{Cumulant}} \\
    \implies G_0 \Sigma G_0 \Sigma G_0 \Sigma G_0 &= G_0 \left( C^{(3)} + \frac{1}{2}C^{(1)} C^{(2)} + \frac{1}{2}C^{(2)} C^{(1)} + \frac{1}{6}(C^{(1)})^3 \right) \\
&= G_0 \left( C^{(3)} + \frac{1}{2}M^{(1)} \left( M^{(2)} - \frac{1}{2}(M^{(1)})^2 \right) + \frac{1}{2}\left( M^{(2)} - \frac{1}{2}(M^{(1)})^2 \right) M^{(1)} + \frac{1}{6}(M^{(1)})^3 \right) \\
\implies C^{(3)} &= \underbrace{\Sigma G_0 \Sigma G_0 \Sigma G_0}_{M^{(3)}} - \frac{1}{2}\left( M^{(1)} M^{(2)} + M^{(2)} M^{(1)} \right) + \frac{1}{3}(M^{(1)})^3
\end{align}
This mirrors the third cumulant in statistics:
\[
\kappa_3 = \mu_3' - 3\mu_2'\mu_1' + 2(\mu_1')^3.
\]
\subsection{GW+C}
\subsubsection{Using exact self-energy}
If you give me the exact self-energy, like $\Sigma = G_0^{-1} - G^{-1}$, this means all my terms in the Dyson expansion are exact; i.e. $G = G_0 + G_0 \Sigma G_0 + G_0 \Sigma G_0 \Sigma G_0 + \ldots$ will give the exact $G$. In other words, I have the exact moments $\mu_{n,k}$ of the interacting Green's function, which in the retarded framework can be written as
\begin{align}
G_k^R(t)&=-i \theta(t)\left\langle\left\{c_k(t), c_k^{\dagger}(0)\right\}\right\rangle \\
&=-i \theta(t)\left\langle\left\{e^{i H t} c_k e^{-i H t}, c_k^{\dagger}\right\}\right\rangle \\
&=-i \theta(t)\left\langle\left\{\sum_{n=0}^{\infty} \frac{(-i t)^n}{n!} \mathcal{L}^n c_k, c_k^{\dagger}\right\}\right\rangle \\
% &=-i \theta(t)\left( \left\langle\left\{c_k, c_k^{\dagger}\right\}\right\rangle+i t\left\langle\left\{\left[H, c_k\right], c_k^{\dagger}\right\}\right\rangle+\frac{(i t)^2}{2}\left\langle\left\{\left[H,\left[H, c_k\right]\right], c_k^{\dagger}\right\}\right\rangle+\cdots \right)\\
&=-i \theta(t)\left( \mu_{0,k}- t\mu_{1,k}+\frac{t^2}{2}\mu_{2,k}+O(t^3) \right)
\end{align}
where we have defined the moments $\mu_{n,k}=\left\langle\left\{\left(i \mathcal{L} \right)^n c_k, c_k^{\dagger}\right\}\right\rangle$ and the Liouvillian superoperator $\mathcal{L} O=[H,O]$. Then, it becomes the mathematical exercise of determining the cumulant $C_k(t)$ in terms of the moments, such that the Taylor expansion of the exponential in $G_k^R(t) = G_{0,k}^R(t) e^{C_k(t)}$ matches the Dyson expansion of the exact $G_k^R(t)$ up to order $n$. Given that the exact cumulant can be expanded as $C_k^R(t) = \kappa_{1,k} t + \kappa_{2,k} t^2 + O(t^3)$, we can Taylor expand the exponential $e^{C_k^R(t)}$ and then match coefficients with the above expression for $R_k(t)$ to plug into the usual relations between the cumulants $\kappa _{n,k}$ and moments $\alpha_{n,k}$, to get
\begin{align}
    \kappa_{1,k} = \alpha_{1,k} &= -\left(\mu_{1,k}-\mu_{1,k}^0\right)\\
    \kappa_{2,k} = \alpha_{2,k} - \frac{\alpha_{1,k}^2}{2} &= \frac{1}{2}\left(\mu_{2,k}-\mu_{2,k}^0\right)-\mu_{1,k}\mu_{1,k}^0+\left(\mu_{1,k}^0\right)^2 -\frac{1}{2}{\left[-\left(\mu_{1,k}-\mu_{1,k}^0\right)\right]^2}\\
&= \frac{1}{2}\left(\mu_{2,k}-\mu_{2,k}^0\right)-\mu_{1,k}\mu_{1,k}^0+\left(\mu_{1,k}^0\right)^2 -\frac{1}{2}\left(\mu_{1,k}-\mu_{1,k}^0\right)^2\\
&= \frac{1}{2}\left[\left( \mu_{2,k} - \mu_{2,k}^0 \right) +\left( \mu_{1,k} \right)^2 + \left( \mu_{1,k}^0 \right)^2 \right]
\end{align}
We know that $\Sigma = G_0^{-1} - G^{-1}$, and inserting this gives\\ $G_0(\omega) \Sigma(\omega) G_0(\omega) = G_0(\omega) \left(G_0^{-1}(\omega) - G^{-1}(\omega)\right) G_0(\omega) = G_0(\omega) - G_0(\omega) G^{-1}(\omega) G_0(\omega)$
\begin{align}
	C_{pq}(t) &= i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t} \left[G_0(\omega) \Sigma(\omega) G_0(\omega)\right]_{pq} \\
&= i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t} \left[G_0(\omega) - G_0(\omega) G^{-
1}(\omega) G_0(\omega)\right]_{pq} \\
&= i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t} \left[\frac{1}{\omega - \epsilon_p^{HF} + i\eta} - \left[G_0(\omega) G^{-1}(\omega) G_0(\omega)\right]_{pq}\right] \\
&= \theta(t) - i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t}  \left[G_0(\omega) G^{-1}(\omega) G_0(\omega)\right]_{pq}
\label{restart} \\
&= i \int \frac{d\omega}{2\pi}  \left[\frac{e^{-i(\omega-\epsilon_p^{HF})t}}{\omega - \epsilon_p^{HF} + i\eta} - \frac{e^{-i(\omega-\epsilon_p^{HF})t}G^{-1}_{pq}(\omega)}{(\omega - \epsilon_p^{HF} + i\eta)(\omega - \epsilon_q^{HF} + i\eta)}\right] \\
&= \theta  (t) - i \int \frac{d\omega}{2\pi}  \frac{e^{-i(\omega-\epsilon_p^{HF})t}G^{-1}_{pq}(\omega)}{(\omega - \epsilon_p^{HF} + i\eta)(\omega - \epsilon_q^{HF} + i\eta)} 
\end{align}
Now we plug this into the ansatz for the retarded Green's function:
\begin{align}
    G_{pq}(t) &= G_{pp}^{HF}(t) e^{C_{pq}(t)} \\
&= -i \theta(t) e^{- i \epsilon_p^{HF} t} \exp \left[\theta(t) - i \int \frac{d\omega}{2\pi}  \frac{e^{-i(\omega-\epsilon_p^{HF})t}G^{-1}_{pq}(\omega)}{(\omega - \epsilon_p^{HF} + i\eta)(\omega - \epsilon_q^{HF} + i\eta)}\right] \\
&\approx -i \theta(t) e^{- i \epsilon_p^{HF} t} \left[1 - i \int \frac{d\omega}{2\pi}  \frac{e^{-i(\omega-\epsilon_p^{HF})t}G^{-1}_{pq}(\omega)}{(\omega - \epsilon_p^{HF} + i\eta)(\omega - \epsilon_q^{HF} + i\eta)}\right] 
\end{align}
This doesn't seem useful, so we can start again with eqn.~\ref{restart}.
We can use a projection technique and split into a HF space where the projector is defined as $\hat{P}=\sum_p^{\text{HF}}\ket{p}\bra{p}$, which we can identify with $\begin{pmatrix}1 \\ 0\end{pmatrix}$ and the rest space with projector $\hat{Q}=1-\hat{P}$, which we can identify with $\begin{pmatrix}0 \\ 1\end{pmatrix}$. Then, using the fact that $G^{-1} = G_0^{-1} - \Sigma$ and assuming the HF reference, we can write:
\begin{align}
    G^{-1}_{pq}(\omega) 
&= \left[\hat{P} G^{-1}(\omega) \hat{P} + \hat{P} G^{-1}(\omega) \hat{Q} + \hat{Q} G^{-1}(\omega) \hat{P} + \hat{Q} G^{-1}(\omega) \hat{Q}\right]_{pq} \\
 &= \left(\left[\omega - \epsilon_p^{HF} \right] \delta _{pq}- \Sigma_{pq}(\omega)\right) \hat{P}\otimes \hat{P} - \left(\Sigma^c_{pQ}\right) \hat{P}\otimes \hat{Q} - \left(\Sigma^c_{Pq}\right) \hat{Q}\otimes \hat{P}\\
& + \left( (\omega - \epsilon_P^{HF}) \delta _{PQ} - \Sigma_{PQ}(\omega)\right) \hat{Q}\otimes \hat{Q} \\
&= \begin{pmatrix} \left[\omega - \epsilon_p^{HF} \right] \delta _{pq}- \Sigma_{pq}(\omega) & -\Sigma^c_{pQ} \\ -\Sigma^c_{Pq} & (\omega - \epsilon_P^{HF}) \delta _{PQ} - \Sigma_{PQ}(\omega) \end{pmatrix} \\
\implies G _{pq}(\omega)&=  
% \\
% &= \left(\left[\omega - \epsilon_p^{HF} \right] \delta _{pq}- \Sigma_{pq}(\omega)\right)\begin{pmatrix} 1 & 0 \\ 0 & 0 \end{pmatrix} - \left(\Sigma^c_{pQ}\right) \begin{pmatrix} 0 & 0 \\ 0 & 1 \end{pmatrix} - \left(\Sigma^c_{Pq}\right) \begin{pmatrix} 1 & 0 \\ 0 & 0 \end{pmatrix} + \left( (\omega - \epsilon_P^{HF}) \delta _{PQ} - \Sigma_{PQ}(\omega)\right) \begin{pmatrix} 0 & 0 \\ 0 & 1 \end{pmatrix}
\end{align}
where lowercase letters indicate indices in the physical space, while uppercase letters indicate indices in the rest space.
\subsubsection{Off-diagonal cumulant with GW self-energy}
We can start with
\begin{align}
		C_{pq}(t) &= i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t} G_{pp}^{HF}(\omega) \Sigma_{pq}^c(\omega) G_{qq}^{HF}(\omega) \\
&= i \int \frac{d\omega}{2\pi} e^{-i(\omega-\epsilon_p^{HF})t} \frac{\Sigma_{pq}^c(\omega)}{(\omega - \epsilon_p^{HF} + i\eta)(\omega - \epsilon_q^{HF} + i\eta)} 
\label{eq:Cpp_m1}\\
\end{align}
At this point we make the frequency shift $\omega \to \omega + \epsilon_p^{HF}$, and then we can write
\begin{align}
    C_{pq}(t) &= i \int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{\Sigma_{pq}^c(\omega + \epsilon_p^{HF})}{(\omega + i\eta)(\omega + \underbrace{\epsilon_p^{HF} - \epsilon_q^{HF}}_{\Delta_{pq}} + i\eta)}
\end{align}
Now using the partial fractions we can write $\frac{1}{(\omega + i\eta)(\omega + \Delta_{pq} + i\eta)} = \frac{1}{\Delta_{pq}}\left(\frac{1}{\omega + i\eta} - \frac{1}{\omega + \Delta_{pq} + i\eta}\right)$ and we can plug in the full form for the retarded GW self-energy as 
\begin{equation}
    \Sigma_{pq}^{c, \mathrm{G}_0 \mathrm{~W}_0}(\omega)= \sum_{i \nu}\left[W_{p i \nu} \frac{1}{\omega-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta} W_{q i \nu}\right]+ \sum_{a \nu}\left[W_{p a \nu} \frac{1}{\omega-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta} W_{q a \nu}\right]
\end{equation}
to get
\begin{align}
    C_{pq}(t) &= \frac{i}{\Delta_{pq}} \int \frac{d\omega}{2\pi} e^{-i\omega t} \left[ \sum_{i \nu} \frac{W_{p i \nu} W_{q i \nu}}{\omega+\epsilon_p-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta} + \sum_{a \nu}  \frac{W_{p a \nu} W_{q a \nu}}{\omega+\epsilon_p-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta} \right] \\
&\left(\frac{1}{\omega + i\eta} - \frac{1}{\omega + \left( \epsilon_p - \epsilon_q\right) + i \eta}\right) \notag \\ 
& = i \sum_{i \nu} \frac{W_{p i \nu} W_{q i \nu}}{\Delta_{pq}} \int \frac{d\omega}{2\pi} e^{-i\omega t} \times \\
&\left(\frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + i\eta\right)} - \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + \left( \epsilon_p - \epsilon_q\right) + i\eta\right)}\right) \notag \\
& + i \sum_{a \nu} \frac{W_{p a \nu} W_{q a \nu}}{\Delta_{pq}} \int \frac{d\omega}{2\pi} e^{-i\omega t} \times \notag \\
&\left(\frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + i\eta\right)} - \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + \left( \epsilon_p - \epsilon_q\right) + i\eta\right)}\right) \notag
\end{align}
To evaluate these contour integrals, recall that $\oint d\omega f(\omega) = \int_{-\infty}^{\infty} d\omega f(\omega) + \int_{\text{arc}} d\omega f(\omega)$, so in order to equate the real frequency integral to the contour integral, which will then allow us to use the residue theorem, we need to ensure that the integral over the arc vanishes. This only will happen (due to Jordan's Lemma) if the numerator $e^{-i\omega t}$ vanishes for $\omega \rightarrow \infty$ and $\omega \rightarrow -\infty$; because we have $t>0$, this is only true if $\operatorname{Im}(\omega) < 0$, and so we must close the contour in the lower half plane. 
\begin{align}
    &\int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + i\eta\right)} = i\left(\frac{e^{-i(\epsilon_i - \Omega_\nu-\epsilon_p)t} - 1}{\epsilon_i - \Omega_\nu-\epsilon_p}\right) \\
    &\int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_i-\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + \Delta_{pq} + i\eta\right)} = i\left(\frac{e^{i(\Delta_{pq})t} - e^{-i(\epsilon_i - \Omega_\nu-\epsilon_p)t}}{-\epsilon_i + \Omega_\nu+\epsilon_p - \Delta_{pq}}\right) \\
&= i\left(\frac{e^{i(\epsilon_p - \epsilon_q)t} - e^{-i(\epsilon_i - \Omega_\nu-\epsilon_p)t}}{-\epsilon_i + \Omega_\nu+\epsilon_q}\right) \notag \\
    &\int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + i\eta\right)} = i\left(\frac{e^{-i(\epsilon_a + \Omega_\nu-\epsilon_p)t} - 1}{\epsilon_a + \Omega_\nu-\epsilon_p}\right) \\
    &\int \frac{d\omega}{2\pi} e^{-i\omega t} \frac{1}{\left(\omega+\epsilon_p-\left(\epsilon_a+\Omega_\nu\right)+\mathrm{i} \eta\right)\left(\omega + \Delta_{pq} + i\eta\right)} = i\left(\frac{e^{i(\Delta_{pq})t} - e^{-i(\epsilon_a + \Omega_\nu-\epsilon_p)t}}{-\epsilon_a - \Omega_\nu+\epsilon_p - \Delta_{pq}}\right) \\
&= i\left(\frac{e^{i(\epsilon_p - \epsilon_q)t} - e^{-i(\epsilon_a + \Omega_\nu-\epsilon_p)t}}{-\epsilon_a - \Omega_\nu+\epsilon_q}\right) \notag
\end{align}
To ease the notation, we can introduce $\Xi_{i\nu} \equiv \epsilon_i - \Omega_\nu$, $\Xi_{a\nu} \equiv \epsilon_a + \Omega_\nu$. Then we can write
\begin{tcolorbox}
As a sanity check at this point, we can consider $\lim_{q \to p} T_{i\nu }(\Delta )$ and see if we recover the diagonal result. We can start by defining $f(\Delta ) = \frac{e^{-i\left(\Xi_{i\nu} - \epsilon_p\right) t}-1 }{\Xi_{i\nu}-\epsilon_p} + \frac{e^{i\Delta t} - e^{-i\left(\Xi_{i\nu} - \epsilon_p\right) t}}{\Xi_{i\nu} - \epsilon_q}$ and $g(\Delta  ) = \Delta$, then $\lim_{q \to p} T_{i\nu}(\Delta ) = \lim_{q \to p}\frac{f(\Delta )}{g(\Delta )} = \frac{0}{0}$. So we can use L'Hpital's rule to get $\lim_{q \to p} T_{i\nu}(\Delta ) = \lim_{q \to p}\frac{f'(\Delta)}{g'(\Delta)} = \lim_{\Delta \to 0} \frac{f'(\Delta)}{1} = \lim_{\Delta \to 0} \frac{\left(i t e^{i \Delta t}\right)\left(\Xi_{i\nu} - \epsilon_p+\Delta\right)-\left(e^{i \Delta t}-e^{-i (\Xi_{i\nu} - \epsilon_p) t}\right)}{\left(\Xi_{i\nu} - \epsilon_p+\Delta\right)^2} = \frac{i \left(\Xi_{i\nu} - \epsilon_p\right) t -1 +e^{-i (\Xi_{i\nu} - \epsilon_p) t }}{\left(\Xi_{i\nu} - \epsilon_p\right)^2} $, which is indeed the diagonal result.
\end{tcolorbox}
% Then
% $$
% N^{\prime}(\Delta)=\frac{\left(i t e^{i \Delta t}\right)(A+\Delta)-\left(e^{i \Delta t}-e^{-i A t}\right)}{(A+\Delta)^2} .
% $$

% Evaluate at $\boldsymbol{\Delta}=\mathbf{0}$ :
% $$
% N^{\prime}(0)=\frac{i t A-\left(1-e^{-i A t}\right)}{A^2} .
% $$
\begin{align}
C_{pq}(t) &=  i^2\left[ \sum_{i\nu} W_{p i \nu} W_{q i \nu} \left(\underbrace{\frac{1}{\Delta}\left[\frac{e^{-i\left(\Xi_{i\nu} - \epsilon_p\right) t}-1 }{\Xi_{i\nu}-\epsilon_p} + \frac{e^{i\Delta t} - e^{-i\left(\Xi_{i\nu} - \epsilon_p\right) t}}{\Xi_{i\nu} - \epsilon_q}\right] }_{T_{i\nu}(t)}\right)\right.\\
& \left. + \sum_{a\nu} W_{p a \nu} W_{q a \nu} 
\left(\underbrace{\frac{1}{\Delta}\left[{\frac{e^{-i\left(\Xi_{a\nu} - \epsilon_p\right) t}-1 }{\Xi_{a\nu}-\epsilon_p} + \frac{e^{i\Delta t} - e^{-i\left(\Xi_{a\nu} - \epsilon_p\right) t}}{\Xi_{a\nu} - \epsilon_q}}\right]}_{T_{a\nu}(t)}\right) \right] \notag \\
\end{align}
Now we just work with
\begin{align}
    T_{i\nu}(t) &= \frac{ \left( \Xi_{i\nu} - \epsilon_q \right) \left[ e^{-i(\Xi_{i\nu} - \epsilon_p)t} - 1  \right] + \left( \Xi_{i\nu} - \epsilon_p \right) \left[ e^{i\left(\epsilon_p - \epsilon_q\right)t} - e^{-i(\Xi_{i\nu} - \epsilon_p)t} \right] }{ (\epsilon_p - \epsilon_q)(\Xi_{i\nu} - \epsilon_p)(\Xi_{i\nu} - \epsilon_q) } \\
&= \frac{- \left( \Xi_{i\nu} - \epsilon_q \right) + \left( \Xi_{i\nu} - \epsilon_p \right) e^{i\left(\epsilon_p - \epsilon_q\right)t} + \left( \epsilon_p - \epsilon_q - 2\Xi_{i\nu} \right) e^{-i(\Xi_{i\nu} - \epsilon_p)t} }{ (\epsilon_p - \epsilon_q)(\Xi_{i\nu} - \epsilon_p)(\Xi_{i\nu} - \epsilon_q) } \\
&= -\frac{1}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)}+\frac{e^{i\left(\epsilon_p-\epsilon_q\right) t}}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_q\right)}+\frac{e^{-i\left(\Xi_{i\nu}-\epsilon_p\right) t}}{\left(\Xi_{i\nu}-\epsilon_p\right)\left(\Xi_{i\nu}-\epsilon_q\right)}-\frac{2 \Xi_{i\nu} e^{-i\left(\Xi_{i\nu}-\epsilon_p\right) t}}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)(\Xi_{i\nu}-\epsilon_q)} .
\end{align}
and we can do the analogous computation to get $T_{a\nu}(t)$.
Now we can plug into the expression for the retarded Green's function to get
\begin{align}
    G_{pq}(t) & = G_{pq}^{HF}(t) e^{C_{pq}(t)} \\
& = -i \Theta(t) e^{-i \epsilon_p t + C_{pq}(t)} \\
& = -i \Theta(t) \exp\left[-i \epsilon_p t - \sum_{i\nu} W_{p i \nu} W_{q i \nu} T_{i\nu}(t) - \sum_{a\nu} W_{p a \nu} W_{q a \nu} T_{a\nu}(t) \right] \\
\end{align}
The Fourier transform to the frequency domain is given by
\begin{align}
    G_{pq}(\omega) &= \int dt e^{i\omega t} G_{pq}(t) \\
&= -i \int_0^\infty dt e^{i(\omega - \epsilon_p) t} \exp{-\sum_{i\nu} W_{p i \nu} W_{q i \nu} T_{i\nu}(t) - \sum_{a\nu} W_{p a \nu} W_{q a \nu} T_{a\nu}(t)} \\
&\approx -i \int_0^\infty dt e^{i(\omega - \epsilon_p) t} \left[1- \sum_{i\nu} W_{p i \nu} W_{q i \nu} T_{i\nu}(t) - \sum_{a\nu} W_{p a \nu} W_{q a \nu} T_{a\nu}(t) \right] \\
\end{align}
where in the last step we have made a Taylor expansion of the exponential, keeping just the 0th and 1st order terms. This is the right thing to do because in one of our first steps we chose to make the expression exact up to the first order in the screened Coulomb interaction $W$. If we were to expand beyond the first order, we would be including terms beyond first order in $W$.
So the form for the off-diagonal GW+C spectral function would be
\begin{align}
    A_{pq}(\omega) &= -\frac{1}{\pi} \text{Im} G_{pq}(\omega) \\
\end{align}
so we would need to determine
\begin{align}
   \operatorname{Im}G_{pq}(\omega) &\approx - \operatorname{Re}\int_0^\infty dt \left[e^{i(\omega - \epsilon_p) t} \left(1 - \sum_{i\nu} W_{p i \nu} W_{q i \nu} T_{i\nu}(t) - \sum_{a\nu} W_{p a \nu} W_{q a \nu} T_{a\nu}(t) \right) \right] \\
&= - \pi \delta(\omega - \epsilon_p) + \sum_{i\nu} W_{p i \nu} W_{q i \nu} \operatorname{Re}\int_0^\infty dt e^{i(\omega - \epsilon_p) t} T_{i\nu}(t) + \sum_{a\nu} W_{p a \nu} W_{q a \nu} \operatorname{Re}\int_0^\infty dt e^{i(\omega - \epsilon_p) t} T_{a\nu}(t)
\end{align}
which leaves us with the task of computing
\begin{align}
    \operatorname{Re}\int_0^\infty dt e^{i(\omega - \epsilon_p) t} T_{i\nu}(t) &= -\frac{\pi\delta(\omega - \epsilon_p)}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)} + \frac{\pi\delta(\omega - \epsilon_q)}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_q\right)}\\
&  + \frac{\pi\delta(\omega - \Xi_{i\nu})}{\left(\Xi_{i\nu}-\epsilon_p\right)\left(\Xi_{i\nu}-\epsilon_q\right)}-\frac{\pi2\Xi_{i\nu}\delta(\omega - \Xi_{i\nu})}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)\left(\Xi_{i\nu}-\epsilon_q\right)} \notag \\
\end{align}
and similarly for $T_{a\nu}(t)$. So
\begin{align}
    A_{pq}(\omega) &\approx \delta(\omega - \epsilon_p) - \sum_{i\nu} W_{p i \nu} W_{q i \nu} \left[-\frac{\delta(\omega - \epsilon_p)}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)} + \frac{\delta(\omega - \epsilon_q)}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_q\right)} + \frac{\delta(\omega - \Xi_{i\nu})}{\left(\Xi_{i\nu}-\epsilon_p\right)\left(\Xi_{i\nu}-\epsilon_q\right)} \right. \\
&\left. - \frac{2\Xi_{i\nu}\delta(\omega - \Xi_{i\nu})}{\left(\epsilon_p-\epsilon_q\right)\left(\Xi_{i\nu}-\epsilon_p\right)\left(\Xi_{i\nu}-\epsilon_q\right)}\right] - \sum_{a\nu} W_{p a \nu} W_{q a \nu} \left[-\frac{\delta(\omega - \epsilon_p)}{\left(\epsilon_p-\epsilon_q\right)\left({\Xi}_{a\nu}-\epsilon_p\right)} + \frac{\delta(\omega - \epsilon_q)}{\left(\epsilon_p-\epsilon_q\right)\left({\Xi}_{a\nu}-\epsilon_q\right)} \right. \\
& \left.+ \frac{\delta(\omega - {\Xi}_{a\nu})}{\left({\Xi}_{a\nu}-\epsilon_p\right)\left({\Xi}_{a\nu}-\epsilon_q\right)}  - \frac{2{\Xi}_{a\nu}\delta(\omega - {\Xi}_{a\nu})}{\left(\epsilon_p-\epsilon_q\right)\left({\Xi}_{a\nu}-\epsilon_p\right)\left({\Xi}_{a\nu}-\epsilon_q\right)}\right] \notag
\end{align}
We can replace all of the delta functions with Lorentzians in practice.
\subsection{Assorted}
\subsubsection{MKCT}
\begin{equation}
\Omega_n=\frac{\left((\mathrm{i} \mathcal{L})^n \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})},
\end{equation}
with the corresponding auxiliary kernels
\begin{equation}
K_n(t)=\frac{\left((\mathrm{i} \mathcal{L})^n \hat{f}(t), \hat{A}\right)}{(\hat{A}, \hat{A})}
\end{equation}
So we can show the main result of their first paper that the higher-order kernels satisfy the following coupled ordinary differential equation (ODE):
\begin{align}
\dot{K}_n(t) & =\frac{\left((\mathrm{i} \mathcal{L})^n \dot{\tilde{f}}(t), \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =\frac{\left((\mathrm{i} \mathcal{L})^n \mathrm{i} \mathcal{Q} \mathcal{L} \hat{f}(t), \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =\frac{\left((\mathrm{i} \mathcal{L})^{n+1} \hat{f}(t), \hat{A}\right)}{(\hat{A}, \hat{A})}-\frac{\left((\mathrm{i} \mathcal{L})^n \mathrm{i} \mathcal{P} \mathcal{L} \hat{f}(t), \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =K_{n+1}(t)-\frac{(\mathrm{i} \mathcal{L} \hat{f}(t), \hat{A})}{(\hat{A}, \hat{A})} \times \frac{\left((\mathrm{i} \mathcal{L})^n \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =K_{n+1}(t)-K_1(t) \Omega_n,
\end{align}
where we have used the fact that the random fluctuation operator is $\hat{f}(t)=e^{\mathrm{i} t}{ }^{\mathrm{Q}}{ }^{\mathrm{C}} \mathcal{Q} \mathrm{i} \mathcal{L} \hat{A} \Longrightarrow \dot{f}(t)=\mathrm{i} \mathcal{Q} \mathcal{L} \hat{f}(t)$ and we can deduce the initial conditions in a similar fashion with $\hat{f}(0)=\mathcal{Q} i \mathcal{L} \hat{A}$, so
\begin{align}
K_n(0) & =\frac{\left((\mathrm{i} \mathcal{L})^n \mathrm{Qi} \mathcal{L} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =\frac{\left((\mathrm{i} \mathcal{L})^n(\mathrm{i} \mathcal{L} \hat{A}-\mathrm{P} \mathrm{i} \mathcal{L} \hat{A}), \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =\frac{\left((\mathrm{i} \mathcal{L})^{n+1} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})}-\frac{\left((\mathrm{i} \mathcal{L})^n \mathrm{P} \mathrm{i} \mathcal{L} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
& =\Omega_{n+1}-\Omega_1 \Omega_n,
\end{align}
suggesting that the central quantity to compute is the $\left\{\Omega_n\right\}$. But an issue with this ODE is that it extends to infinite order, and hard truncation to finite order can lead to numerical instabilities. To this end, they introduce a truncation scheme with Pad approximants. First, they noticed that the $m$-th derivative of kernel $K_n(t)$ evaluated at $t=0$ is
\begin{align}
K_n^{(m)} &= \frac{\left((\mathrm{i} \mathcal{L})^n(\mathcal{Q} \mathrm{i} \mathcal{L})^{m+1} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
&= \frac{\left((\mathrm{i} \mathcal{L})^n \mathcal{Q} \mathrm{i} \mathcal{L} (\mathcal{Q} \mathrm{i} \mathcal{L})^{m}\hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
&= \frac{\left((\mathrm{i} \mathcal{L})^n \left(1-\mathcal{P}\right) \mathrm{i} \mathcal{L} (\mathcal{Q} \mathrm{i} \mathcal{L})^{m} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
&= \frac{\left((\mathrm{i} \mathcal{L})^{n+1} (\mathcal{Q} \mathrm{i} \mathcal{L})^{m} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} - \frac{\left((\mathrm{i} \mathcal{L})^n \mathcal{P} \mathrm{i} \mathcal{L} (\mathcal{Q} \mathrm{i} \mathcal{L})^{m} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
&= K_{n+1}^{(m-1)} - \frac{\left(\mathrm{i} \mathcal{L}(\mathcal{Q} \mathrm{i} \mathcal{L})^m \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \times \frac{\left((\mathrm{i} \mathcal{L})^n \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} \\
&= K_{n+1}^{(m-1)} - \bar{\Omega}_m \Omega_n 
\end{align}
where we introduced the auxiliary moment $\bar{\Omega}_m=\frac{\left(\mathrm{i} \mathcal{L}(\mathcal{Q} \mathrm{i} \mathcal{L})^m \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})}$.
So recursively applying this expression leads to the relation: 
\begin{align}
K_n^{(m)} &= K_{n+2}^{(m-2)} - \bar{\Omega}_{m-1} \Omega_{n+1} - \bar{\Omega}_m \Omega_{n} \\
&= K_{n+m}^{(0)} - \sum_{j=0}^{m-1} \bar{\Omega}_{m-j} \Omega_{n+j} \\
&= \Omega_{n+m+1} - \Omega_{1} \Omega_{n+m} - \sum_{j=0}^{m-1} \bar{\Omega}_{m-j} \Omega_{n+j} \\
&= \Omega_{n+m+1} - \bar{\Omega}_{0} \Omega_{n+m} - \sum_{j=0}^{m-1} \bar{\Omega}_{m-j} \Omega_{n+j} \\
&= \Omega_{n+m+1} - \sum_{j=0}^{m} \bar{\Omega}_{m-j} \Omega_{n+j} \\
\end{align}
that $K_{n}^{(m)}$ can be expressed with moments and auxiliary moments. Similarly, the auxiliary moments themselves have recursions
\begin{equation}    
\begin{aligned}
    \tilde{\Omega}_m &= \frac{\left((\mathrm{i} \mathcal{L} \mathcal{Q})^{m} \mathrm{i} \mathcal{L} \hat{A}, \hat{A}\right)}{(\hat{A}, \hat{A})} - \tilde{\Omega}_{m-1} \Omega_1\\
% (\im\Lv (\Qroj \im \Lv)^{m-1} \im \Lv \hat{A}, \hat{A}) (\hat{A}, \hat{A})^{-1} - \tilde{\Omega}_{m-1} \Omega_1, \\
    &= \Omega_{m+1} - \sum_{j=0}^{m-1} \tilde{\Omega}_j \Omega_{m-j} \\ 
\end{aligned}
\end{equation}
which means the auxiliary moments $\{\tilde{\Omega}_m\}$ can be obtained by the moments $\{\Omega_n\}$; it becomes a problem of efficiently computing the moments. The series expansion for the $n$-th order auxiliary kernel can then be given by Pad\'{e} approximant. Initially, $K_n(t)$ is expressed as a truncated Taylor series:
\begin{equation}
    K_n(t) \approx \sum_{j=0}^{M} \frac{K_n^{(j)}(0)}{j!} t^j,
\end{equation}
which is a good local approximation but lacks accuracy over a broader range of $t$. A more reliable approximation can be achieved using the Pad\'{e} approximant: 
\begin{equation}\label{eqn:pade}
    K_n(t) \approx \frac{p_{M_1}(t)}{q_{M_2}(t)} = \frac{a_0 + a_1 t + \dots + a_{M_1} t^{M_1}}{1 + b_1 t + \dots + b_{M_2} t^{M_2}},
\end{equation}
where $ p_{M_1}(t)$ and $q_{M_2}(t)$ are polynomials of degrees $M_1$ and $M_2$, respectively. The coefficients $\{a_i\}$ and $\{b_i\}$ are computed using the python library SciPy, which implements the standard Pad\'{e} approximant procedure as described in Ref.~\cite{Baker1996pade}. Overall, Eq.~\ref{eqn:pade} provides a numerically stable truncation for the MKCT Eq.~\ref{eqn:kn_ode}, where \emph{all} coefficients can be evaluated with higher-order moments $\{ \Omega_n \}$.
\subsubsection{Relation of improper self energy to cumulant}
The Dyson equation for the one particle greens function can be written using an improper $\Sigma^I$ self energy as
\begin{align}
    \label{dyson}
    & G_k(t,t') =G_k^0(t,t') + G_k^0(t,t')\Sigma_k^I(t,t')G_k^0(t,t'),\\
\end{align}
instead of using the proper self energy $\Sigma^*$, which satisfies $G_k(t,t') = G_k^0(t,t') + G_k^0(t,t')\Sigma_k^*(t,t')G_k(t,t').$ 
% We can rewrite
% \begin{align}
% & G\left(t, t^{\prime}\right)-G^0\left(t, t^{\prime}\right)=\iint d t_1 d t_2 G^0\left(t, t_1\right) \Sigma^I\left(t_1, t_2\right) G^0\left(t_2, t^{\prime}\right)\\
% & \implies \frac{G\left(t, t^{\prime}\right)}{G^0\left(t, t^{\prime}\right)}-1=\left[G^0\left(t, t^{\prime}\right)\right]^{-1} \iint d t_1 d t_2 G^0\left(t, t_1\right) \Sigma^I\left(t_1, t_2\right) G^0\left(t_2, t^{\prime}\right)\\
%     % &= G_k^0(t,t')[1 + \Sigma_k^{I}(t,t')G_k^0(t,t')] \label{dysoni}\\
%     % &= {G_k^0(t,t') \over 1 - \Sigma_k^*(t,t')G_k^0(t,t')} \label{dysonp},
% \end{align} 
Now, the retarded cumulant ansatz can be written as
\begin{align}
&G_k^R(t,t') = G_k^{0,R}(t,t')e^{C_k^R(t,t')}\\
& \implies {G_k^R(t,t') \over G_k^{0,R}(t,t')} = e^{C_k^R(t,t')}\\
\end{align}
%  This leads to the following form for the cumulant 
% \begin{eqnarray}
% C_k(t,t') &=& \ln\left(1 + \left[G_k^{R,0}(t,t')\right]^{-1}\iint dt_1dt_2 \textcolor{white}{\int}G_k^{R,0}(t,t_1)\Sigma_k^{R,I}(t_1,t_2)G_k^{R,0}(t_2,t')\right).
% \label{cum_time}
% \end{eqnarray}
% So
% \begin{align}
% &e^{C_k\left(t, t^{\prime}\right)}-1=\left[G_k^{0}\left(t, t^{\prime}\right)\right]^{-1} \iint d t_1 d t_2 G_k^{0}\left(t, t_1\right) \Sigma_k^{I}\left(t_1, t_2\right) G_k^{0}\left(t_2, t^{\prime}\right) \\
% & \implies C_k\left(t, t^{\prime}\right)=\ln \left(1+\left[G_k^{0}\left(t, t^{\prime}\right)\right]^{-1} \iint d t_1 d t_2 G_k^{0}\left(t, t_1\right) \Sigma_k^{I}\left(t_1, t_2\right) G_k^{0}\left(t_2, t^{\prime}\right)\right)
% \end{align}
 Let's deal directly with this ratio instead of needing to introduce a self energy.
The retarded Green's function can be written as
\begin{align}
G_k^R(t)&=-i \theta(t)\left\langle\left\{c_k(t), c_k^{\dagger}(0)\right\}\right\rangle \\
&=-i \theta(t)\left\langle\left\{e^{i H t} c_k e^{-i H t}, c_k^{\dagger}\right\}\right\rangle \\
&=-i \theta(t)\left\langle\left\{\sum_{n=0}^{\infty} \frac{(-i t)^n}{n!} \mathcal{L}^n c_k, c_k^{\dagger}\right\}\right\rangle \\
% &=-i \theta(t)\left( \left\langle\left\{c_k, c_k^{\dagger}\right\}\right\rangle+i t\left\langle\left\{\left[H, c_k\right], c_k^{\dagger}\right\}\right\rangle+\frac{(i t)^2}{2}\left\langle\left\{\left[H,\left[H, c_k\right]\right], c_k^{\dagger}\right\}\right\rangle+\cdots \right)\\
&=-i \theta(t)\left( \mu_{0,k}- t\mu_{1,k}+\frac{t^2}{2}\mu_{2,k}+O(t^3) \right)
\end{align}
where we have defined the moments $\mu_{n,k}=\left\langle\left\{\left(i \mathcal{L} \right)^n c_k, c_k^{\dagger}\right\}\right\rangle$ and the Liouvillian superoperator $\mathcal{L} O=[H,O]$. The non-interacting retarded Green's function is given by
\begin{align}
G_k^{R,0}(t)&=-i \theta(t)\left( \mu_{0,k}^0- t\mu_{1,k}^0+\frac{t^2}{2}\mu_{2,k}^0+O(t^3) \right)
\end{align}
where the non-interacting moments are $\mu_{n,k}^0=\left\langle\left\{\left( i \mathcal{L}_0\right)^n c_k, c_k^{\dagger}\right\}\right\rangle$ and $\mathcal{L}_0 O=[H_0,O]$. Defining $A(t)= 1-t\mu_{1,k}+\frac{t^2}{2}\mu_{2,k}+O(t^3)$ and $B(t)= 1- t\mu_{1,k}^0+\frac{t^2}{2}\mu_{2,k}^0+O(t^3)$ we can use a geometric series to write
\begin{align}
\frac{1}{B(t)}&=1+ t \mu_{1, k}^0+t^2\left[\left(\mu_{1, k}^0\right)^2-\frac{1}{2}\mu_{2, k}^0\right]+O\left(t^3\right)
\end{align}
Note that the inverse power series coefficients can be computed by Wronski's formula (if one is interested in still higher orders of $t$).
So, we can write the ratio and then group terms by order in $t$, to get
\begin{align}
R_k(t)=\frac{G_k^R(t)}{G_k^{R,0}(t)}
&=\frac{-i\theta (t)}{-i\theta (t)}\times\frac{A(t)}{B(t)} \\
&= \left( 1- t\mu_{1,k}+\frac{t^2}{2}\mu_{2,k}+O(t^3) \right) \left( 1+ t \mu_{1, k}^0+t^2\left[\left(\mu_{1, k}^0\right)^2-\frac{1}{2}\mu_{2, k}^0\right]+O\left(t^3\right) \right)\\
&= \left( 1+t\underbrace{\left[-\left(\mu_{1,k}-\mu_{1,k}^0\right)\right]}_{\alpha _{1,k}}+t^2\underbrace{\left[\frac{1}{2}\left(\mu_{2,k}-\mu_{2,k}^0\right)-\mu_{1,k}\mu_{1,k}^0+\left(\mu_{1,k}^0\right)^2\right]}_{\alpha _{2,k}}+O(t^3) \right)
\end{align}
Given that the cumulant can be expanded as $C_k^R(t) = \kappa_{1,k} t + \kappa_{2,k} t^2 + O(t^3)$, we can Taylor expand the exponential $e^{C_k^R(t)}$ and then match coefficients with the above expression for $R_k(t)$ to plug into the usual relations between the cumulants $\kappa _{n,k}$ and moments $\alpha_{n,k}$, to get
\begin{align}
    \kappa_{1,k} = \alpha_{1,k} &= -\left(\mu_{1,k}-\mu_{1,k}^0\right)\\
    \kappa_{2,k} = \alpha_{2,k} - \frac{\alpha_{1,k}^2}{2} &= \frac{1}{2}\left(\mu_{2,k}-\mu_{2,k}^0\right)-\mu_{1,k}\mu_{1,k}^0+\left(\mu_{1,k}^0\right)^2 -\frac{1}{2}{\left[-\left(\mu_{1,k}-\mu_{1,k}^0\right)\right]^2}\\
&= \frac{1}{2}\left(\mu_{2,k}-\mu_{2,k}^0\right)-\mu_{1,k}\mu_{1,k}^0+\left(\mu_{1,k}^0\right)^2 -\frac{1}{2}\left(\mu_{1,k}-\mu_{1,k}^0\right)^2\\
&= \frac{1}{2}\left[\left( \mu_{2,k} - \mu_{2,k}^0 \right) +\left( \mu_{1,k} \right)^2 + \left( \mu_{1,k}^0 \right)^2 \right]
\end{align}
So now we need to determine how to compute the moments for this cumulant approach and potentially for the MKCT approach. But let's begin by discerning the form for the 2/2 Pad approximant to the cumulant for the memory kernel at n=1:
\begin{align}
    K_1(t) &\approx \frac{a_0 + a_1 t+ a_2 t^2}{1 + b_1 t + b_2 t^2}\\
& \approx \left(a_0 + a_1 t+ a_2 t^2\right)\left(1 - b_1 t + \left(b_1^2 - b_2\right) t^2 + O(t^3)\right) \\
& \approx a_0 + t\left(a_1 - a_0 b_1\right) + t^2\left(a_2 - a_1 b_1 + a_0\left(b_1^2 - b_2\right)\right) + O(t^3)
\end{align}
with the derivatives given by $c_0 = K_1(0)$, $c_1 = K_1^{(1)}(0)$, and $c_2 = \frac{K_1^{(2)}(0)}{2}$. Matching coefficients of $t^0$, $t^1$, and $t^2$ gives us the following system of equations:
\begin{align}
    c_0 &= a_0 \\
    c_1 &= a_1 - a_0 b_1 \implies a_1 = c_1 + a_0 b_1\\
    c_2 &= a_2 - a_1 b_1 + a_0\left(b_1^2 - b_2\right) \implies a_2 = c_2 + a_1 b_1 - a_0\left(b_1^2 - b_2\right)
\end{align}
We can find that $a_0 = K_1(0)$, $a_1 = K_1^{(1)}(0) - \frac{K_1(0) K_1^{(2)}(0)}{2 K_1^{(1)}(0)}$, and $b_1 = -\frac{K_1^{(2)}(0) / 2}{K_1^{(1)}(0)}$. We start by computing
\begin{align}
    K_1(0) &= \Omega_2 - \Omega_1^2 = \mu_{2,k} - \mu_{1,k}^2\\
    K_1^{(1)}(0) &= K_2(0) - \bar{\Omega}_1 \Omega_1 = \Omega_3 - \Omega_1 \Omega_2 - \bar{\Omega}_1 \Omega_1 = \mu_{3,k} - \mu_{1,k} \mu_{2,k} - \bar{\Omega}_1 \mu_{1,k}\\
\end{align}
% So:
% $$
% b_1=-\frac{K_n^{(2)}(0) / 2}{K_n^{(1)}(0)}, \quad a_1=K_n^{(1)}(0)-\frac{K_n(0) K_n^{(2)}(0)}{2 K_n^{(1)}(0)}
% $$

% Final [1/1] Pad:
% $$
% K_n^{[1 / 1]}(t)=\frac{K_n(0)+\left(K_n^{(1)}(0)-\frac{K_n(0) K_n^{(2)}(0)}{2 K_n^{(1)}(0)}\right) t}{1-\frac{K_n^{(2)}(0)}{2 K_n^{(1)}(0)} t} .
% $$
% \begin{align}
%     \mu_{2,k} &= \left\langle\left\{\mathcal{L}^2 c_k, c_k^{\dagger}\right\}\right\rangle = \left\langle\left\{[H,[H,c_k]], c_k^{\dagger}\right\}\right\rangle \\
%     &= \left\langle\left\{[H_0 + V,[H_0 + V,c_k]], c_k^{\dagger}\right\}\right\rangle \\4
% \end{align}
\subsubsection{Fundamental starting point}
We start with the definition of the retarded Green's function in the time domain:
\begin{equation}
G_k^R(t) \equiv -i \theta(t)\left\langle\left\{c_k(t), c_k^{\dagger}(0)\right\}\right\rangle .
\end{equation}
Immediately, we can Fourier transform to the frequency domain:
\begin{equation}
G_k^R(\omega)=\int_{-\infty}^{\infty} d t e^{i \omega t} G_k^R(t) .
\end{equation}
But because $G_k^R(t)$ is already zero for $t<0$ (by the $\theta(t)$ ), this integral reduces to
\begin{align}
G_k^R(\omega)&=-i \int_0^{\infty} d t e^{i \omega t}\left\langle\left\{c_k(t), c_k^{\dagger}(0)\right\}\right\rangle \\
&=-i \int_0^{\infty} d t e^{i \omega t} \sum_{n=0}^{\infty} \frac{(i t)^n}{n!}\mu_{n,k} \\
&=-i \sum_{n=0}^{\infty} \frac{i^n}{n!}\mu_{n,k} \int_0^{\infty} d t e^{i \omega t}t^n \\
&=-i \sum_{n=0}^{\infty} \frac{i^n}{n!}\mu_{n,k} \frac{n!}{(i \omega)^{n+1}} \\
&=-\sum_{n=0}^{\infty} \frac{\mu_{n,k}}{\omega^{n+1}} ,
\end{align}
where we have defined the moments $\mu_{n,k}=\left\langle\left\{\mathcal{L}^n c_k, c_k^{\dagger}\right\}\right\rangle$. This works because $c_k(t)=e^{i H t} c_k e^{-i H t} = e^{i \mathcal{L} t} c_k$, where $\mathcal{L}$ is the Liouvillian superoperator, so the time evolution operator can be expanded in a Taylor series, as $e^{i \mathcal{L} t}=\sum_{n=0}^{\infty} \frac{(i t)^n}{n!} \mathcal{L}^n \implies \left\langle\left\{c_k(t), c_k^{\dagger}(0)\right\}\right\rangle  = \sum_{n=0}^{\infty} \frac{(i t)^n}{n!}\mu_{n,k}$. The complementary projection operator is $\mathcal{Q} = 1 - \mathcal{P}$. The Liouvillian superoperator acts on an arbitrary operator $X$ as $\mathcal{L} X = [H,X]$.
Since we know that Mori's is formally a projector method with $\mathcal{P}X = \frac{(X,c_k)}{(c_k,c_k)} c_k$, where $(A,B) = \langle \{A, B^\dagger\} \rangle$ is the fermionic Mori inner product, so $(c_k, c_k) = \langle \{c_k, c_k^\dagger\} \rangle = 1$. Lanczos is also formally a projection onto the Krylov subspace, so we can try to exploit this by devising a Lanczos procedure. Then we can initiate a Lanczos sequence with $|f_0\rangle = c_k$ and then for $n=0$, we have
\begin{equation}
|f_1\rangle = \mathcal{L} |f_0\rangle - a_0 |f_0\rangle ,
\end{equation}
where $a_0 = \frac{(\mathcal{L} f_0, f_0)}{(f_0, f_0)} = \mu_{1,k}$. Then for 
$n \geq 1$ define
\begin{equation}
|f_{n+1}\rangle = \mathcal{L} |f_n\rangle - a_n |f_n\rangle - b_n^2 |f_{n-1}\rangle ,
\end{equation}
where the coefficients are given by $a_n = \frac{(\mathcal{L} f_n, f_n)}{(f_n, f_n)}$ and $b_{n+1}^2 = \frac{(f_{n+1}, f_{n+1})}{(f_n, f_n)}$. Let us try to determine the action of the Liouvillian onto a given state $|f_n\rangle$. We can write
\begin{align}
\mathcal{L} |f_n\rangle &= [H_0 + V, |f_n\rangle] \\
&= \mathcal{L}_0 |f_n\rangle + [V, |f_n\rangle] \\
\end{align}
where $H_0$ is the non-interacting Hamiltonian and $V$ is the interaction. We can also define a non-interacting Liouvillian $\mathcal{L}_0$ such that $\mathcal{L}_0 X = [H_0, X]$. So we can write