\section{Naming conventions}
\begin{frame}
    \frametitle{How we get the cumulant}
\begin{align}
    \bm{G}^0(t) \bm{C}(t) &= \iint \dd t_1 \dd t_2 \bm{G}^0(t-t_1) \bm{\Sigma}^c(t_1 - t_2) \bm{G}^0(t_2) \label{eq:GC} \\
\implies C_{pp}(t)&= i\int  \frac{\dd \omega'}{2\pi} e^{-i\omega' t} \frac{{\Sigma}_{pp}^c(\omega' + \epsilon_p)}{(\omega' + i\eta)^2} \label{eq:Cpp_0} \\
\implies C^{(2)}_{pp}(t)&= \frac{1}{2}\sum_{iab} \frac{\left< pi \left| \right| ab \right>^2}{\left(\epsilon_{pi}^{ab}\right)^2}
\left(e^{-i \epsilon_{pi}^{ab} t} +i \epsilon_{pi}^{ab} t -1 \right)
+2h1p \\
\implies A_{pp}(\omega) &= -\frac{1}{\pi} \operatorname{Im} \left(-i \Theta(t) e^{-i\epsilon_p t} e^{C^{(2)}_{pp}(t)} \right)
\label{eq:cumulant_2nd}
\end{align}
but Loos takes the first order cumulant, which presumably avoids numerical instability because it is just defined in the frequency domain
\begin{align}
    A_{pp}(\omega) = \frac{Z_p^{QP}}{\omega - \epsilon_p^{QP} + i\eta} + \sum_{i a b} \frac{Z_{piab}^{sat}}{\omega - \epsilon_{piab}^{sat} + i\eta} + \sum_{i j a} \frac{Z_{pija}^{sat}}{\omega - \epsilon_{pija}^{sat} + i\eta}
\end{align}
\end{frame}
\begin{frame}
    \frametitle{Naming conventions}
    \begin{itemize}
        \item As eqn. \ref{eq:GC} shows, the $G_0$ that defines both components in \ref{eq:cumulant_2nd} should be the same.
        \item HF+C(2) makes sense and is probably clearer than HF+MP2+C
        \item HF+C(SRG-2) is not consistent, but SRG-MP2+C(SRG-2) is.
        \item We want to do BWs2+C(BWs2).
        \item This is why I prefer the notation $G_0@X;C(2@X)$.
    \end{itemize}
\end{frame}
\section{TDL clarifications}
\begin{frame}
    \frametitle{What is Garnet's Fig. 2b showing?}
    \begin{itemize}
        \item Why do you say we don't know the TDL spectral function at TDL?
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Argument against the use of SRG-MP2 in extended systems}
\begin{itemize}
    \item Look at Kresse's argument
    \item Should I run SRG-MP2+C for rs=2 to check if this holds for cumulants?
\end{itemize}
\end{frame}